%
% SKTDOC.SKT
%
% Revision 1.0 1996/02/13 Charles Wikner wikner@nacdh4.nac.ac.za
% Revision 1.1 1996/03/05 added skt*.tfm files to distribution
% Revision 2.0 1996/11/27 major upgrade.
% Revision 2.2.1 2016/09/01 compilation fixes and modernization
%
% Copyright 1996 & 2002 Charles Wikner
% This program can be redistributed and/or modified under the terms
% of the LaTeX Project Public License Distributed from CTAN
% archives in directory macros/latex/base/lppl.txt; either
% version 1 of the License, or any later version.
%
%
% This is the documentation source file.
%

\documentclass[12pt]{article}
\usepackage[larger,iitalic,uitalic]{skt}
% Page size compatible both with Letter and A4 papers.
\usepackage[paperheight=279.4mm, paperwidth=210mm]{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{mflogo}
\providecommand{\lightgray}{\color{lightgray}}
\usepackage{microtype}
\usepackage{titlesec}

% Tweak section title format to conserve space.
\titleformat{\section}{\large\bfseries}{\thesection}{\parskip}{}
% Make \section*s unnumbered.
\setcounter{secnumdepth}{0}

\DeclareFixedFont{\bigskt}{OT1}{skt}{m}{n}{46mm}

% Dotted hrule.
\makeatletter
\newcommand{\Dotfill}{\leavevmode \cleaders \hb@xt@ .9em{\hss .\hss }\hfill \kern \z@}
\makeatother
\newcommand{\dotrule}{\hspace*{\fill}\parbox{0.3\textwidth}{\Dotfill}\hspace*{\fill}}

\pagenumbering{skt}

{\skt }

%\makeatletter\def\@skt#1{{\bf\small Beta - }{{}\skt\number #1}}\makeatother%%%

%\addtolength{\columnsep}{-44pt}
\parindent 0pt
\addtolength{\parskip}{2mm}
\tolerance=500
\raggedbottom
\hyphenpenalty=9999

% The following commands etc. are used by the sa.myoga table only.
\newcounter{entrycount}
\setcounter{entrycount}{0}
\newcommand{\entrynumber}[1]%
   {\stepcounter{entrycount}%
    \makebox[7mm][r]{\theentrycount}%
    \makebox[1mm][l]{\textsuperscript{#1}}}
\newcommand{\sing}[3]%
   {\mbox{\entrynumber{#1} \makebox[14mm][l]{#2}{#3}}\par}
\newcommand{\dual}[4]%
   {\mbox{\entrynumber{#1} \makebox[14mm][l]{#2}{#3}}\par%
    \hspace*{23.5mm}\mbox{#4}\par}

\title{Sanskrit for \LaTeXe{}\\Version 2}
\author{Charles Wikner (1996-2002)\\Václav Haisman (2016-2025)\\Sumukh Prasad (2025-\textit{present})}
\date{}

\begin{document}

\begin{titlepage}
  \maketitle
\end{titlepage}

\tableofcontents
\clearpage

\section{Introduction}%
%
The package contains the font files and pre-processor for printing
Sanskrit text in both {\skti devan\=agar\={\i}} and transliterated Roman
with diacritics.

Some features of the {\skti devan\=agar\={\i}} font:\\[2mm]
\makebox[8mm][c]{$\bullet$}
      Font available in three weights 
      and two slopes.\\ 
\makebox[8mm][c]{$\bullet$}
      The i-hooks connect to the consonants at the correct positions.\\
\makebox[8mm][c]{$\bullet$}
      Accents for all {\skti Veda\/}s ({\skti \d Rgveda}, {\skti S\=amaveda}, 
      {\skti Taittir\={\i}ya}), etc.\\
\makebox[8mm][c]{$\bullet$}
      Accent marking in colour or grey shading.\\
\makebox[8mm][c]{$\bullet$}
      Choice of character forms (e.g.~{\skt A\,\ZN{/}\,`A}) and
      {\skti sa\d myoga} (e.g.~{\skt \ZM{BNz0dcRfA}*.a\,\ZN{/}\,Vca}).\\
\makebox[8mm][c]{$\bullet$}
      Range of intra- and inter-syllable spacing.\\
\makebox[8mm][c]{$\bullet$}
      Dynamic option selection.

Some features of the transliterated Roman:\\[2mm]
\makebox[8mm][c]{$\bullet$}
      Full accent marking and stacking in basic transliteration mode.\\
\makebox[8mm][c]{$\bullet$}
      Four `cases' (as per S.\,M.\,Katre) in technical transliteration mode.\\
\makebox[8mm][c]{$\bullet$}
      Each transliteration mode has four styles: Roman/italic $\times$\ 
      bold/normal. 

Indebtedness to the earlier work of Frans Velthuis and Dominik Wujastyk is
acknowledged: the overall structure and encoding is based upon theirs.

\section{Upgrading from Version 1}%
%
Every file in this package differs greatly from the Version~1 release,
so all need to be replaced, and all related pixel files (e.g.~\verb+skt*.pk+)
should be deleted.

While this is essentially a major upgrade to Version~1, there are some changes
that impact on the users' files (those with a \verb+.skt+ extension):

\makebox[8mm][c]{$\bullet$}
      The accent marking symbols, \verb+<+ and \verb+>+, have changed.\\
\makebox[8mm][c]{$\bullet$}
      The punctuation marks \verb+! ` ' [ ]+ no longer pass through as 
      Roman.\newline\hspace*{8mm}\ (But see page~\pageref{ref:punct} for producing them
      in version 2.)\\
\makebox[8mm][c]{$\bullet$}
      The option file (\verb+skt.opt+) is no longer used; instead the 
      selection of\newline\hspace*{8mm}\ 
      options is included anywhere within the \verb+.skt+ file.\\
\makebox[8mm][c]{$\bullet$}
      Any direct access of the skt font (e.g. \verb+\symbol{128}+) should be 
      checked\newline\hspace*{8mm}\ 
      against the new font map.\\
\makebox[8mm][c]{$\bullet$}
      Any direct use of the \verb+\Z*+ commands which are defined in the style 
      file,\newline\hspace*{8mm}\ 
      should be checked against their new definitions.
\vspace{5mm}

\section{Illustrations of Input and {\sktX Devan\=agar\={\i}} Output}%
%
The following brief samples demonstrate the available styles of 
{\skti devan\=agar\={\i}\/} font and their encoding. In this mode upper 
case characters are disallowed. 

Note that the `larger' option has been selected so that, in
this 12pt document, the {\skti devan\=agar\={\i}\/} is printed at 14pt.

\verb+{\+\verb+sktb  te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\sktb  .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}\\[1mm]
\verb+{\+\verb+skt   te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\skt  .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}\\[1mm]
\verb+{\+\verb+sktf  te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\sktf  .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}\\[1mm]
\verb+{\+\verb+sktbs te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\sktbs .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}\\[1mm]
\verb+{\+\verb+skts  te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\skts  .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}\\[1mm]
\verb+{\+\verb+sktfs te_ja_svi naa_vadhii!tamastu|}+\hspace{2mm}
             {\sktfs .te\ZK{`8}a.j\ZK{`8}a:\ZH{0}{i0//Y7}a.s1va na.\ZK{`8}a:va:Di4a.\ZK{`7}a:ta:ma:s1tua\ZS{12}@A}


The intra- and inter-character spacing options give six steps of horizontal
density; the extremes are:
\vspace{-1mm}
\begin{center}
{\skt  .nEa;va ;Y2a;k\ZH{-12}{M}+:Y4a;.ca;tk+.=+ea;mi6a;a;Y3a;ta yua;k2+:ea ma;nyea;ta ta:t1va;Y2a;va;t,a\ZS{12}@A}\\[2mm]
{\skt  .nEa.va ;i9ak\ZH{-12}{M}+Y1a.ca.tk;=.ea.mi3aa.Y0ata yua.k2;ea ma.nyea.ta tat1va.i9ava.t,a\ZS{12}@A}
\end{center}


\section{Illustrations of Basic Transliteration}%
%
The same input may also be used to produce transliterated output.
Note that the `\verb+iitalic+' option is selected, but not `\verb+xitalic+'.

{\skt }
\verb+{\+\verb+sktx te_ja_svi naa_vadhii!tamastu|}+\hspace{.8mm}
             {\sktx t\ZA{2}{e}j\ZA{2}{a}svi n\ZA{2}{\=a}vadh\ZA{1}{\={\i}}tamastu{\upshape\,$\mid$}}

\verb+{\+\verb+sktX te_ja_svi naa_vadhii!tamastu|}+\hspace{.8mm}
             {\sktX t\ZA{2}{e}j\ZA{2}{a}svi n\ZA{2}{\=a}vadh\ZA{1}{\={\i}}tamastu{\upshape\boldmath\,$\mid$}}

\verb+{\+\verb+skti te_ja_svi naa_vadhii!tamastu|}+\hspace{.8mm}
             {\skti t\ZA{2}{e}j\ZA{2}{a}svi n\ZA{2}{\=a}vadh\ZA{1}{\={\i}}tamastu{\upshape\,$\mid$}}

\verb+{\+\verb+sktI te_ja_svi naa_vadhii!tamastu|}+\hspace{.8mm}
             {\sktI t\ZA{2}{e}j\ZA{2}{a}svi n\ZA{2}{\=a}vadh\ZA{1}{\={\i}}tamastu{\upshape\boldmath\,$\mid$}}

It can be seen from the above examples that \verb+sktX+ is a boldface
version of \verb+sktx+ (i.e.~also upright), and that \verb+sktI+ is
similarly a boldface version of \verb+skti+ (also italic).
The only difference between \verb+sktx/X+ and \verb+skti/I+ is that
they may be independently selected as italic in the style file options.

\pagebreak

The Western accent marking system may also be used:\\[2mm]
\verb+{\+\verb+skti tejasvi' naava'dhii`tamastu|}+\hspace{.8mm}
             {\skti tejasv\ZA{8}{{\i}} n\=av\ZA{8}{a}dh\ZA{7}{\={\i}}tamastu{\upshape\,$\mid$}}

In this basic transliteration mode (\verb+sktx/X+ or \verb+skti/I+) uppercase 
characters are allowed: these do not affect the transliteration encoding, 
but facilitate the printing of capital letters, for example:\\[2mm]
\verb+{\+\verb+sktI  Bhaarate Raamo vasati}+\hspace{5mm}
                   {\sktI  Bh\=arate R\=amo vasati}
\vspace{4mm}

\section{Illustrations of Technical Transliteration}%
%
As in the basic transliteration mode, there are four font styles selected
through \verb+sktt/T+ or \verb+sktu/U+; however, in this mode only the
Western accent marking is allowed. This technical (grammatical) mode
follows the style of S\,M\,Katre in his translation of the 
{\skti A\d s\d t\=adhy\=ay\={\i}}, having four `cases' of letters.

Uppercase is used to indicate {\sktT \ZY{I}\ZY{T}\/} letters 
(e.g.~{\skti praty\=ah\=ara\/} {\sktT a\ZX{C}\/}): note that in this mode
a {\skti mah\=apr\=a\d na spar\'sa\/} (e.g.~{\skti Bha\/}) must have the 
`{\skti h\/}' in the same case as the previous letter. In the example 
given above, \verb+Bhaarate+ would produce an error: it needs to be 
\verb+bhaarate+ or \verb+BHaarate+. The uppercase letters in this mode 
are slightly smaller than those in the basic transliteration mode.

In this mode only, letters may also be preceded by the underscore character
`\verb+_+'. The effect that this has depends upon the case of the following
letter: if the letter is lowercase, it will be underlined to indicate that
its presence is for the sake of pronunciation only (e.g.~{\sktT jh\ZW{a}\ZX{L}}\/);
before an uppercase letter, it will reduce the size of the uppercase letter
to the height of the lowercase letters to indicate technical words
(e.g.~{\sktT \ZY{I}\ZY{T}\/}).
For example, the {\skti P\=a\d nini s\=utra\/}\\[2mm]
{\skt ..ca:ja;eaH\ZS{4} k\ZH{-12}{u} ;Y3a;Ga;NNya;ta;eaH\ZS{4}\ZS{12}@A\ZS{6}@A 7\ZS{12}@A 3\ZS{12}@A 52\ZS{12}@A\ZS{6}@A}\\[2mm]
may be encoded in the technical mode as\\[3mm]
\verb+{\+\verb+sktT c_a-j-o.h kU GH_I_T=.NyaT-o.h}+ to produce\\[2mm]
{\sktT c\ZW{a}\ZN{-}j\ZN{-}o\d h k\ZX{U} \ZX{GH}\ZY{I}\ZY{T}\ZN{=}\ZX{\d N}ya\ZX{T}\ZN{-}o\d h}\\[3mm]
This translates as: A substitute {\sktT k\ZX{U}\/} replaces {\sktT c\/} or 
{\sktT j\/} before {\sktT \ZX{\d N}ya\ZX{T}\/} or [affixes]\newline\hspace*{35mm}with 
{\sktT \ZX{GH}\/} as an {\sktT \ZY{I}\ZY{T}\/} marker.

\section{Vedic Accent Marking}%
%
Since the significance of the {\skti devan\=agar\={\i}} accent marking may
differ between {\skti Veda\/}s (e.g.~{\skt A\ZH{-6}{\ZK{`7}}} is {\skti svarita} in
{\skti \d Rgveda}, but {\skti ud\=atta} in {\skti K\=a\d thaka\/}), the character
used for encoding is, where possible, vaguely similar to the form used in
the {\skti devan\=agar\={\i}}, and this form is largely retained in the 
transliterated output. 
\vspace{\fill}

{\skt }
\renewcommand{\arraystretch}{1}%{1.2}
\begin{tabular}{|c|c|c|c|}
\multicolumn{4}{c}{{\skti \d Rgveda\/} etc.~marking system:} \\[.5mm]
\multicolumn{4}{c}{use option~6 to enable these in}\\[-.5mm]
\multicolumn{4}{c}{the basic transliteration mode.} \\[2mm]
\hline input & skt     & skti          & sktt       \\
\hline
\verb+a!+    & {\skt A\ZH{-6}{\ZK{`7}}}    & {\skti \ZA{1}{a}}    & error      \rule{0mm}{6.5mm} \\
\verb+a!!+   & {\skt A\ZH{-9}{\ZK{`7}}\ZH{-3}{\ZK{`7}}}   & {\skti \ZA{6}{a}}   & error      \rule{0mm}{6.5mm} \\
\verb+a_+    & {\skt A\ZH{-6}{\ZK{`8}}}    & {\skti \ZA{2}{a}}    & {\small see note} \rule{0mm}{5.5mm}\\
\verb+a"1+   & {\skt A\ZK{1\ZH{-12}{`7}\ZH{-10}{`8}}}   & {\skti \ZA{4}{a}}   & error      \rule{0mm}{7.5mm}\\
\verb+a"3+   & {\skt A\ZH{-6}{\ZK{`8}}\ZK{3\ZH{-12}{`7}\ZH{-8}{`8}}}   & {\skti \ZA{3}{a}}   & error      \rule{0mm}{7.5mm}\\
\verb+a.1+   & {\skt A\ZK{1\ZH{-10}{`8}}}   & {\skti \ZA{15}{a}}   & error      \rule{0mm}{5.5mm}\\
\verb+a.3+   & {\skt A\ZK{3\ZH{-12}{`7}\ZH{-8}{`8}}}   & {\skti \ZA{16}{a}}   & error      
             \raisebox{-2.5mm}{\rule{0mm}{10mm}}\\
\hline
\multicolumn{4}{c}{Note: {\smaller The underscore character is}
                   \rule{0mm}{6mm}}\\[-.8mm]
\multicolumn{4}{c}{{\smaller is used differently in technical mode.}}\\
\multicolumn{4}{c}{Western (and technical) marking.}\rule{0mm}{12mm} \\[2mm]
\hline input & skt     & skti          & sktt       \\
\hline
\verb+a^+    & {\skt A\ZH{-6}{\ZK{`0}}}    & {\skti \ZA{5}{a}}    & {\sktt \ZA{5}{a}} \rule{0mm}{7mm} \\
\verb+a'+    & error                     & {\skti \ZA{8}{a}}    & {\sktt \ZA{8}{a}} \\
\verb+a`+    & error                     & {\skti \ZA{7}{a}}    & {\sktt \ZA{7}{a}} \\\hline
\end{tabular}
%
\hspace{\fill}
%
\begin{tabular}{|c|c|c|c|}
\multicolumn{4}{c}{{\skti S\=amaveda} and other accents: }\\[.5mm]
\multicolumn{4}{c}{use option~7 to enable these in}\\[-.5mm]
\multicolumn{4}{c}{the basic transliteration mode.} \\[2mm]
\hline input & skt     & skti          & sktt       \\
\hline
\verb+a<1>+  & {\skt A\ZH{-6}{\ZK{`1}}}   & {\skti \ZA{9}{a}}  & error \rule{0mm}{7mm} \\
\verb+a<2>+  & {\skt A\ZH{-6}{\ZK{`2}}}   & {\skti \ZA{10}{a}}  & error \rule{0mm}{6mm} \\
\verb+a<3>+  & {\skt A\ZH{-6}{\ZK{`3}}}   & {\skti \ZA{11}{a}}  & error \rule{0mm}{6mm} \\
\verb+a<2r>+ & {\skt A\ZH{-10}{\ZK{`4}}}  & {\skti \ZA{12}{a}} & error \rule{0mm}{6mm} \\
\verb+a<2u>+ & {\skt A\ZH{-10}{\ZK{`5}}}  & {\skti \ZA{13}{a}} & error \rule{0mm}{6mm} \\
\verb+a<3k>+ & {\skt A\ZH{-12}{\ZK{`6}}}  & {\skti \ZA{14}{a}} & error \rule{0mm}{6mm} \\\hline
\verb+a<!!>+ & {\skt A\ZH{-11}{\ZK{`!}}}  & {\skti \ZA{25}{a}} & error \rule{0mm}{7mm} \\
\verb+a<u>+  & {\skt A\ZH{-6}{\ZK{`u}}}   & {\skti \ZA{17}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<w>+  & {\skt A\ZH{-6}{\ZK{`z}}}   & {\skti \ZA{18}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<_>+  & {\skt A\ZP{-16}{-10}{\ZK{@I@o}}}   & {\skti \ZA{19}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<.>+  & {\skt A\ZP{-8}{-10}{\ZK{@M}}}   & {\skti \ZA{20}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<..>+ & {\skt A\ZP{-8}{-10}{\ZK{@M\ZS{-9}@M}}}  & {\skti \ZA{21}{a}} & error \rule{0mm}{5mm} \\
\verb+a<!>+  & {\skt A\ZP{-6}{-12}{\ZK{@I\ZV{2}{@I}}}}   & {\skti \ZA{22}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<^>+  & {\skt A\ZP{-6}{-16}{\ZK{@r\ZP{-3}{5}{@b}\ZV{2}{@b}}}}   & {\skti \ZA{24}{a}}  & error \rule{0mm}{5mm} \\
\verb+a<s>+  & {\skt A\ZS{1}\ZK{`s}}   & {\skti \ZA{23}{a}}  & error \rule{0mm}{5mm} \\\hline
\end{tabular}
{\skt }
\vspace{\fill}

The pre-processor only allows accents after a vowel, Vedic 
{\skti anusv\=ara}, or~\verb+n+; where the vowel is nasalised 
as well, the nasalisation must be after the accent, 
i.e.~\verb+a_#+ to produce {\skt A\ZH{-6}{<}\ZH{-6}{\ZK{`8}}}.

The {\skti devan\=agar\={\i}\/} accent marks themselves may be printed in
colour (red is the tradition) or grey. This actually makes the text easier 
to read: the sample text from the {\skti \d Rgveda} on page~\pageref{rgtext}
has the accents in the first four verses the default black, and in the next 
four verses they are `lightgray' (using \verb+xcolor+).
To set the accent colour redefine the \verb+\ZK+ command anywhere in the 
\verb+.skt+~file as \verb+\renewcommand{\ZK}[1]{{\lightgray #1}}+ for example.

In transiteration, the accents should stack correctly and track in 
italics, e.g.:\\
{\sktt \ZA{68}{\ZW{\=r\llap{\d{\kern.51em}}}}} and {\sktu \ZA{68}{\ZW{\=r\llap{\d{\kern.51em}}}}} (signifying a long or short 
{\skti ud\=atta r\llap{\d{\kern.51em}}} used for pronunciation only).

\section{Dynamic Option Selection}%
%
The selection and deselection of options may occur anywhere in the preamble
(but after \verb+\usepackage{skt}+) or in the body of the text. 
By default all options are deselected
The options are used by the pre-processor
and not passed to the \verb+.tex+ output file: be aware of this when using
\LaTeX\ \verb+\include+ or \verb+\input+ commands.

Each option comprises a numeric string in the range 0--199 followed by a
\verb/+/ or \verb+-+ to respectively select or deselect the option: the
options must be enclosed within square brackets to distinguish them from
the rest of the text. Multiple options within the same square brackets
should be separated by one or more spaces.
For example, \verb/[40+]/ selects option 40, \verb/[40- 49+ 44+]/ deselects
option 40 and selects options 44 and 49. (Details of the effects of the
options are given in the next four sections.)
The option selection must necessarily be within a \verb+{+\verb+\skt...}+ 
group since this is the only text that is actually parsed by the pre-processor.

Note that both square brackets, \verb+[+ and \verb+]+, need to be on
the same input text line. For example:\\[2mm]
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{l|c|}\cline{2-2}
\verb/\documentclass[12pt]{article}/             & \\ 
\verb/\usepackage[larger]{skt}/                  & This will\\
\verb/{/\verb/\skt [40+]} % select alternate a/  & print as:\\
\verb/\begin{document}/                          & \\
\verb/{/\verb/\skt ak.sa.na [40- 49+ 44+]ak.sa.na[49- 44-]}/ &
                          {\skt `A;[a;Na A:`[a;`Na}\\
\verb/\end{document}/                            & \\\cline{2-2}
\end{tabular}

Note that once an option is selected (anywhere in the file), it remains
in effect until explicitly deselected, irrespective of \verb+{+\verb+\skt...}+
groupings.

\clearpage

\section{Control Options (0--11)}%
%
The control options are all those that do not affect character shapes in
transliteration or {\skti devan\=agar\={\i}}.
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 0:} Set all options to known state.
\end{minipage}}

In documents such as this one, where the options are changed very often,
it is useful from time to time to reset all options to the default state.
Option~\verb/0+/ will select all options, and option~\verb/0-/ will deselect 
them all.
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 1:} Set intraspace less than interspace.\\
{\bf Option 2:} Reduce interspace.\\
{\bf Option 3:} Minimum interspace.
\end{minipage}}

These three interact to set the horizontal space within
{\skti devan\=agar\={\i}\/} words: options~2 and~3 provide three levels of
interspace (the space between syllables), while option~1 selects the
intraspace (space within a syllable, i.e.~when the syllable vowel adds
an extra vertical bar).

\renewcommand{\arraystretch}{1.6}
\begin{tabular}{p{40mm}|c|c|c|l|}
\cline{2-4} 
Illustration:\makebox[18mm]{}
              & 1  & 2  & 3  & \multicolumn{1}{c}{} \\\cline{2-5}
\rule{0mm}{5.5mm}&--&-- & -- & {\skt  A;ea;Y6a;ma;tyea;ta;d;[a:=+Y6a;ma;d\ZS{1}> .sa;vRa;m,a}\\
Option selection: 
              & +  & -- & -- & {\skt  A:ea;Y5a:ma;tyea;ta;d;[a:=+Y5a:ma;d\ZS{1}> .sa;vRa;m,a}\\
\makebox[5mm][c]{+} = selected;      
              & -- & +  & -- & {\skt  A:ea:Y5a:ma:tyea:ta:d:[a.=;Y5a:ma:d> .sa:vRa:m,a}\\
\makebox[5mm][c]{--} = deselected;    
              & +  & +  & -- & {\skt  A.ea:Y4a.ma:tyea:ta:d:[a.=;Y4a.ma:d> .sa:vRa:m,a}\\
\makebox[5mm][c]{x} = don't care.    
              & -- & x  & +  & {\skt  A.ea:Y4a.ma.tyea.ta.d.[a=:Y4a.ma.d> .sa.vRa.m,a}\\
              & +  & x  & +  & {\skt  Aea:Y3ama.tyea.ta.d.[a=:Y3ama.d> .sa.vRa.m,a}\\
\cline{2-5}
\end{tabular}{\skt }
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 4:} Raise accents (less significant bit).\\
{\bf Option 5:} Raise accents (more significant bit).
\end{minipage}}

These two adjust the minimum spacing of {\skti devan\=agar\={\i}\/} accents above 
the hortizontal line, and may be used to minimize or eliminate the variation
in the accent's vertical position that arises due to vowel hooks etc.~above
the horizontal line\,---\,this is particularly important for the 
{\skti S\=amaveda} accents.

\clearpage

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{p{40mm}|c|c|l|}
\cline{2-3}
Illustration:     & 4  & 5  &   \multicolumn{1}{c}{} \\\cline{2-4}
                  & -- & -- & \rule{0mm}{7mm}{\skt  
 :pa;a;v\ZK{`3}a;k\ZH{-12}{\ZK{`2}}\ZS{3}H\ZS{4} :p\ZK{`3}a;d;\ZK{`1}a v\ZK{`2}a:=+\ZK{`3}a;h;e\ZK{`2}a 
 `A\ZH{-12}{\ZK{`6}};Bye\ZV{8}{\ZH{-4}{\ZK{`4}}}a;Y3a;t\ZK{`3}a \ZS{2}:=\ZH{-6}{e}\ZH{-6}{\ZK{`1}}+B\ZK{`2}a;n,a\ZS{12}@A\ZS{6}@A}\\
%             ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}\\
Option selection: & +  & -- & {\skt  
 :pa;a;v\ZV{8}{\ZK{`3}}a;k\ZV{8}{\ZH{-12}{\ZK{`2}}}\ZS{3}H\ZS{4} :p\ZV{8}{\ZK{`3}}a;d;\ZV{8}{\ZK{`1}}a v\ZV{8}{\ZK{`2}}a:=+\ZV{8}{\ZK{`3}}a;h;e\ZV{8}{\ZK{`2}}a 
 `A\ZV{8}{\ZH{-12}{\ZK{`6}}};Bye\ZV{8}{\ZH{-4}{\ZK{`4}}}a;Y3a;t\ZV{8}{\ZK{`3}}a \ZS{2}:=\ZH{-6}{e}\ZV{8}{\ZH{-6}{\ZK{`1}}}+B\ZV{8}{\ZK{`2}}a;n,a\ZS{12}@A\ZS{6}@A}\\
%             ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}\\
\makebox[5mm][c]{+} = selected;      
                  & -- & +  & {\skt  
 :pa;a;v\ZV{12}{\ZK{`3}}a;k\ZV{12}{\ZH{-12}{\ZK{`2}}}\ZS{3}H\ZS{4} :p\ZV{12}{\ZK{`3}}a;d;\ZV{12}{\ZK{`1}}a v\ZV{12}{\ZK{`2}}a:=+\ZV{12}{\ZK{`3}}a;h;e\ZV{12}{\ZK{`2}}a 
 `A\ZV{12}{\ZH{-12}{\ZK{`6}}};Bye\ZV{12}{\ZH{-4}{\ZK{`4}}}a;Y3a;t\ZV{12}{\ZK{`3}}a \ZS{2}:=\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`1}}}+B\ZV{12}{\ZK{`2}}a;n,a\ZS{12}@A\ZS{6}@A}\\
%             ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}\\
\makebox[5mm][c]{--} = deselected;    
                  & +  & +  & {\skt  
 :pa;a;v\ZV{16}{\ZK{`3}}a;k\ZV{16}{\ZH{-12}{\ZK{`2}}}\ZS{3}H\ZS{4} :p\ZV{16}{\ZK{`3}}a;d;\ZV{16}{\ZK{`1}}a v\ZV{16}{\ZK{`2}}a:=+\ZV{16}{\ZK{`3}}a;h;e\ZV{16}{\ZK{`2}}a 
 `A\ZV{16}{\ZH{-12}{\ZK{`6}}};Bye\ZV{16}{\ZH{-4}{\ZK{`4}}}a;Y3a;t\ZV{16}{\ZK{`3}}a \ZS{2}:=\ZH{-6}{e}\ZV{16}{\ZH{-6}{\ZK{`1}}}+B\ZV{16}{\ZK{`2}}a;n,a\ZS{12}@A\ZS{6}@A}\\
%             ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}\\
\cline{2-4}
\end{tabular}{\skt }
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 6:} Enable {\skti \d Rg/Tait{\upshape$^\circ$}} accents in basic transliteration mode.
\end{minipage}}

The pre-processor treats the use of these accents in the basic transliteration
mode as as an error unless this option is selected.
The form of the accents approximates those of the {\skti devan\=agar\={\i}}.

Illustration: \hfill 
{\skt  ;Da;a;t\ZK{`8}a:=+a;y\ZK{`7}a;ntua .s\ZK{`8}a;vRa;t\ZK{`8}aH\ZS{4} .s1va;a;h;\ZH{-6}{\ZK{`7}}\ZH{-0}{\ZK{`7}}a\ZS{12}@A :pr\ZK{`8}a;Y3a;t\ZK{`8}a;ve\ZK{`8}a;Za;e\ZK{`7}a;Y6a;s\ZK{`8}a\ZS{12}@A 
 :pra ma;\ZK{`7}a :pa;d\ZM{fByF0E};a;s1ya\ZS{12}@A\ZS{6}@A}\\[.5mm]\hspace*{\fill}
{\skti dh\=at\ZA{2}{a}r\=ay\ZA{1}{a}ntu s\ZA{2}{a}rvat\ZA{2}{a}\d h sv\=ah\ZA{6}{\=a}{\upshape\,$\mid$} pr\ZA{2}{a}t\ZA{2}{i}v\ZA{2}{e}\'s\ZA{1}{o}s\ZA{2}{i}{\upshape\,$\mid$} 
 pra m\ZA{1}{\=a} padyasya{\upshape\,$\mid\mid$}}
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 7:} Enable {\skti S\=amaveda} etc.~accents in basic transliteration mode.
\end{minipage}}

The pre-processor treats the use of these accents in the basic transliteration
mode without this option selected, as as an error.
The form of the accents follows those of the {\skti devan\=agar\={\i}}, but in 
Roman script.

Illustration: \hfill
{\skt  m\ZV{8}{\ZK{`1}}a;Y2a;h\ZV{8}{\ZH{-6}{\ZK{`2}}};v.ra;t\ZV{8}{\ZK{`3}}aH\ZS{4} Z\ZV{8}{\ZK{`1}}ua;Y4a;.c\ZV{8}{\ZK{`2}}a;ba;nDuaH\ZS{4} 
 :pa;a;v\ZV{8}{\ZK{`3}}a;k\ZV{8}{\ZH{-12}{\ZK{`2}}}\ZS{3}H\ZS{4} :p\ZV{8}{\ZK{`3}}a;d;\ZV{8}{\ZK{`1}}a v\ZV{8}{\ZK{`2}}a:=+\ZV{8}{\ZK{`3}}a;h;e\ZV{8}{\ZK{`2}}a 
 `A\ZV{8}{\ZH{-12}{\ZK{`6}}};Bye\ZV{8}{\ZH{-4}{\ZK{`4}}}a;Y3a;t\ZV{8}{\ZK{`3}}a \ZS{2}:=\ZH{-6}{e}\ZV{8}{\ZH{-6}{\ZK{`1}}}+B\ZV{8}{\ZK{`2}}a;n,a\ZS{12}@A\ZS{6}@A}\\[1mm]\hspace*{\fill}
{\skti m\ZA{9}{a}h\ZA{10}{i}vrat\ZA{11}{a}\d h \'s\ZA{9}{u}c\ZA{10}{i}bandhu\d h 
 p\=av\ZA{11}{a}k\ZA{10}{a}\d h p\ZA{11}{a}d\ZA{9}{\=a} v\ZA{10}{a}r\ZA{11}{\=a}h\ZA{10}{o} 
 \ZA{14}{a}bhy\ZA{12}{e}t\ZA{11}{i} r\ZA{9}{e}bh\ZA{10}{a}n{\upshape\,$\mid\mid$}}
%{\skt  a<2>gna<3> aa<1> yaa<2>hi vii<3>ta<1>ye<2> g.r.naa<3>no<2>
%        ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}\\
%{\skti a<2>gna<3> aa<1> yaa<2>hi vii<3>ta<1>ye<2> g.r.naa<3>no<2>
%        ha<3k>vyadaa<2>taye ni<2r> hotaa<2r> satsi va<3>hi<1>si<2>}
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 8:} Enable {\skti sa\d myoga} warnings.
\end{minipage}}

This enables the printing of warning messages by the pre-processor when using
a {\skti vir\=ama} in forming a {\skti sa\d myoga}. Given the range of 
{\skti sa\d myoga} supported by the font, this warning should only occur
with very exotic syllables.
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 9:} Enable obey-lines.
\end{minipage}}

Long lines to the output file are normally wrapped to limit their length to 
eighty characters (i.e.~the output file will have more lines than the input
file), but with this option enabled the output follows the input, line
for line, irrespective of the resultant line length: a warning message will
be printed if the line length exceeds 250 characters. It is helpful to have 
obey-lines active so that \LaTeX\ errors refer to the source line number of 
the \verb+.skt+ file.

\pagebreak

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 10:} Enable discretionary hyphens.
\end{minipage}}

Without this option enabled, the pre-processor will discard any discretionary
hyphens, \verb+\-+, in the input text.
\vfill

\framebox[\textwidth]{\hspace*{5mm}\begin{minipage}{130mm}
{\bf Option 11:} Enable auto-hyphenation.
\end{minipage}}

\vspace{1mm}

The auto-hyphenation is extremely crude (it adds a discretionary hyphen
after every vowel!), and should only be used for drafts.

\section{Transliteration Options (20--38)}%
%
The following table illustrates the transliteration options available:\\[2mm]
\renewcommand{\arraystretch}{1}
\begin{tabular}{|c|c|c|c|c|}
\cline{1-4} option & input & default & option & \multicolumn{1}{c}{}\\
\cline{1-4}
20 & \verb+a~m+ & {\skti a\d{\~m}} & {\skti a\d m} & \multicolumn{1}{c}{}\\
21 & \verb+a~m+ & {\skti a\d{\~m}} & {\skti a\.m} & \multicolumn{1}{c}{}\\
22 & \verb+a.m+ & {\skti a\d m} & {\skti a\.m} & \multicolumn{1}{c}{}\\
23 & \verb+a"m+ & {\skti a\.m} & {\skti a\d m} & \multicolumn{1}{c}{}\\
\hline
24 & \verb+a"m+ & {\skti a\.m} & {\skti a\b n} & \\
25 & \verb+.r/.r.r+  & {\skti r\llap{\d{\kern.51em}}/\=r\llap{\d{\kern.51em}}}  & {\skti r\llap{\d{\kern.51em}}i/r\llap{\d{\kern.51em}}\={\i}} & 
  Monier-Williams\\
26 & \verb+.l/.l.l+  & {\skti \d l/\,\d{\=l}}  & {\skti lr\llap{\d{\kern.51em}}i/\,lr\llap{\d{\kern.51em}}\={\i}} & \\
27 & \verb+"s+  & {\skti \'s}  & {\skti \.s} & 
  transliteration\\
28 & \verb+.s+  & {\skti \d s}  & {\skti sh} & 
  scheme\\
29 & \verb+"d+  & {\skti \ZZ d}  & {\skti \d l} & \\
\hline
30 & \verb+"d+  & {\skti \ZZ d}  & {\skti \b l} & \multicolumn{1}{c}{}\\
31 & \verb+"d+  & {\skti \ZZ d}  & {\skti \b d} & \multicolumn{1}{c}{}\\
32 & \verb+"h+  & {\skti \ZZ h}  & {\skti \b h} & \multicolumn{1}{c}{}\\
33 & \verb+.o+  & {\skti O\~m}  & {\skti Om} & 
  \multicolumn{1}{c}{Where multiple options apply}\\
34 & \verb+.o+  & {\skti O\~m}  & {\skti O{\relsize{-3}M}} & 
  \multicolumn{1}{c}{to the same input (e.g.~33--37)}\\
35 & \verb+.o+  & {\skti O\~m}  & {\skti OM} & 
  \multicolumn{1}{c}{the highest value of selected}\\
36 & \verb+.o+  & {\skti O\~m}  & {\skti A{\relsize{-3}UM}} & 
  \multicolumn{1}{c}{option will apply.}\\
37 & \verb+.o+  & {\skti O\~m}  & {\skti AUM} & \multicolumn{1}{c}{}\\
38 & \verb+a#+  & {\skti \ZA{30}{a}}  & {\skti \ZA{60}{a}} & \multicolumn{1}{c}{}\\
\cline{1-4}
\end{tabular}
\vspace{2mm}

The last option has a twofold application: firstly, depending on the font
and size used, it may be used to overcome the difficulty distinguishing
between the macron and the tilde (i.e.~{\skti \=a \ZA{30}{a} \ZA{60}{a}\/}); and
secondly, it may be used in technical grammar to indicate an explicit
short vowel ({\sktt \ZA{60}{a}}) or long or short ({\sktt \ZA{60}{\=a}})

\pagebreak

\section{{\sktX Devan\=agar\={\i}} Character Options (40--79)}%
%
The table illustrates the basic character forms available: where multiple
options apply to the same input (e.g.~65 and~75) the selected option
with the highest value will apply. Although {\sktX k\d sa} and {\sktX j\~na}
are strictly speaking {\skti sa\d myoga}, they are nevertheless included here 
rather than in the next section.

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
40 & \verb+a+    & {\skt A}    & {\skt `A } \\
41 & \verb+.r+   & {\skt `x}   & {\skt `r } \\
42 & \verb+jha+  & {\skt Ja}  & {\skt `J } \\
43 & \verb+"da+  & {\skt L}  & {\skt L2a } \\
44 & \verb+.na+  & {\skt :Na}  & {\skt .`Na } \\
45 & \verb+tha+  & {\skt Ta}  & {\skt `Ta } \\
46 & \verb+la+   & {\skt l}   & {\skt l1a } \\
47 & \verb+a~m+  & {\skt A\ZS{1}>}  & {\skt A\ZS{3}.gM,a } \\
48 & \verb+a~m+  & {\skt A\ZS{1}>}  & {\skt A`> } \\
49 & \verb+k.sa+ & {\skt [a} & {\skt `[a } \\
50 & \verb+j~na+ & {\skt :]a} & {\skt `]a } \\
51 & \verb+"s+  & {{}\skt (}  & {{}\skt )            } \\
52 & \verb+"s.r+ & {\skt Zxa} & {\skt (\ZV{4}{x}a } \\\hline
\end{tabular}
\hfill
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
61 & \verb+1+    & {\skt 1}    & {\skt @1 } \\
   &             &             &                        \\
64 & \verb+4+    & {\skt 4}    & {\skt @4 } \\
65 & \verb+5+    & {\skt 5}    & {\skt @5 } \\
66 & \verb+6+    & {\skt 6}    & {\skt @6 } \\
   &             &             &                        \\
68 & \verb+8+    & {\skt 8}    & {\skt @8 } \\
69 & \verb+9+    & {\skt 9}    & {\skt @9 } \\
   &             &             &                        \\
75 & \verb+5+    & {\skt 5}    & {\skt @0 } \\
   &             &             &                        \\
79 & \verb+9+    & {\skt 9}    & {\skt @2 } \\\hline
\end{tabular}
\vfill

\section{{\sktX Devan\=agar\={\i} Sa\d myoga\/} Options (100--199)}%
%
The table illustrates the basic {\skti sa\d myoga\/} options available.
In general, the default {\skti sa\d myoga\/} is the most compact, and the 
options use a looser form: the latter may be easier to read, particularly
when the combination is more unusual.

In forming a complex {\skti sa\d myoga} two or more options may interact:
for example, in forming the {\skti sa\d myoga} for {\sktX ktya}, options~103 
and~108 both come into play so that there are three possibilities
(\,{\skt k2y2+.a k2:y1a k1tya}\,).
The {\skti Sa\d myoga\/} Table at the end of this document illustrates all
varieties available.

For those {\skti sa\d myoga\/} where it may appear preferable to use a 
{\skti vir\=ama} (typically those beginning with {\skt .z f F .q}
or {\skt Q}\,), braces may be used. For example,\vspace{1mm}\linebreak
\verb+{+\verb+\skt a"nk.s.na a{"n}k.s.na}+ produces
{\skt A:*\ZM{p0xdPqLOMbbNbBILBELdEd0a}* A{;z\ZH{-12}{,}}+[Na}.

\pagebreak

\renewcommand{\arraystretch}{1.05}
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
101 & \verb+kka+   & {\skt \ZM{0NkLNPLPE00kL0PLhA}*:}    & {\skt k1k } \\
102 & \verb+k"na+  & {\skt \ZM{0NkLNPLPELNE00qP0M}*;}   & {\skt k1z } \\
103 & \verb+kta+   & {\skt k2}    & {\skt k1ta } \\
104 & \verb+ktra+  & {\skt k2\ZP{-10}{-2}{r1}}   & {\skt k1+t4a } \\
105 & \verb+ktva+  & {\skt k3}   & {\skt k1tva } \\
106 & \verb+kna+   & {\skt \ZM{0NkLNPLPE0DnLDE}*:}    & {\skt k1na } \\
107 & \verb+kma+   & {\skt k4}    & {\skt k1ma } \\
108 & \verb+kya+   & {\skt ky2+.a}    & {\skt k1ya } \\
109 & \verb+kla+   & {\skt \ZM{0NkLNPLPELFI00l}*:}    & {\skt k1l } \\
110 & \verb+kva+   & {\skt \ZM{0NkLNPLPE00kLhA}*:}    & {\skt k1va } \\
111 & \verb+khna+  & {\skt \ZM{0NKFRIDbnMbeRbE}*.a}   & {\skt K.na } \\
112 & \verb+gna+   & {\skt \ZM{0NgFRI0FnIFe}+;a}    & {\skt gna } \\
113 & \verb+ghna+  & {\skt \ZM{BNHMDeDDnR0ARbA}*+}   & {\skt ;Gna } \\
114 & \verb+cca+   & {\skt c1a}    & {\skt ..cca } \\
115 & \verb+c~na+  & {\skt \ZM{0JcBBzRdA}*.a}   & {\skt ..c.Va } \\
116 & \verb+cna+   & {\skt \ZM{0JcDDnMDeRDE}*.a}    & {\skt ..cna } \\
117 & \verb+chma+  & {\skt \ZM{0PCDbmQbiXbEJ0I}*+a}   & {\skt C.m2a } \\
118 & \verb+chya+  & {\skt C1}   & {\skt C.y1a } \\
119 & \verb+jja+   & {\skt \ZM{0Jj0djRdA}*.a}    & {\skt j2a } \\
120 & \verb+jna+   & {\skt \ZM{0JjDDnMDeRDE}*.a}    & {\skt .j1na } \\
121 & \verb+~nca+  & {\skt \ZM{BNz0dcRfA}*.a}   & {\skt Vca } \\
122 & \verb+~nja+  & {\skt \ZM{BNz0djR0ARdA}*+}   & {\skt V\ZS{-6}ia } \\
123 & \verb+~n~na+ & {\skt \ZM{0Oz0BzPBE}*a}  & {\skt VVa } \\
124 & \verb+~nna+  & {\skt \ZM{0OzBFnKFe}*a}   & {\skt Vna } \\
125 & \verb+.tma+  & {\skt \ZM{0PfB0mQ0eV0E}*;a}   & {\skt fm2a } \\
126 & \verb+.thma+ & {\skt \ZM{0PFB0mQ0eV0E}*;a}  & {\skt F:m2a } \\
127 & \verb+.thya+ & {\skt F:y3a}  & {\skt Fy1a } \\
128 & \verb+.dma+  & {\skt \ZM{0PqDbmObiVbE}*;a}   & {\skt q:m2a } \\
129 & \verb+.dya+  & {\skt q:y3a}   & {\skt qy1a } \\
130 & \verb+.dhma+ & {\skt \ZM{0PQB0mO0eT0E}*:a}  & {\skt Q.m2a } \\
131 & \verb+.dhya+ & {\skt Q.y3a}  & {\skt Qy1a } \\
132 & \verb+.nna+  & {\skt :\ZM{DBnMBeRdI}Na}   & {\skt :Nna } \\
133 & \verb+.nra+  & {\skt :N.=}   & {\skt :N@Ra } \\
134 & \verb+tta+   & {\skt t1a}    & {\skt tta } \\
135 & \verb+tna+   & {\skt t2a}    & {\skt tna } \\
\hline
\end{tabular}
\hfill
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
136 & \verb+thna+   & {\skt T\ZM{pBneBe0BE}a}   & {\skt Tna } \\
137 & \verb+ddya+   & {\skt d1\ZM{dbyHbE}+a}   & {\skt d1y1a } \\
138 & \verb+ddvya+  & {\skt d1\ZM{oekdbyHbE}+a}  & {\skt d1\ZM{oek}y1a } \\
139 & \verb+ddhma+  & {\skt .;d2\ZM{tBDjhmCheHnAdbE}+a}  & {\skt .;d\ZM{t0Dj0b}m2a } \\
140 & \verb+ddhya+  & {\skt .;d\ZM{t0DfByF0E};a}  & {\skt .;d\ZM{t0Dj0b}y1a } \\
141 & \verb+dbhya+  & {\skt .;d\ZM{x0Bi0efByF0E};a}  & {\skt .;d2\ZM{x0Bi0ed0E}y1a } \\
142 & \verb+dma+    & {\skt d2\ZM{j0mC0eH0E}+a}    & {\skt dm2a } \\
143 & \verb+dya+    & {\skt d\ZM{fByF0E};a}    & {\skt dy1a } \\
144 & \verb+dhna+   & {\skt \ZM{0XiBNHMXeDDnRDENXiKDi}\ZS{14}:a}   & {\skt ;Dna } \\
145 & \verb+nca+    & {\skt \ZM{00cBRnMRe}*.a}    & {\skt n.ca } \\
146 & \verb+nja+    & {\skt \ZM{00jDRnKRi}*.a}    & {\skt n\ZS{-6}ia } \\
147 & \verb+nna+    & {\skt n1a}    & {\skt \ZM{0Rn0HnIReIHe}+;a } \\
148 & \verb+pta+    & {\skt p1a}    & {\skt :pta } \\
149 & \verb+pna+    & {\skt :p\ZM{lBn0BE}a}    & {\skt :pna } \\
150 & \verb+pla+    & {\skt :p\ZM{lbl0FI0PE};}    & {\skt :pl } \\
151 & \verb+phna+   & {\skt :P\ZM{vBnjBE}}   & {\skt :P1na } \\
152 & \verb+phya+   & {\skt :Py2+.a}   & {\skt :P1ya } \\
153 & \verb+bna+    & {\skt \ZM{0Ok0Ob0FnIFe}+;a}    & {\skt b.na } \\
154 & \verb+bba+    & {\skt \ZM{0Ok0Ob0Bk0BbNdA}+;a}    & {\skt b.ba } \\
155 & \verb+bva+    & {\skt \ZM{0Ok0Ob0BkNdA}+;a}    & {\skt b.va } \\
156 & \verb+bhna+   & {\skt B\ZM{jFncLe}.a}   & {\skt Bna } \\
157 & \verb+mna+    & {\skt m1\ZM{hFnaLe}:a}    & {\skt m1\ZM{cLe}.na } \\
158 & \verb+mla+    & {\skt m1\ZM{aLeDPEDFIhBl}+}    & {\skt m1l } \\
159 & \verb+yna+    & {\skt y\ZM{nBneBe0BE}a}    & {\skt yna } \\
160 & \verb+lla+    & {\skt l2}    & {\skt l1l } \\
161 & \verb+vna+    & {\skt \ZM{0Ok0FnIFeN0A}+;a}    & {\skt v.na } \\
162 & \verb+vva+    & {\skt \ZM{0Ok0BkNdA}+;a}    & {\skt v.va } \\
163 & \verb+"sca+   & {\skt (\ZM{rac0FI}a}   & {\skt Z.ca } \\
164 & \verb+"sna+   & {\skt (\ZM{pFngFi}a}   & {\skt Zna } \\
165 & \verb+"sla+   & {\skt (\ZM{lBl0FI0PE};}   & {\skt Zl } \\
166 & \verb+"sva+   & {\skt (\ZM{dGu};a}   & {\skt Zva } \\
167 & \verb+.s.ta+  & {\skt :S1}  & {\skt :Sf } \\
168 & \verb+.s.tha+ & {\skt :S2} & {\skt :SF } \\
169 & \verb+.sna+   & {\skt :S\ZM{lBn0dI}a}   & {\skt :Sna } \\
170 & \verb+sna+    & {\skt .=+:\ZM{rMolHneHegMi}a}    & {\skt .s1na } \\
\hline
\end{tabular}
\vspace{5mm}

\clearpage

\setlength{\unitlength}{1mm}
\begin{picture}(136,192)
\put(0,151.5){\begin{minipage}{69mm}
\renewcommand{\arraystretch}{1}
\begin{tabular}{|c|p{47.5mm}|}
\hline option & function \\\hline
 0 & Set all to known state \\
 1 & Intraspace $<$ interspace \\
 2 & Reduce interspace \\
 3 & Minimum interspace \\
 4 & Raise accents (lsb) \\
 5 & Raise accents (msb) \\
 6 & Enable {\skti \d Rg\//Tait{\upshape$^\circ$}} accents\linebreak\hspace*{\fill} in 
     basic transliteration \\
 7 & Enable {\skti S\=ama{\upshape$^\circ$}} etc.~accents \linebreak\hspace*{\fill} in 
     basic transliteration \\
 8 & Enable {\skti sa\d myoga\/} warnings \\
 9 & Enable obey-lines \\
10 & Enable discr.~hyphens \\
11 & Enable auto-hyphenation\\
\hline
\end{tabular}
\end{minipage}
}
\put(0,56){\begin{minipage}{69mm}
\renewcommand{\arraystretch}{1}
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
20 & {\tt a\raisebox{-.35ex}{\tt \~\null}m}
               & {\skti a\d{\~m}} & {\skti a\d m } \\
21 & {\tt a\raisebox{-.35ex}{\tt \~\null}m}
               & {\skti a\d{\~m}} & {\skti a\.m } \\
22 & {\tt a.m} & {\skti a\d m} & {\skti a\.m } \\
23 & {\tt a"m} & {\skti a\.m} & {\skti a\d m } \\
24 & {\tt a"m} & {\skti a\.m} & {\skti a\b n } \\
25 & {\tt .r/.r.r}  & {\skti r\llap{\d{\kern.51em}}/\=r\llap{\d{\kern.51em}}}  & {\skti r\llap{\d{\kern.51em}}i/r\llap{\d{\kern.51em}}\={\i} } \\
26 & {\tt .l/.l.l}  & {\skti \d l/\d{\=l}}  & {\skti lr\llap{\d{\kern.51em}}i/lr\llap{\d{\kern.51em}}\={\i} } \\
27 & {\tt "s}  & {\skti \'s}  & {\skti \.s } \\
28 & {\tt .s}  & {\skti \d s}  & {\skti sh } \\
29 & {\tt "d}  & {\skti \ZZ d}  & {\skti \d l } \\
30 & {\tt "d}  & {\skti \ZZ d}  & {\skti \b l } \\
31 & {\tt "d}  & {\skti \ZZ d}  & {\skti \b d } \\
32 & {\tt "h}  & {\skti \ZZ h}  & {\skti \b h } \\
33 & {\tt .o}  & {\skti O\~m}  & {\skti Om } \\
34 & {\tt .o}  & {\skti O\~m}  & {\skti O{\relsize{-3}M} } \\
35 & {\tt .o}  & {\skti O\~m}  & {\skti OM } \\
36 & {\tt .o}  & {\skti O\~m}  & {\skti A{\relsize{-3}UM} } \\
37 & {\tt .o}  & {\skti O\~m}  & {\skti AUM } \\
38 & {\tt a\#}  & {\skti \ZA{30}{a}}  & {\skti \ZA{60}{a} } \\
\hline
\end{tabular}
\end{minipage}
}
\put(71,122){\begin{minipage}{63mm}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|c|}
\hline option & input & default & option \\\hline
40 & {\tt a}    & {\skt A}    & {\skt `A } \\
41 & {\tt .r}   & {\skt `x}   & {\skt `r } \\
42 & {\tt jha}  & {\skt Ja}  & {\skt `J } \\
43 & {\tt "da}  & {\skt L}  & {\skt L2a } \\
44 & {\tt .na}  & {\skt :Na}  & {\skt .`Na } \\
45 & {\tt tha}  & {\skt Ta}  & {\skt `Ta } \\
46 & {\tt la}   & {\skt l}   & {\skt l1a } \\
47 & {\tt a\raisebox{-.35ex}{\tt \~\null}m}
                & {\skt A\ZS{1}>}  & {\skt A\ZS{3}.gM,a } \\
48 & {\tt a\raisebox{-.35ex}{\tt \~\null}m}
                & {\skt A\ZS{1}>}  & {\skt A`> } \\
49 & {\tt k.sa} & {\skt [a} & {\skt `[a } \\
50 & {\tt j\raisebox{-.35ex}{\tt \~\null}na}
                & {\skt :]a} & {\skt `]a } \\
51 & {\tt "s}   & {{}\skt (}  & {{}\skt )            } \\
52 & {\tt "s.r} & {\skt Zxa} & {\skt (\ZV{4}{x}a } \\
61 & {\tt 1}    & {\skt 1}    & {\skt @1 } \\
64 & {\tt 4}    & {\skt 4}    & {\skt @4 } \\
65 & {\tt 5}    & {\skt 5}    & {\skt @5 } \\
66 & {\tt 6}    & {\skt 6}    & {\skt @6 } \\
68 & {\tt 8}    & {\skt 8}    & {\skt @8 } \\
69 & {\tt 9}    & {\skt 9}    & {\skt @9 } \\
75 & {\tt 5}    & {\skt 5}    & {\skt @0 } \\
79 & {\tt 9}    & {\skt 9}    & {\skt @2 } \\\hline
\end{tabular}
\end{minipage}
}
\put(71,40){\begin{minipage}{63mm}
{\smaller Where an input has multiple options,\\
the highest value selected will apply.}
\end{minipage}
}
\put(71,6){\frame{\begin{minipage}{62mm}
\begin{center}
\textbf{{\Large SKT Options\rule{0mm}{7mm}}\\
{\large Summary Sheet\rule[-3mm]{0mm}{9mm}}}
\end{center}
\end{minipage}}
}
\end{picture}

\clearpage

\section{The Pre-processor: skt.c}%
%
This ANSI C program processes the source text file (with a default \verb+.skt+
filename extension) to produce a file suitable for \LaTeXe\ (with a default
\verb+.tex+ extension). For example, the command \verb+skt test+ will convert
\verb+test.skt+ to \verb+test.tex+; fuller filenames may be used, 
e.g.~\verb+skt foo.bar+ will produce \verb+foo.tex+, and 
\verb+skt foo.bar far.boo+ will produce \verb+far.boo+ from \verb+foo.bar+.
If no filename is specified, you will be prompted for input and output
filenames.

The program passes the text from the input file to the output file
unaltered, until it finds the string `\verb+{+\verb+\skt+'. 
It then checks the following character(s) for the acceptable modifiers
\verb+b f s bs fs x X i I t T u+ or \verb+U+, and this must be followed by
a space character: if this test fails it reports an error, otherwise
the program converts the following input text to {\skti devan\=agar\={\i}\/}
or transliteration format as required, until the matching `\verb+}+'.
The cycle is then repeated.

Within the \verb+skt+ text, the following punctuation characters will be
passed to the output as roman:\label{ref:punct}

\begin{center}
\framebox{\texttt{ ( ) * + , - / : ; = ? }}
\end{center}

Furthermore, two successive periods `..' will be passed to the output as 
a single roman period.  This technique of repeating the character twice 
to produce a single roman character applies to the four characters [`'] 
as well; and the two-character string `.!' will pass through as a single 
roman exclamation mark.  You will need to use \verb+{+\verb+\sktx ``a'{}''}+
to produce {\sktx `\ZA{8}{a}'} (see Supplementary Notes for explanation).

\LaTeX\ command strings embedded within the \verb+skt+ text will be
passed to the output file unchanged\,---\,but beware: command parameters
will be converted\,! Thus commands without parameters (e.g.~\verb+\clearpage+)
are safe, but commands with parameters (e.g.~\verb+\hspace{3mm}+) will
cause problems unless the parameters are meant to be converted
(e.g.~\verb+\underline{naaman}+).

A complete list of the input encoding scheme, together with the resultant
{\skti devan\=agar\={\i}\/} and transliterated output, is included at the end
of this document.
\vfill

\begin{center}
\framebox{\begin{minipage}{100mm}
\textbf{Note: }This program will stop passing text to the output file
as soon as an error in the source file is detected; it will however,
continue processing the input file until ten or more errors are 
encountered.
\end{minipage}}
\end{center}

\pagebreak

\section{The skt package: skt.sty}%
%
The following statement needs to be in the preamble of the document:\\
\verb+\usepackage[options]{skt}+\\
where `options' may be any or all or none of the following:

\textbf{larger} This will cause all {\skti devan\=agar\={\i}\/} text to be 
                printed at a larger size than\newline\hspace*{14mm}the 
                prevailing environment.

\textbf{xitalic} Text transliterated by \verb+sktx+ or \verb+sktX+ will
                use the italic font \verb+cmmit+;\newline\hspace*{14mm}the 
                default is the upright \verb+cmr+ font.

\textbf{iitalic} As for \verb+xitalic+, but using \verb+skti+ and \verb+sktI+.

\textbf{titalic} As for \verb+xitalic+, but for the technical modes 
                \verb+sktt+ and \verb+sktT+.

\textbf{uitalic} As for \verb+titalic+, but using \verb+sktu+ and \verb+sktU+.

This document uses the first, third, and fifth options, that is to say 
it has the statement
\verb+\usepackage[larger,iitalic,uitalic]{skt}+.

This style file also allows page numbering to be in {\skti devan\=agar\={\i}\/}
by using the \LaTeX\ command \verb+\pagenumbering{skt}+\,---\,as has been
done for this document. The size of the numerals will follow the `larger'
option.

This package makes use of David Carlisle's \verb+ifthen.sty+ which is
included in the standard \LaTeXe\ distribution, and Donald Arseneau's 
\verb+relsize.sty+ which you may need to get from the CTAN archives.
\vspace{5mm}

\section{Supplementary Notes}%
%
The program can be simply `fooled' when necessary by inserting a 
\LaTeX\ null string `\verb+{}+': for example `\verb+{{}\skt >}+' will
not be `seen' by the pre-processor and thus passed to the output unchanged.
\LaTeX\ will ignore the null string but respond to the \verb+\skt+ command
and print {{}\skt >} (which is the {\skti devan\=agar\={\i}\/} character in the
position of the ASCII `\verb+>+' character). 
(A map of the font and access codes is included at the end of this document.)
This requirement may arise (as for example in producing the font map) because
the pre-processor requires that there be a vowel before an accent or
{\skti anusv\=ara}.

\dotrule
%\pagebreak

For those rare words that have two successive vowels in {\skti devan\=agar\={\i}\/} 
(such as in {\skt :pra;\ZS{-2}o+.ga}) that the pre-processor would misinterpret
(and this only applies to the combinations {\skti au\/} and {\skti ai\/} 
which the encoding scheme defines as single vowels, producing {\skt :pra;Ea;ga}
for example), there are three ways to fool the pre-processor;
only the first of these is carried through to the transliteration modes:

\verb+{+\verb+\skt a{}iu.n| .r.lk| eo"n| aiauc|| pra{}uga pra{uga} pra%+\\
\verb+uga||}+\\[2mm]
Note that, for the third method, there must be a \verb+newline+ immediately 
after the \verb+%+\,---\,this is the \TeX\ line continuation method.

{\skt A;I+.\ZS{-2}o+.N,a\ZS{12}@A `x+.`w+.k\ZH{-12}{,}\ZS{12}@A O;\ZS{2}A;ea;z\ZH{-12}{,}\ZS{12}@A Oe;\ZS{2}A;Ea;.c,a\ZS{12}@A\ZS{6}@A
:pra;\ZS{-2}o+.ga :pra{;\ZS{-2}o+.ga} :pra%
;\ZS{-2}o+.ga\ZS{12}@A\ZS{6}@A}

{\skti a\ZS{1}\raisebox{.4ex}{.}\ZS{-1}i\ZS{1}\raisebox{.4ex}{.}\ZS{-1}u\d n{\upshape\,$\mid$} r\llap{\d{\kern.51em}}\ZS{1}\raisebox{.4ex}{.}\ZS{-1}\d lk{\upshape\,$\mid$} 
e\ZS{1}\raisebox{.4ex}{.}\ZS{-1}o\.n{\upshape\,$\mid$} ai\ZS{1}\raisebox{.4ex}{.}\ZS{-1}auc{\upshape\,$\mid\mid$}
pra\ZS{1}\raisebox{.4ex}{.}\ZS{-1}uga pra{uga} pra%
uga{\upshape\,$\mid\mid$}}

The same trick may be used to split any multicharacter input, provided
that what is either side of the \verb+{}+ is still valid, for example:\\
\verb+{+\verb+\skt tha t{}ha}+ produces \ {\skt Ta th}.

\dotrule

Some \LaTeX\ commands are `fragile' and balk at having {\bf skt} commands within
their arguments, e.g.~\verb+\section{\+\verb+skt bahuvriihi}+ produces the 
error message \verb+Undefined Control Sequence+.
To get around this sort of problem, define the {\bf skt} argument outside the
fragile command, e.g.\\
\verb+\newcommand{\bahuvriihi}{\+\verb+skt bahuvriihi}+\\
\verb+\section{\protect\bahuvriihi}+

\dotrule

Finally, the simplest method of producing larger sizes of the font is to
add the command \verb+\DeclareFixedFont{\bigskt}{OT1}{skt}{m}{n}{46mm}+ for example, in the
preamble to the document, and then use \verb+{+\verb+\skt \bigskt tattvamasi}+
in the text body. The result (in `lightgray' to save ink) is:
\vfill
\nopagebreak%
{\skt {\lightgray \bigskt tat1va.ma.Y4a.sa}}

\section{Installation}%
%
If \verb+sktbugxx.txt+ files exist, you may want to implement
any changes or patches first.

Run the \MF{} program on the eight font source files (the typical 
command would be \verb+mf "\mode=ljfour; mag=1; input skt8;"+)
to produce the \verb+.tfm+ files. 
If you are using \verb+dvips+, then the \verb+.pk+ files will be produced 
automatically on demand; if not, then you will need to (1) Convert the
\verb+.gf+ files with the command \verb+gftopk skt8.600gf+ (the number `600' 
depends upon your printer resolution and the magnification) to produce
\verb+skt8.600pk+ which must be placed in the appropriate subdirectory. 
(2) Repeat this process with all eight fonts.
(3) For the six \verb+skt*10.mf+ files the whole process needs 
to be repeated with the \verb+mag+ value in the \verb+mf+ 
command set to 1.095, 1.2, 1.44, 1.728, 2.074 and 2.488.

The \verb+mf_inputs+ path needs to point to the files with a \verb+.mf+ 
extension; the \verb+tex_fonts+ path should point to the \verb+.tfm+ files;
the \verb+tex_inputs+ path should point to the files 
\verb+skt.sty+ and \verb+ot1skt.fd+.
The \verb+tex_exe+ (or other appropriate) path should point to \verb+skt.exe+.

To test the setup on this documentation file: first run the pre-processor 
\verb+skt sktdoc+ and then \verb+latex sktdoc+. 
The files \verb+ifthen.sty+, \verb+relsize.sty+ and \verb+multicol.sty+ 
are also required.

The files in this package are:

\textbf{readme.txt} An ASCII version of these installation notes and part
                    of the\newline\hspace*{22mm}introduction.

\textbf{skt.sty} Style file (\LaTeXe) for the skt-series fonts.

\textbf{ot1skt.fd} Font descriptor file for the skt-series fonts.

\textbf{skt.c} Pre-processor source program in ANSI C.

\textbf{sktdoc.skt} Source file of documentation and samples.

\textbf{sktdefs.mf} Common definitions of pens, macros, etc.~for 
                    skt-series fonts.

\textbf{sktchars.mf} Common character source file for skt-series fonts.

\textbf{sktligs.mf} Ligature codes (in fact access codes for non-printing
                    ASCII code\newline\hspace*{22mm}characters) for 
                    the skt-series fonts.

\textbf{skt8.mf} \MF{} source file for skt font at 8pt upright.

\textbf{skt9.mf} \MF{} source file for skt font at 9pt upright.

\textbf{skt10.mf} \MF{} source file for skt font at 10pt upright.

\textbf{sktb10.mf} \MF{} source file for skt font at 10pt bold upright.

\textbf{sktf10.mf} \MF{} source file for skt font at 10pt feint upright.

\textbf{skts10.mf} \MF{} source file for skt font at 10pt slanted.

\textbf{sktbs10.mf} \MF{} source file for skt font at 10pt bold slanted.

\textbf{sktfs10.mf} \MF{} source file for skt font at 10pt feint slanted.

\textbf{skt*.tfm} Eight \verb+.tfm+ font files for above.

\textbf{sktbugxx.txt} There may be a series of such files, where `\verb+xx+'
                      is a two-digit\newline\hspace*{22mm}number, listing 
                      reported bugs and (possibly) fixes or patches.
\vspace{5mm}

Suggestions and bug reports to: \verb+vhaisman@gmail.com+

\vfill

\clearpage

\setlength{\unitlength}{1mm}
\begin{picture}(136,192)
\put(0,130.5){\begin{minipage}{50mm}
\renewcommand{\arraystretch}{1.2}
\addtolength{\tabcolsep}{-.7mm}
\begin{tabular}{|c|c|c|}
\hline
{\small input} & {\small skt} & {\small skti} \\
\hline
{\tt a}    & {\skt A} or implicit                    & {\skti a}          \\
{\tt aa}   & {\skt A.a} or {{}\skt ;a}                & {\skti \=a}         \\
{\tt i}    & {\skt I} or {{}\skt ;i8a}               & {\skti i}          \\
{\tt ii}   & {\skt I\ZH{-6}{R}} or \hspace*{1mm} {{}\skt i8\ZS{10};a} & {\skti \={\i}} \\
{\tt u}    & {\skt o} or \hspace*{1mm} {{}\skt u}    & {\skti u}          \\
{\tt uu}   & {\skt `o} or \hspace*{1mm} {{}\skt U}   & {\skti \=u}         \\
{\tt .r}   & {\skt `x} or \hspace*{1mm} {{}\skt x}   & {\skti r\llap{\d{\kern.51em}}}         \\
{\tt .r.r} & {\skt `X} or \hspace*{1mm} {{}\skt X} & {\skti \=r\llap{\d{\kern.51em}}}       \\
{\tt .l}   & {\skt `w} or \hspace*{1mm} {{}\skt w}   & {\skti \d l}         \\
{\tt .l.l} & {\skt `W} or \hspace*{1mm} {{}\skt W} & {\skti \d{\=l}}       \\
{\tt e}    & {\skt O;} or \hspace*{1mm} {{}\skt e}    & {\skti e}          \\
{\tt ai}   & {\skt Oe;} or \hspace*{1mm} {{}\skt E}   & {\skti ai}         \\
{\tt o}    & {\skt A.ea} or \hspace*{1mm} {{}\skt *ea}  & {\skti o}          \\
{\tt au}   & {\skt A.Ea} or \hspace*{1mm} {{}\skt *Ea} & {\skti au}         \\
{\tt a.m}  & {\skt A\ZH{-6}{M}}                              & {\skti a\d m}        \\
{\tt a"m}  & {\skt A\ZH{-6}{M}}                              & {\skti a\.m}        \\
{\tt a\raisebox{-.35ex}{\tt \~\null}m}
           & {\skt A>}                              & {\skti a\d{\~m}}        \\
{\tt a.h}  & {\skt AH\ZS{2}}                              & {\skti a\d h}        \\
\hline
\end{tabular}
\end{minipage}
}
\put(57,102){\begin{minipage}{35mm}
\renewcommand{\arraystretch}{1.03}
\begin{tabular}{|c|c|c|}
\hline
{\small input} & {\small skt} & {\small skti} \\
\hline
{\tt ka}      & {\skt k}   & {\skti ka}   \\
{\tt kha}     & {\skt Ka}  & {\skti kha}  \\
{\tt ga}      & {\skt ga}   & {\skti ga}   \\
{\tt gha}     & {\skt ;Ga}  & {\skti gha}  \\
{\tt "na}     & {\skt .z}  & {\skti \.na}  \\
{\tt ca}      & {\skt ..ca}   & {\skti ca}   \\
{\tt cha}     & {\skt C}  & {\skti cha}  \\
{\tt ja}      & {\skt .ja}   & {\skti ja}   \\
{\tt jha}     & {\skt Ja}  & {\skti jha}  \\
{\tt \raisebox{-.35ex}{\tt \~\null}na}
              & {\skt Va}  & {\skti \~na}  \\
{\tt .ta}     & {\skt f}  & {\skti \d ta}  \\
{\tt .tha}    & {\skt F} & {\skti \d tha} \\
{\tt .da}     & {\skt .q}  & {\skti \d da}  \\
{\tt .dha}    & {\skt Q} & {\skti \d dha} \\
{\tt .na}     & {\skt :Na}  & {\skti \d na}  \\
{\tt ta}      & {\skt ta}   & {\skti ta}   \\
{\tt tha}     & {\skt Ta}  & {\skti tha}  \\
{\tt da}      & {\skt d}   & {\skti da}   \\
{\tt dha}     & {\skt ;Da}  & {\skti dha}  \\
{\tt na}      & {\skt na}   & {\skti na}   \\
{\tt pa}      & {\skt :pa}   & {\skti pa}   \\
{\tt pha}     & {\skt :P}  & {\skti pha}  \\
{\tt ba}      & {\skt ba}   & {\skti ba}   \\
{\tt bha}     & {\skt Ba}  & {\skti bha}  \\
{\tt ma}      & {\skt ma}   & {\skti ma}   \\
{\tt ya}   & {\skt ya}   & {\skti ya}   \\
{\tt ra}   & {\skt .=}   & {\skti ra}   \\
{\tt la}   & {\skt l}   & {\skti la}   \\
{\tt va}   & {\skt va}   & {\skti va}   \\
{\tt "sa}  & {\skt Za}  & {\skti \'sa}  \\
{\tt .sa}  & {\skt :Sa}  & {\skti \d sa}  \\
{\tt sa}   & {\skt .sa}   & {\skti sa}   \\
{\tt ha}   & {\skt h}   & {\skti ha}   \\
\hline
\end{tabular}
\end{minipage}}
\put(7,39){\begin{minipage}{35mm}
\renewcommand{\arraystretch}{1.03}
\begin{tabular}{|c|c|c|}
\hline
{\small input} & {\small skt} & {\small skti} \\
\hline
{\tt 0}    & {\skt 0}    & {\skti 0}    \\
{\tt 1}    & {\skt 1}    & {\skti 1}    \\
{\tt 2}    & {\skt 2}    & {\skti 2}    \\
{\tt 3}    & {\skt 3}    & {\skti 3}    \\
{\tt 4}    & {\skt 4}    & {\skti 4}    \\
{\tt 5}    & {\skt 5}    & {\skti 5}    \\
{\tt 6}    & {\skt 6}    & {\skti 6}    \\
{\tt 7}    & {\skt 7}    & {\skti 7}    \\
{\tt 8}    & {\skt 8}    & {\skti 8}    \\
{\tt 9}    & {\skt 9}    & {\skti 9}    \\
\hline
\end{tabular}
\end{minipage}
}
\put(99,89.2){\begin{minipage}{38mm}
\renewcommand{\arraystretch}{.95} %{1.16}
{\skt }
\begin{tabular}{|c|c|c|}
\hline
{\small input} & {\small skt} & {\small skti} \\
\hline
{\tt .a}      & {\relsize{-1}{{}\skt\symbol{89}}}
                                             & {{}\skti $^\prime $}  \\
{\tt |}       & {\relsize{-1}{\skt \ZS{12}@A}}       & {\skti {\upshape\,$\mid$}}    \\
{\tt ||}      & {\relsize{-1}{\skt \ZS{12}@A\ZS{6}@A}}      & {\skti {\upshape\,$\mid\mid$}}   \\
{\tt .o}      & {\relsize{-1}{\skt ?}}      & {\skti O\~m}   \\
{\tt "h}      & {\relsize{-1}{\skt H1}}      & {\skti \ZZ h}   \\
{\tt "da}     & {\relsize{-1}{\skt L}}     & {\skti \ZZ da}  \\
{\tt "dha}    & {\relsize{-1}{\skt L1h}}    & {\skti \ZZ dha} \\
{\tt a@}      & {\relsize{-1}{\skt A\ZM{FTV}\ZS{20}}}      & {\skti a{\upshape$^\circ$}}   \\
{\tt ..}      & {\relsize{-1}{\skt \ZN{.}}}      & {\skti .}   \\
{\tt a\#}     & {\relsize{-1}{\skt A\ZH{-6}{<}}}      & {\skti \ZA{30}{a}}   \\
{\tt a!}      & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`7}}}}      & {\skti \ZA{1}{a}}   \\
{\tt a!!}     & {\relsize{-1}{\skt A\ZH{-9}{\ZK{`7}}\ZH{-3}{\ZK{`7}}}}     & {\skti \ZA{6}{a}}  \\
{\tt a\_}     & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`8}}}}      & {\skti \ZA{2}{a}}   \\
{\tt a"1}     & {\relsize{-1}{\skt A\ZK{1\ZH{-12}{`7}\ZH{-10}{`8}}}}     & {\skti \ZA{4}{a}}\rule{0mm}{6mm} \\
{\tt a"3}     & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`8}}\ZK{3\ZH{-12}{`7}\ZH{-8}{`8}}}}     & {\skti \ZA{3}{a}}\rule{0mm}{6mm} \\
{\tt a.1}     & {\relsize{-1}{\skt A\ZK{1\ZH{-10}{`8}}}}     & {\skti \ZA{15}{a}}\rule{0mm}{5mm} \\
{\tt a.3}     & {\relsize{-1}{\skt A\ZK{3\ZH{-12}{`7}\ZH{-8}{`8}}}}     & {\skti \ZA{16}{a}}\rule{0mm}{6mm} \\
{\tt a\^{}}   & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`0}}}}      & {\skti \ZA{5}{a}}\rule{0mm}{6mm} \\
{\tt a'}      &  ---                         & {\skti \ZA{8}{a}}      \\
{\tt a`}      &  ---                         & {\skti \ZA{7}{a}}      \\
{\tt a<1>}    & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`1}}}}    & {\skti \ZA{9}{a}}    \\
{\tt a<2>}    & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`2}}}}    & {\skti \ZA{10}{a}}    \\
{\tt a<3>}    & {\relsize{-1}{\skt A\ZH{-6}{\ZK{`3}}}}    & {\skti \ZA{11}{a}}    \\
{\tt a<2r>}   & {\relsize{-1}{\skt A\ZH{-10}{\ZK{`4}}}}   & {\skti \ZA{12}{a}}   \\
{\tt a<2u>}   & {\relsize{-1}{\skt A\ZH{-10}{\ZK{`5}}}}   & {\skti \ZA{13}{a}}   \\
{\tt a<3k>}   & {\relsize{-1}{\skt A\ZH{-12}{\ZK{`6}}}}   & {\skti \ZA{14}{a}}   \\
{\tt a<!!>}   & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZH{-11}{\ZK{`!}}}}   & {\skti \ZA{25}{a}}   \\
{\tt a<u>}    & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZH{-6}{\ZK{`u}}}}    & {\skti \ZA{17}{a}}    \\
{\tt a<w>}    & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZH{-6}{\ZK{`z}}}}    & {\skti \ZA{18}{a}}    \\
{\tt a<\_>}   & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZP{-16}{-10}{\ZK{@I@o}}}}    & {\skti \ZA{19}{a}}    \\
{\tt a<.>}    & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZP{-8}{-10}{\ZK{@M}}}}    & {\skti \ZA{20}{a}}    \\
{\tt a<..>}   & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZP{-8}{-10}{\ZK{@M\ZS{-9}@M}}}}   & {\skti \ZA{21}{a}}   \\
{\tt a<!>}    & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZP{-6}{-12}{\ZK{@I\ZV{2}{@I}}}}}    & {\skti \ZA{22}{a}}    \\
{\tt a<\^{}>} & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZP{-6}{-16}{\ZK{@r\ZP{-3}{5}{@b}\ZV{2}{@b}}}}}    & {\skti \ZA{24}{a}}    \\
{\tt a<s>}    & \raisebox{0mm}[\height][0mm]{\relsize{-1}{\skt A\ZK{`s}}}    & {\skti \ZA{23}{a}}    \\
\hline
\end{tabular}
{\skt }
\end{minipage}
}
\put(45,3){\makebox(0,0){\textbf{\large Encoding and Transliteration Scheme.}}}
\put(42,-3){\makebox(0,0){(default options)}}
\end{picture}

\clearpage

\hspace*{10mm}%
\begin{minipage}{122mm}
\addtolength{\parskip}{2mm}
\renewcommand{\baselinestretch}{1.1}

\section{Sample Text from {\sktX \d Rgveda 10.125.}}
\vspace{10mm}

\label{rgtext}
{\skt 
`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} 
 .r8\ZH{-4}{\ZK{`8}}+.d\ZP{-8}{-4}{@R}\ZH{-6}{e};Y4a.B\ZK{`8}a:vRa:s\ZK{`7}ua:Y4a.Ba:(\ZM{rac0FI}a.=:a:m1y\ZK{`8}a:h:ma.\ZK{`7}a:Y0a.d\ZH{-6}{\ZK{`8}}:tyEa.r8\ZH{-4}{\ZK{`8}}+.ta 
 ;Y0a.v\ZK{`8}a.(\ZM{dGu};a:d\ZH{-6}{e}\ZH{-6}{\ZK{`7}}:vEaH\ZS{2}\ZS{12}@A\\
`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} ;Y4a.m\ZK{`8}a.t3a.a:va.r8\ZH{-10}{\ZK{`7}}+.`Na.e\ZK{`8}a:Ba.a
 ;Y0a.b\ZK{`7}a:Ba:m1yR\ZK{`8}a:h:Y4a.m\ZK{`7}a:nd\ZP{-8}{-4}{@R}:\ZK{`8}a:\ZM{0NgFRI0FnIFe}+;a\ZH{-6}{i4}.a 
 `A\ZH{-6}{\ZK{`8}}:h:m\ZK{`8}a:Y5a(\ZM{dGu};a:na.e\ZK{`8}a:Ba.a\ZS{12}@A\ZS{6}@A 1\ZS{12}@A\ZS{6}@A

`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} .sa.ea:m\ZK{`7}a:ma.a:h\ZP{-4}{-4}{\ZK{`8}}:na:sM\ZV{8}{\ZK{`7}}a ;Y0a.ba:Ba:m1yR\ZK{`8}a:h\ZH{-6}{M} 
 tva:S1.\ZK{`7}a.=;mu\ZV{-8}{\ZK{`8}}a:ta :pU\ZV{-8}{\ZK{`8}}a:Sa:`NM\ZK{`8}a Ba:g\ZK{`7}a:m,a\ZS{12}@A\\
`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} d\ZH{-6}{\ZK{`7}}:Da.a:Y4a.m\ZK{`8}a d\ZP{-8}{-4}{@R};Y0a.v\ZK{`7}a:`NMa h\ZP{-4}{-4}{\ZK{`8}}:Y0a.va:Sm\ZK{`7}a:tea 
 .sua:pra.\ZK{`8}a:v.ye\ZK{`8}a\ZK{3\ZH{-12}{`7}\ZH{-8}{`8}} ya.j\ZK{`7}a:ma.a:na.a:ya .sua:nv\ZK{`8}a:tea\ZS{12}@A\ZS{6}@A 2\ZS{12}@A\ZS{6}@A

`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} .=:a:S1\ZH{-10}{r1}\ZH{-6}{i4}.\ZK{`7}a .sM\ZK{`8}a:ga:m\ZK{`7}a:ni4a.\ZK{`8}a va:s\ZK{`7}Ua:na.Ma 
 ;Y2a..ca:Y0a.k\ZH{-8}{\ZK{`8}}+.tua:Si4a.\ZK{`7}a :pra:T\ZK{`8}a:ma.a y\ZK{`8}a.:]i4a.a:ya.\ZK{`7}a:na.a:m,a\ZS{12}@A\\
ta.Ma ma.\ZK{`7}a :d\ZH{-6}{e}\ZH{-6}{\ZK{`8}}:va.a v.y\ZK{`7}a:d:DuaH\ZS{2} :pua.r8\ZH{-4}{\ZK{`8}}+t3a.a 
 BUa:i6a=\ZH{-6}{\ZK{`7}};s1Ta.a.t3a.M\ZK{`8}a BUa:ya.R\ZV{8}{\ZK{`7}}a:ve\ZK{`8}a:Za:y\ZK{`7}a:nti4a.a:m,a\ZS{12}@A\ZS{6}@A 3\ZS{12}@A\ZS{6}@A

ma:ya.\ZK{`8}a .sa.ea `A:n1\ZK{`7}a:ma:Y3at1\ZK{`8}a ya.ea ;Y0a.v\ZK{`8}a:pa:Zy\ZK{`7}a:Y1a.t\ZK{`8}a yaH\ZS{2} 
 :pra.a:Y3a.`N\ZK{`7}a:Y1a.t\ZK{`8}a ya I\ZH{-6}{R2}\ZV{8}{\ZH{-6}{\ZK{`7}}} Zx\ZV{-12}{\ZK{`8}}a:`Na.ea:tyu\ZV{-8}{\ZK{`8}}a:k2+.m,a\ZS{12}@A\\
`A\ZH{-6}{\ZK{`8}}:m\ZK{`8}a:nta:va.e\ZK{`8}a ma.Ma ta o+p\ZK{`7}a ;Y4a.[a:ya:\ZH{0}{i0//Y7}a.nta (ru\ZV{-8}{\ZK{`8}}a:Y1a.Da 
 (r\ZK{`7}ua:ta (ra:Y2a;d\ZM{t0Dj0b}\ZP{-6}{-2}{\ZK{`8}}:vMa .te\ZK{`7}a va:d.a:Y4a.ma\ZS{12}@A\ZS{6}@A 4\ZS{12}@A\ZS{6}@A}

\renewcommand{\ZK}[1]{{\lightgray #1}}

{\skt 
`A\ZH{-6}{\ZK{`8}}:h:me\ZK{`8}a:va .s1v\ZK{`8}a:ya:Y4a.m\ZK{`8}a:d\ZH{-6}{M} v\ZK{`7}a:d.a:Y4a.m\ZK{`8}a .jua:S1\ZH{-6}{M}\ZV{8}{\ZH{-6}{\ZK{`7}}} 
 :d\ZH{-6}{e}\ZH{-6}{\ZK{`8}}:vea:Y4a.B\ZK{`7}a.r8\ZH{-4}{\ZK{`8}}+.ta ma.a:n\ZK{`7}ua:Sea:Y4a.BaH\ZS{2}\ZS{12}@A\\
yMa k+\ZK{`8}a:ma:ye\ZK{`8}a tMa:t\ZK{`7}a:mu\ZV{-8}{\ZK{`8}}a:gr4Ma k\ZH{-12}{\ZK{`7}}\ZH{-12}{\ZV{4}{x}}+.`Na.ea:Y4a.ma tMa
 b.r\ZK{`8}a:h2.a:`Na.M\ZK{`8}a ta.a:m\ZV{2}{x}a:Y0a.SM\ZK{`8}a tMa .s\ZK{`7}ua:me\ZK{`8}a:Da.a:m,a\ZS{12}@A\ZS{6}@A 5\ZS{12}@A\ZS{6}@A

`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} .r8\ZH{-4}{\ZK{`8}}+.d\ZP{-8}{-4}{@R}:a:y\ZK{`8}a ;Da:nu\ZV{-8}{\ZK{`8}}a.=:a t\ZK{`7}a:na.ea:Y4a.ma 
 b.ra:h2\ZP{-6}{-4}{\ZK{`8}}:Y0a.d\ZM{oau}:Se\ZK{`8}a Za.=\ZH{-6}{\ZK{`7}};ve\ZK{`8}a h:nt\ZK{`8}a:va.a o\ZH{-6}{\ZK{`7}}\ZS{12}@A\\
`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} .ja:na.\ZK{`7}a:ya .s\ZK{`8}a:m\ZK{`7}a:d\ZH{-6}{M} k\ZH{-12}{\ZV{4}{x}}+.`Na.ea:m1y\ZK{`8}a:h\ZH{-6}{M} 
 d\ZM{fByF0E};a.a:va.\ZK{`7}a:p\ZV{4}{x}a:Y2a.T\ZK{`8}a:vi4a.a `A.a ;Y0a.v\ZK{`7}a:vea:Za\ZS{12}@A\ZS{6}@A 6\ZS{12}@A\ZS{6}@A

`A\ZH{-6}{\ZK{`8}}:h\ZH{-6}{M} .s\ZK{`7}ua:vea ;Y0a.p\ZK{`8}a:ta.=\ZH{-6}{\ZK{`7}};ma:s1ya mU\ZV{-8}{\ZK{`8}}a:DRa:nm1\ZM{cLe}.a:m\ZK{`8}a 
 ya.ea:Y2a.n\ZK{`7}a.=\ZH{-2}{\ZK{`8}};ps1va\ZK{1\ZH{-12}{`7}\ZH{-10}{`8}};ntaH\ZS{2} .s\ZK{`7}a:mu\ZV{-8}{\ZK{`8}}a:d\ZP{-8}{-4}{@R}\ZH{-6}{e}\ZS{12}@A\\
ta:ta.e\ZK{`8}a ;Y0a.va ;Y1a.t\ZK{`7}a:S2\ZH{-6}{e}\ZH{-6}{\ZK{`8}} Bua:v\ZK{`8}a:na.a:nu\ZV{-8}{\ZK{`8}}a ;Y0a.va.(\ZM{dGu};a.e\ZK{`8}a:ta.a:mMUa 
 d\ZM{fByF0E};a.Ma v\ZK{`8}a:SmRa:`Na.ea:p\ZK{`7}a .s1\ZM{cLe}.p\ZV{4}{x}a:Za.a:Y4a.ma\ZS{12}@A\ZS{6}@A 7\ZS{12}@A\ZS{6}@A

`A\ZH{-6}{\ZK{`8}}:h:me\ZK{`8}a:va va.a:t\ZK{`7}a I+v\ZK{`8}a :pra 
 va.\ZK{`7}a:m1ya.\ZK{`8}a.=;B\ZK{`7}a:ma.a:`Na.\ZK{`8}a 
 Bua:v\ZK{`7}a:na.a:Y2a.n\ZK{`8}a ;Y0a.va.(\ZM{dGu};\ZK{`7}a\ZS{12}@A\\
:p\ZK{`8}a.=:ea ;Y0a.d\ZH{-6}{\ZK{`8}}:va.a :p\ZK{`8}a.= O;\ZH{-6}{\ZK{`8}}:na.a :p\ZK{`7}\ZV{4}{x}a:Y2a.Ta:v.yEa:ta.a:v\ZK{`7}a:ti4a.a 
 ma:Y0a.h\ZP{-4}{-4}{\ZK{`8}}:na.a .sMa b\ZK{`7}a:BUa:va\ZS{12}@A\ZS{6}@A 8\ZS{12}@A\ZS{6}@A

}

\renewcommand{\baselinestretch}{1}
\addtolength{\parskip}{-2mm}
\end{minipage}

\clearpage

\clearpage

\hspace*{10mm}%
\begin{minipage}{122mm}
\addtolength{\parskip}{4mm}
\renewcommand{\baselinestretch}{1.2}

\section{Sample Text from {\sktX S\=amaveda}}
\vspace{6mm}

{\sktI S\=amaveda Sa\d mhit\=a} ({\skti Kauthuma\/}), verses 523--528.
\vspace{15mm}

{\skt }

{\skt 
:pr\ZV{12}{\ZK{`1}}a tua d\ZP{-8}{-4}{@R}\ZV{12}{\ZH{-8}{\ZK{`4}}};v\ZV{12}{\ZK{`3}}a :p\ZV{12}{\ZK{`2}}a:i7a.=\ZV{12}{\ZH{-6}{\ZK{`3}}} k+.e\ZV{12}{\ZK{`2}}a:ZM\ZV{12}{\ZK{`3}}a ;Y3a:n\ZV{12}{\ZK{`1}}a 
 :Si5a:\ZV{12}{\ZK{`2}}a:d\ZV{12}{\ZH{-6}{\ZK{`3}}} n\ZV{12}{\ZK{`1}}\ZV{4}{x}a:Y5a:B\ZV{12}{\ZK{`2}}aH\ZS{2} :pua:na:\ZV{12}{\ZK{`3}}a:na:e\ZV{12}{\ZK{`2}}a `A\ZV{12}{\ZH{-6}{\ZK{`3}}}:Y5a:B\ZV{12}{\ZK{`1}}a 
 va:a.j\ZV{12}{\ZH{-4}{\ZK{`4}}}a:ma:SRa\ZS{12}@A \\
`A\ZV{12}{\ZH{-6}{\ZK{`2}}}:ZvM\ZV{12}{\ZK{`3}}a n\ZV{12}{\ZK{`1}}a tva:\ZV{12}{\ZK{`2}}a va:\ZV{12}{\ZK{`3}}a:Y5a.j\ZV{12}{\ZK{`1}}a:nM\ZV{12}{\ZK{`2}}a 
 m\ZV{12}{\ZK{`3}}a.jR\ZV{12}{\ZK{`2}}a:y\ZV{12}{\ZK{`3}}a:nta:e\ZV{12}{\ZK{`1}}aY:.cC+\ZV{12}{\ZK{`2}}a v\ZV{12}{\ZK{`3}}a:h\ZH{-6}{i5}:R\ZV{12}{\ZK{`1}}a 
 .=\ZV{12}{\ZH{-6}{\ZK{`2}}};Z\ZV{12}{\ZK{`3}}a:na:\ZV{12}{\ZK{`1}}a:Y5a:B\ZV{12}{\ZK{`2}}a:nRa:ya:\ZH{0}{i0///Y7}a:nta\ZS{12}@A\ZS{6}@A 523\ZS{12}@A\ZS{6}@A

:pr\ZV{12}{\ZK{`1}}a k+.a:v.y\ZV{12}{\ZH{-4}{\ZK{`4}}}a:m\ZV{12}{\ZK{`3}}ua:Z\ZV{12}{\ZK{`1}}a:ne\ZV{12}{\ZK{`2}}a:va 
 b.r\ZV{12}{\ZK{`3}}ua:va:a:`Na:e\ZV{12}{\ZK{`2}}a :d\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`3}}}:va:e\ZV{12}{\ZK{`2}}a :d\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`3}}}:va:\ZV{12}{\ZK{`2}}a:na:M\ZV{12}{\ZK{`3}}a 
 .j\ZV{12}{\ZK{`1}}a:Y3a:n\ZV{12}{\ZK{`2}}a:ma:a ;Y1a:va:va:Y2a:k2\ZS{12}@A \\
m\ZV{12}{\ZK{`1}}a:Y1a:h\ZV{12}{\ZH{-6}{\ZK{`2}}}:v.ra:t\ZV{12}{\ZK{`3}}aH\ZS{2} Z\ZV{12}{\ZK{`1}}ua:Y3a:.c\ZV{12}{\ZK{`2}}a:ba:nDuaH\ZS{2} 
 :pa:a:v\ZV{12}{\ZK{`3}}a:k\ZV{12}{\ZH{-12}{\ZK{`2}}}\ZS{2}H\ZS{2} :p\ZV{12}{\ZK{`3}}a:d:\ZV{12}{\ZK{`1}}a v\ZV{12}{\ZK{`2}}a.=;\ZV{12}{\ZK{`3}}a:h:e\ZV{12}{\ZK{`2}}a 
 `A\ZV{12}{\ZH{-12}{\ZK{`6}}}:Bye\ZV{12}{\ZH{-4}{\ZK{`4}}}a:Y2a:t\ZV{12}{\ZK{`3}}a \ZS{2}:=\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`1}}};B\ZV{12}{\ZK{`2}}a:n,a\ZS{12}@A\ZS{6}@A 524\ZS{12}@A\ZS{6}@A

;Y2a:t\ZV{12}{\ZK{`3}}a:s1\ZM{aLeDDr}:a:e\ZV{12}{\ZK{`1}}a va:a:.c\ZV{12}{\ZH{-4}{\ZK{`4}}}a I\ZH{-6}{R};=;ya:Y2a:t\ZV{12}{\ZK{`3}}a :pr\ZV{12}{\ZK{`1}}a 
 va:Y1a:h3\ZM{nCneCe}\ZV{12}{\ZH{-8}{\ZK{`4}}}+.`r\ZH{-6}{R}\ZV{12}{\ZH{-6}{\ZK{`3}}}:t\ZV{12}{\ZK{`1}}a:s1y\ZV{12}{\ZK{`2}}a 
 ;Di5a:\ZV{12}{\ZK{`3}}a:Y2a:tM\ZV{12}{\ZK{`1}}a b.ra:h2\ZV{12}{\ZH{-10}{\ZK{`4}}}:`Na:ea ma:ni5a:\ZV{12}{\ZK{`3}}a:Sa:\ZV{12}{\ZK{`2}}a:m,a\ZS{12}@A \\
ga:\ZV{12}{\ZK{`1}}a:va:e\ZV{12}{\ZK{`2}}a ya:\ZH{0}{i0///Y7}a:nt\ZV{12}{\ZK{`3}}a ga:e\ZV{12}{\ZK{`1}}a:p\ZV{12}{\ZK{`2}}a:Y2a:tMa :p\ZV{12}{\ZK{`3}}\ZV{4}{x}a:.cC\ZV{12}{\ZH{-6}{\ZK{`2}}}+ma:\ZV{12}{\ZK{`2}}a:na:\ZV{12}{\ZK{`3}}aH\ZS{2} 
 .sa:e\ZV{12}{\ZK{`1}}a:mM\ZV{12}{\ZK{`2}}a ya:\ZH{0}{i0///Y7}a:nta m\ZV{12}{\ZK{`3}}a:t\ZV{12}{\ZK{`1}}a:ya:e\ZV{12}{\ZK{`2}}a va:a:va:Za:\ZV{12}{\ZK{`3}}a:na:\ZV{12}{\ZK{`2}}aH\ZS{2}\ZS{12}@A\ZS{6}@A 525\ZS{12}@A\ZS{6}@A

`A\ZV{12}{\ZH{-6}{\ZK{`3}}}:s1y\ZV{12}{\ZK{`2}}a :pre\ZV{12}{\ZK{`3}}a:Sa:\ZV{12}{\ZK{`2}}a :h\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`3}}}:m\ZV{12}{\ZK{`1}}a:na:\ZV{12}{\ZK{`2}}a 
 :p\ZV{12}{\ZK{`3}}Ua:y\ZV{12}{\ZK{`1}}a:ma:\ZV{12}{\ZK{`2}}a:na:ea :d\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`3}}}:va:e\ZV{12}{\ZK{`2}}a :d\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`3}}}:ve\ZV{12}{\ZK{`2}}a:Y5a:B\ZV{12}{\ZK{`3}}aH\ZS{2} 
 .s\ZV{12}{\ZK{`1}}a:m\ZV{12}{\ZK{`2}}a:p\ZV{4}{x}a:k2\ZV{12}{\ZH{-10}{\ZK{`3}}} .=\ZV{12}{\ZH{-6}{\ZK{`1}}};s\ZV{12}{\ZK{`2}}a:m,a\ZS{12}@A \\
.s\ZV{12}{\ZK{`3}}ua:t\ZV{12}{\ZK{`2}}aH\ZS{2} :p\ZV{12}{\ZK{`3}}a:Y1a:v\ZV{12}{\ZK{`2}}a.t3M\ZV{12}{\ZK{`3}}a :p\ZV{12}{\ZK{`1}}a:yyeR\ZV{12}{\ZK{`2}}a:Y2a:t\ZV{12}{\ZK{`3}}a 
 \ZS{2}:=\ZH{-6}{e}\ZV{12}{\ZH{-6}{\ZK{`1}}};B\ZV{12}{\ZK{`2}}a:\ZH{0}{i0//////Y7}a:nm1\ZM{cLe}.\ZV{12}{\ZK{`3}}a:te\ZV{12}{\ZK{`2}}a:v\ZV{12}{\ZK{`3}}a .s\ZV{12}{\ZK{`1}}a:d2\ZM{j0mC0eH0E}+a\ZV{12}{\ZH{-6}{\ZK{`2}}} 
 :pa:Z\ZV{12}{\ZK{`3}}ua:m\ZV{12}{\ZK{`2}}a:\ZH{0}{i0///Y7}a:nt\ZV{12}{\ZK{`1}}a h:e\ZV{12}{\ZK{`2}}a:ta:a\ZS{12}@A\ZS{6}@A 526\ZS{12}@A\ZS{6}@A

.sa:e\ZV{12}{\ZK{`1}}a:m\ZV{12}{\ZK{`2}}aH\ZS{2} :pa:va:tea .ja:Y3a:n\ZV{12}{\ZK{`3}}a:ta:\ZV{12}{\ZK{`1}}a m\ZV{12}{\ZK{`2}}a:ti5a:\ZV{12}{\ZK{`3}}a:na:M\ZV{12}{\ZK{`1}}a 
 .j\ZV{12}{\ZK{`2}}a:Y3a:n\ZV{12}{\ZK{`3}}a:ta:\ZV{12}{\ZK{`2}}a ;Y1a:d\ZV{12}{\ZH{-6}{\ZK{`3}}}:va:e\ZV{12}{\ZK{`1}}a .j\ZV{12}{\ZK{`2}}a:Y3a:n\ZV{12}{\ZK{`3}}a:ta:\ZV{12}{\ZK{`1}}a 
 :p\ZV{12}{\ZK{`2}}\ZV{4}{x}a:Y3a:T\ZV{12}{\ZK{`3}}a:v.ya:\ZV{12}{\ZK{`2}}aH\ZS{2}\ZS{12}@A \\
.j\ZV{12}{\ZK{`3}}a:Y3a:na:ta:\ZV{12}{\ZK{`1}}a:gnea.jR\ZV{12}{\ZH{-4}{\ZK{`4}}}a:Y3a:n\ZV{12}{\ZK{`3}}a:ta:\ZV{12}{\ZK{`1}}a .sUa:yR\ZV{12}{\ZH{-4}{\ZK{`4}}}a:s1ya 
 .ja:Y3a:n\ZV{12}{\ZK{`3}}a:te\ZV{12}{\ZK{`1}}a:nd\ZP{-8}{-4}{@R}\ZV{12}{\ZH{-6}{\ZK{`2}}};s1ya .ja:Y3a:n\ZV{12}{\ZK{`3}}a:ta:e\ZV{12}{\ZK{`1}}a:ta ;Y1a:va:S`Na:e\ZV{12}{\ZH{-4}{\ZK{`4}}}aH\ZS{2}\ZS{12}@A\ZS{6}@A 527\ZS{12}@A\ZS{6}@A

`A\ZV{12}{\ZH{-6}{\ZK{`3}}}:Y5a:B\ZV{12}{\ZK{`1}}a ;Y1a.t3\ZV{12}{\ZK{`2}}a:p\ZV{12}{\ZK{`3}}\ZV{4}{x}a:S2\ZH{-6}{M}\ZV{12}{\ZH{-6}{\ZK{`1}}} v\ZV{4}{x}a:S\ZV{12}{\ZH{-4}{\ZK{`4}}}a:`NMa 
 .va:ya:e\ZV{12}{\ZK{`3}}a:Da:\ZV{12}{\ZK{`1}}a:m\ZV{12}{\ZK{`2}}a:\ZM{0PqPOM0bgNaENdE}*:+e\ZV{12}{\ZK{`3}}a:Y1a:S\ZV{12}{\ZK{`1}}a:`N\ZV{12}{\ZK{`2}}a:ma:va:a:va:Za:nt\ZV{12}{\ZK{`3}}a 
 va:\ZV{12}{\ZK{`1}}a:`Ni5a:\ZV{12}{\ZK{`2}}aH\ZS{2} \\
v\ZV{12}{\ZK{`2}}a:na:\ZV{12}{\ZK{`3}}a b\ZV{12}{\ZK{`1}}a:sa:\ZV{12}{\ZK{`2}}a:na:e\ZV{12}{\ZK{`3}}a v\ZV{12}{\ZK{`1}}a.r8\ZV{12}{\ZH{-10}{\ZK{`2}}}+.`Na:e\ZV{12}{\ZK{`3}}a 
 n\ZV{12}{\ZH{-4}{\ZK{`5}}}a ;Y5a:sa:nD\ZV{12}{\ZK{`3}}ua:Y1a:vR\ZV{12}{\ZK{`1}}a .=\ZV{12}{\ZH{-6}{\ZK{`2}}};t2\ZV{12}{\ZK{`3}}a:Da:\ZV{12}{\ZK{`1}}a
 d\ZV{12}{\ZH{-6}{\ZK{`2}}}:ya:te\ZV{12}{\ZK{`3}}a va:\ZV{12}{\ZK{`1}}a:ya:R\ZV{12}{\ZK{`2}}a:Y4a:`Na\ZS{12}@A\ZS{6}@A 528\ZS{12}@A\ZS{6}@A

}
\vfill

\addtolength{\parskip}{-4mm}
\renewcommand{\baselinestretch}{1}
\end{minipage}

{\skt }

\clearpage

\begin{center}

{\smaller
\vspace{10mm}
\renewcommand{\arraystretch}{2}
\addtolength{\tabcolsep}{-.55mm}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c||}
\cline{2-17}
\multicolumn{1}{c|}{}&
{\small 0} & {\small 1} & {\small 2} & {\small 3} & {\small 4} & {\small 5} & 
{\small 6} & {\small 7} & {\small 8} & {\small 9} & {\small A} & {\small B} & 
{\small C} & {\small D} & {\small E} & 
\multicolumn{1}{c|}{\small F}\\ 
\cline{2-17} \noalign{\vspace{\doublerulesep}} \hline
{\small 00} &
{\large\skt\symbol{'0}} &
{\large\skt\symbol{'1}} &
{\large\skt\symbol{'2}} &
{\large\skt\symbol{'3}} &
{\large\skt\symbol{'4}} &
{\large\skt\symbol{'5}} &
{\large\skt\symbol{'6}} &
{\large\skt\symbol{'7}} &
{\large\skt\symbol{'10}} &
{\large\skt\symbol{'11}} &
{\large\skt\symbol{'12}} &
{\large\skt\symbol{'13}} &
{\large\skt\symbol{'14}} &
{\large\skt\symbol{'15}} &
{\large\skt\symbol{'16}} &
{\large\skt\symbol{'17}} \\ \hline
{\small 10} &
{\large\skt\symbol{'20}} &
{\large\skt\symbol{'21}} &
{\large\skt\symbol{'22}} &
{\large\skt\symbol{'23}} &
{\large\skt\symbol{'24}} &
{\large\skt\symbol{'25}} &
{\large\skt\symbol{'26}} &
{\large\skt\symbol{'27}} &
{\large\skt\symbol{'30}} &
{\large\skt\symbol{'31}} &
{\large\skt\symbol{'32}} &
{\large\skt\symbol{'33}} &
{\large\skt\symbol{'34}} &
{\large\skt\symbol{'35}} &
{\large\skt\symbol{'36}} &
{\large\skt\symbol{'37}} \\ \hline
{\small 20} &
{\large\skt\symbol{'40}} &
{\large\skt\symbol{'41}} &
{\large\skt\symbol{'42}} &
{\large\skt\symbol{'43}} &
{\large\skt\symbol{'44}} &
{\large\skt\symbol{'45}} &
{\large\skt\symbol{'46}} &
{\large\skt\symbol{'47}} &
{\large\skt\symbol{'50}} &
{\large\skt\symbol{'51}} &
{\large\skt\symbol{'52}} &
{\large\skt\symbol{'53}} &
{\large\skt\symbol{'54}} &
{\large\skt\symbol{'55}} &
{\large\skt\symbol{'56}} &
{\large\skt\symbol{'57}} \\ \hline
{\small 30} &
{\large\skt\symbol{'60}} &
{\large\skt\symbol{'61}} &
{\large\skt\symbol{'62}} &
{\large\skt\symbol{'63}} &
{\large\skt\symbol{'64}} &
{\large\skt\symbol{'65}} &
{\large\skt\symbol{'66}} &
{\large\skt\symbol{'67}} &
{\large\skt\symbol{'70}} &
{\large\skt\symbol{'71}} &
{\large\skt\symbol{'72}} &
{\large\skt\symbol{'73}} &
{\large\skt\symbol{'74}} &
{\large\skt\symbol{'75}} &
{\large\skt\symbol{'76}} &
{\large\skt\symbol{'77}} \\ \hline
{\small 40} &
{\large\skt\symbol{'100}} &
{\large\skt\symbol{'101}} &
{\large\skt\symbol{'102}} &
{\large\skt\symbol{'103}} &
{\large\skt\symbol{'104}} &
{\large\skt\symbol{'105}} &
{\large\skt\symbol{'106}} &
{\large\skt\symbol{'107}} &
{\large\skt\symbol{'110}} &
{\large\skt\symbol{'111}} &
{\large\skt\symbol{'112}} &
{\large\skt\symbol{'113}} &
{\large\skt\symbol{'114}} &
{\large\skt\symbol{'115}} &
{\large\skt\symbol{'116}} &
{\large\skt\symbol{'117}} \\ \hline
{\small 50} &
{\large\skt\symbol{'120}} &
{\large\skt\symbol{'121}} &
{\large\skt\symbol{'122}} &
{\large\skt\symbol{'123}} &
{\large\skt\symbol{'124}} &
{\large\skt\symbol{'125}} &
{\large\skt\symbol{'126}} &
{\large\skt\symbol{'127}} &
{\large\skt\symbol{'130}} &
{\large\skt\symbol{'131}} &
{\large\skt\symbol{'132}} &
{\large\skt\symbol{'133}} &
{\large\skt\symbol{'134}} &
{\large\skt\symbol{'135}} &
{\large\skt\symbol{'136}} &
{\large\skt\symbol{'137}} \\ \hline
{\small 60} &
{\large\skt\symbol{'140}} &
{\large\skt\symbol{'141}} &
{\large\skt\symbol{'142}} &
{\large\skt\symbol{'143}} &
{\large\skt\symbol{'144}} &
{\large\skt\symbol{'145}} &
{\large\skt\symbol{'146}} &
{\large\skt\symbol{'147}} &
{\large\skt\symbol{'150}} &
{\large\skt\symbol{'151}} &
{\large\skt\symbol{'152}} &
{\large\skt\symbol{'153}} &
{\large\skt\symbol{'154}} &
{\large\skt\symbol{'155}} &
{\large\skt\symbol{'156}} &
{\large\skt\symbol{'157}} \\ \hline
{\small 70} &
{\large\skt\symbol{'160}} &
{\large\skt\symbol{'161}} &
{\large\skt\symbol{'162}} &
{\large\skt\symbol{'163}} &
{\large\skt\symbol{'164}} &
{\large\skt\symbol{'165}} &
{\large\skt\symbol{'166}} &
{\large\skt\symbol{'167}} &
{\large\skt\symbol{'170}} &
{\large\skt\symbol{'171}} &
{\large\skt\symbol{'172}} &
{\large\skt\symbol{'173}} &
{\large\skt\symbol{'174}} &
{\large\skt\symbol{'175}} &
{\large\skt\symbol{'176}} &
{\large\skt\symbol{'177}} \\ \hline
{\small 80} &
{\large\skt\symbol{'200}} &
{\large\skt\symbol{'201}} &
{\large\skt\symbol{'202}} &
{\large\skt\symbol{'203}} &
{\large\skt\symbol{'204}} &
{\large\skt\symbol{'205}} &
{\large\skt\symbol{'206}} &
{\large\skt\symbol{'207}} &
{\large\skt\symbol{'210}} &
{\large\skt\symbol{'211}} &
{\large\skt\symbol{'212}} &
{\large\skt\symbol{'213}} &
{\large\skt\symbol{'214}} &
{\large\skt\symbol{'215}} &
{\large\skt\symbol{'216}} &
{\large\skt\symbol{'217}} \\ \hline
{\small 90} &
{\large\skt\symbol{'220}} &
{\large\skt\symbol{'221}} &
{\large\skt\symbol{'222}} &
{\large\skt\symbol{'223}} &
{\large\skt\symbol{'224}} &
{\large\skt\symbol{'225}} &
{\large\skt\symbol{'226}} &
{\large\skt\symbol{'227}} &
{\large\skt\symbol{'230}} &
{\large\skt\symbol{'231}} &
{\large\skt\symbol{'232}} &
{\large\skt\symbol{'233}} &
{\large\skt\symbol{'234}} &
{\large\skt\symbol{'235}} &
{\large\skt\symbol{'236}} &
{\large\skt\symbol{'237}} \\ \hline
{\small A0} &
{\large\skt\symbol{'240}} &
{\large\skt\symbol{'241}} &
{\large\skt\symbol{'242}} &
{\large\skt\symbol{'243}} &
{\large\skt\symbol{'244}} &
{\large\skt\symbol{'245}} &
{\large\skt\symbol{'246}} &
{\large\skt\symbol{'247}} &
{\large\skt\symbol{'250}} &
{\large\skt\symbol{'251}} &
{\large\skt\symbol{'252}} &
{\large\skt\symbol{'253}} &
{\large\skt\symbol{'254}} &
{\large\skt\symbol{'255}} &
{\large\skt\symbol{'256}} &
{\large\skt\symbol{'257}} \\ \hline
{\small B0} &
{\large\skt\symbol{'260}} &
{\large\skt\symbol{'261}} &
{\large\skt\symbol{'262}} &
{\large\skt\symbol{'263}} &
{\large\skt\symbol{'264}} &
{\large\skt\symbol{'265}} &
{\large\skt\symbol{'266}} &
{\large\skt\symbol{'267}} &
{\large\skt\symbol{'270}} &
{\large\skt\symbol{'271}} &
{\large\skt\symbol{'272}} &
{\large\skt\symbol{'273}} &
{\large\skt\symbol{'274}} &
{\large\skt\symbol{'275}} &
{\large\skt\symbol{'276}} &
{\large\skt\symbol{'277}} \\ \hline
{\small C0} &
{\large\skt\symbol{'300}} &
{\large\skt\symbol{'301}} &
{\large\skt\symbol{'302}} &
{\large\skt\symbol{'303}} &
{\large\skt\symbol{'304}} &
{\large\skt\symbol{'305}} &
{\large\skt\symbol{'306}} &
{\large\skt\symbol{'307}} &
{\large\skt\symbol{'310}} &
{\large\skt\symbol{'311}} &
{\large\skt\symbol{'312}} &
{\large\skt\symbol{'313}} &
{\large\skt\symbol{'314}} &
{\large\skt\symbol{'315}} &
{\large\skt\symbol{'316}} &
{\large\skt\symbol{'317}} \\ \hline
{\small D0} &
{\large\skt\symbol{'320}} &
{\large\skt\symbol{'321}} &
{\large\skt\symbol{'322}} &
{\large\skt\symbol{'323}} &
{\large\skt\symbol{'324}} &
{\large\skt\symbol{'325}} &
{\large\skt\symbol{'326}} &
{\large\skt\symbol{'327}} &
{\large\skt\symbol{'330}} &
{\large\skt\symbol{'331}} &
{\large\skt\symbol{'332}} &
{\large\skt\symbol{'333}} &
{\large\skt\symbol{'334}} &
{\large\skt\symbol{'335}} &
{\large\skt\symbol{'336}} &
{\large\skt\symbol{'337}} \\ \hline
{\small E0} &
{\large\skt\symbol{'340}} &
{\large\skt\symbol{'341}} &
{\large\skt\symbol{'342}} &
{\large\skt\symbol{'343}} &
{\large\skt\symbol{'344}} &
{\large\skt\symbol{'345}} &
{\large\skt\symbol{'346}} &
{\large\skt\symbol{'347}} &
{\large\skt\symbol{'350}} &
{\large\skt\symbol{'351}} &
{\large\skt\symbol{'352}} &
{\large\skt\symbol{'353}} &
{\large\skt\symbol{'354}} &
{\large\skt\symbol{'355}} &
{\large\skt\symbol{'356}} &
{\large\skt\symbol{'357}} \\ \hline
{\small F0} &
{\large\skt\symbol{'360}} &
{\large\skt\symbol{'361}} &
{\large\skt\symbol{'362}} &
{\large\skt\symbol{'363}} &
{\large\skt\symbol{'364}} &
{\large\skt\symbol{'365}} &
{\large\skt\symbol{'366}} &
{\large\skt\symbol{'367}} &
{\large\skt\symbol{'370}} &
{\large\skt\symbol{'371}} &
{\large\skt\symbol{'372}} &
{\large\skt\symbol{'373}} &
{\large\skt\symbol{'374}} &
{\large\skt\symbol{'375}} &
{\large\skt\symbol{'376}} &
{\large\skt\symbol{'377}} \\ \hline \noalign{\vspace{\doublerulesep}} \cline{2-17}
\end{tabular}
}

\vspace{10mm}
\textbf{Font Table: skt-series fonts (at 17.28pt).}
\end{center}

\clearpage

\begin{center}

\vspace{10mm}
{\smaller
\renewcommand{\arraystretch}{2}
\addtolength{\tabcolsep}{-.3mm}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c||}
\cline{2-17}
\multicolumn{1}{c|}{} &
0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & A & B & C & D & E & 
\multicolumn{1}{c|}{F}\\ 
\cline{2-17} \noalign{\vspace{\doublerulesep}} \hline
00 &
{\tt i0} &
{\tt i3} &
{\tt i4} &
{\tt i5} &
{\tt i6} &
{\tt i7} &
{\tt i8} &
{\tt i9} &
{\tt Y0} &
{\tt Y1} &
{\tt Y2} &
{\tt Y3} &
{\tt Y4} &
{\tt Y5} &
{\tt Y6} &
{\tt Y7} \\ \hline
10 &
{\tt `0} &
{\tt `1} &
{\tt `2} &
{\tt `3} &
{\tt `4} &
{\tt `5} &
{\tt `6} &
{\tt `7} &
{\tt `o} &
{\tt `x} &
{\tt `X} &
{\tt `w} &
{\tt `W} &
{\tt r8} &
{\tt r9} &
{\tt `>} \\ \hline
20 &
{\tt R2} &
{\tt `8} &
{\tt r1} &
{\tt k1} &
{\tt j1} &
{\tt P1} &
{\tt h1} &
{\tt r2} &
{\tt (} &
{\tt )} &
{\tt *} &
{\tt +} &
{\tt ,} &
{\tt -} &
{\tt .} &
{\tt /} \\ \hline
30 &
{\tt 0} &
{\tt 1} &
{\tt 2} &
{\tt 3} &
{\tt 4} &
{\tt 5} &
{\tt 6} &
{\tt 7} &
{\tt 8} &
{\tt 9} &
{\tt :} &
{\tt ;} &
{\tt <} &
{\tt =} &
{\tt >} &
{\tt ?} \\ \hline
40 &
    --  &
{\tt A} &
{\tt B} &
{\tt C} &
{\tt D} &
{\tt E} &
{\tt F} &
{\tt G} &
{\tt H} &
{\tt I} &
{\tt J} &
{\tt K} &
{\tt L} &
{\tt M} &
{\tt N} &
{\tt O} \\ \hline
50 &
{\tt P} &
{\tt Q} &
{\tt R} &
{\tt S} &
{\tt T} &
{\tt U} &
{\tt V} &
{\tt W} &
{\tt X} &
{\tt Y} &
{\tt Z} &
{\tt [} &
{\tt L1} &
{\tt ]} &
{\tt H1} &
{\tt R1} \\ \hline
60 &
    --  &
{\tt a} &
{\tt b} &
{\tt c} &
{\tt d} &
{\tt e} &
{\tt f} &
{\tt g} &
{\tt h} &
{\tt i} &
{\tt j} &
{\tt k} &
{\tt l} &
{\tt m} &
{\tt n} &
{\tt o} \\ \hline
70 &
{\tt p} &
{\tt q} &
{\tt r} &
{\tt s} &
{\tt t} &
{\tt u} &
{\tt v} &
{\tt w} &
{\tt x} &
{\tt y} &
{\tt z} &
{\tt r4} &
{\tt L2} &
{\tt m1} &
{\tt s1} &
{\tt l1} \\ \hline
80 &
{\tt k2} &
{\tt k3} &
{\tt k4} &
{\tt c1} &
{\tt C1} &
{\tt j2} &
{\tt t1} &
{\tt t2} &
{\tt t3} &
{\tt d1} &
{\tt n1} &
{\tt p1} &
{\tt l2} &
{\tt S1} &
{\tt S2} &
{\tt h2} \\ \hline
90 &
{\tt t4} &
{\tt d2} &
{\tt m2} &
{\tt y1} &
{\tt y2} &
{\tt y3} &
{\tt h3} &
{\tt h4} &
{\tt h5} &
    --   &
    --   &
    --   &
{\tt `!} &
{\tt `s} &
{\tt `u} &
{\tt `w} \\ \hline
A0 &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   &
    --   \\ \hline
B0 &
{\tt @0} &
{\tt @1} &
{\tt @2} &
{\tt `r} &
{\tt @4} &
{\tt @5} &
{\tt @6} &
{\tt `R} &
{\tt @8} &
{\tt @9} &
{\tt `A} &
{\tt `[} &
{\tt `]} &
{\tt `J} &
{\tt `N} &
{\tt `T} \\ \hline
C0 &
    --  &
{\tt @A} &
{\tt @B} &
{\tt @C} &
{\tt @D} &
{\tt @E} &
{\tt @F} &
{\tt @G} &
{\tt @H} &
{\tt @I} &
{\tt @J} &
{\tt @K} &
{\tt @L} &
{\tt @M} &
{\tt @N} &
{\tt @O} \\ \hline
D0 &
{\tt @P} &
{\tt @Q} &
{\tt @R} &
{\tt @S} &
{\tt @T} &
{\tt @U} &
{\tt @V} &
{\tt @W} &
{\tt @X} &
{\tt @Y} &
{\tt @Z} &
    --  &
    --  &
    --  &
    --  &
    --  \\ \hline
E0 &
    --   &
{\tt @a} &
{\tt @b} &
{\tt @c} &
{\tt @d} &
{\tt @e} &
{\tt @f} &
{\tt @g} &
{\tt @h} &
{\tt @i} &
{\tt @j} &
{\tt @k} &
{\tt @l} &
{\tt @m} &
{\tt @n} &
{\tt @o} \\ \hline
F0 &
{\tt @p} &
{\tt @q} &
{\tt @r} &
{\tt @s} &
{\tt @t} &
{\tt @u} &
{\tt @v} &
{\tt @w} &
{\tt @x} &
{\tt @y} &
{\tt @z} &
    --  &
    --  &
    --  &
    --  &
    --  \\ \hline \noalign{\vspace{\doublerulesep}} \cline{2-17}
\end{tabular}
}

\vspace{\fill}
\textbf{Font Access Codes: skt-series fonts.}
\end{center}

\clearpage

\addtolength{\evensidemargin}{-17mm}
\addtolength{\oddsidemargin}{-17mm}
\addtolength{\textwidth}{34mm}
\addtolength{\linewidth}{34mm}
\addtolength{\hsize}{34mm}
% The additional width is for the sa.myoga table that follows

\renewcommand{\baselinestretch}{1}\large\normalsize

\hspace*{17mm}\begin{minipage}{137mm}
\addtolength{\parskip}{2mm}
\section{{\sktX Sa\d myoga} Table}%
%
This lists the {\skti sa\d myoga} tested by the font: the first shown is the
default; where it is affected by user-selectable options, all the possible 
forms are shown.
The sources used in compiling this table, in order consulted, are:\\
\makebox[2mm][l]{\textsuperscript{c}}
Michael Coulson, \emph{Teach Yourself Sanskrit}, pp.~22--24.\\
\makebox[2mm][l]{\textsuperscript{m}}
Monier-Williams, \emph{A Practical Grammar of the Sanskrit Language}, p.~2.\\
\makebox[2mm][l]{\textsuperscript{p}}
S.\,C.\,Vasu, {\skti A\d s\d t\=adhy\=ay\={\i}} \emph{of} {\skti P\=a\d nini},
           (Riddled with typo's.)\\
\makebox[2mm][l]{\textsuperscript{a}}
J.\,E.\,Agenbroad, \emph{Difficult Characters: A Collection of Devanagari 
           Conjunct\newline\hspace*{2mm} 
           Consonants}, Int.~Assoc.~of Orientalist Librarians, 
           Bulletin~38, pp.~17--53.
\addtolength{\parskip}{-2mm}
\end{minipage}

\renewcommand{\baselinestretch}{1}\large\normalsize

\begin{multicols}{3}

\columnseprule .1mm
\parindent 0pt

\sing{c}{\skti kka}{\skt \ZM{0NkLNPLPE00kL0PLhA}*: k1k }
\sing{a}{\skti kk\d na}{\skt k1k1Na k1k1`Na }
\sing{a}{\skti kkya}{\skt \ZM{0NkLNPLPE00kL0PLhA}*:\ZV{2}{y2}+.a \ZM{0NkLNPLPE00kL0PLhA}*;y1a k1k1ya }
\sing{a}{\skti kk\'sa}{\skt k1k1Za}
\sing{c}{\skti kkha}{\skt k1Ka}
\sing{a}{\skti kkhya}{\skt k1K.ya}
\sing{p}{\skti k\.na}{\skt \ZM{0NkLNPLPELNE00qP0M}*; k1z } 
\sing{c}{\skti kca}{\skt k1:ca}
\sing{p}{\skti kcha}{\skt k1C} 
\sing{a}{\skti kja}{\skt k1ja}
\sing{p}{\skti k\d ta}{\skt k1f} 
\sing{a}{\skti k\d tra}{\skt k1f\ZH{-12}{r1}}
\sing{p}{\skti k\d tha}{\skt k1F} 
\sing{c}{\skti k\d na}{\skt k1Na}
\sing{c}{\skti kta}{\skt k2 k1ta }
\sing{a}{\skti ktca}{\skt k1t:ca}
\sing{c}{\skti ktya}{\skt k2y2+.a k2:y1a k1tya }
\sing{c}{\skti ktra}{\skt k2\ZP{-10}{-2}{r1} k1+t4a }
\sing{c}{\skti ktrya}{\skt k2\ZP{-10}{-2}{r1}y2+.a k2\ZP{-10}{-2}{r1}:y1a  k1+t4ya }
\sing{c}{\skti ktva}{\skt k3 k1tva }
\sing{p}{\skti ktha}{\skt k1Ta k1`Ta } 
\dual{p}{\skti kthna}{\skt k1T\ZM{pBneBe0BE}a k1`T\ZM{pBneBe0BE}a}{\skt k1`Tna k1Tna } 
\sing{p}{\skti kthya}{\skt k1Tya k1`Tya } 
\sing{a}{\skti kda}{\skt k1d}
\sing{c}{\skti kna}{\skt \ZM{0NkLNPLPE0DnLDE}*: k1na }
\sing{c}{\skti knya}{\skt \ZM{0NkLNPLPE0DnLDE}*:\ZV{2}{y2}+.a \ZM{0NkLNPLPE0DnLDE}*;y1a k1nya }
\sing{p}{\skti kpa}{\skt k1pa} 
\sing{p}{\skti kpra}{\skt k1pra} 
\sing{p}{\skti kpha}{\skt k1P} 
\sing{c}{\skti kma}{\skt k4 k1ma }
\sing{a}{\skti kmya}{\skt k4y1a k1mya }
\sing{c}{\skti kya}{\skt ky2+.a k1ya }
\sing{c}{\skti kra}{\skt k\ZM{l0R}}
\sing{c}{\skti krya}{\skt k\ZM{l0R}y2+.a k1\ZM{l0R}ya }
\sing{c}{\skti kla}{\skt \ZM{0NkLNPLPELFI00l}*: k1l k1l1a \ZM{DNkPNPP0APbE00L}*+ }
\dual{a}{\skti klya}{\skt *\ZM{pNkdNPdPEdFIp0lBHy}+;a \ZM{0NkLNPLPELFI00l}*;y1a *\ZM{lNk0NP00A0bEp0LFHy}*.a}{\skt \ZM{DNkPNPP0APbE00L}*+.y1a k1l1ya }
\sing{c}{\skti kva}{\skt \ZM{0NkLNPLPE00kLhA}*: k1va }
\sing{c}{\skti kvya}{\skt \ZM{0NkLNPLPE00kLhA}*:\ZV{2}{y2}+.a \ZM{0NkLNPLPE00kLhA}*;y1a k1v.ya }
\sing{p}{\skti k\'sa}{\skt k1Za} 
\dual{p}{\skti k\'sla}{\skt k1(\ZM{lBl0FI0PE}; k1(\ZM{pBL00E}a k1)\ZM{pBL00E}a}{\skt k1)\ZM{lBl0FI0PE}; k1Zl k1Zl1a } 
\sing{a}{\skti k\'s\'sa}{\skt k1ZZa}
\sing{c}{\skti k\d sa}{\skt [a `[a }
\dual{m}{\skti k\d s\d na}{\skt [Na `[Na}{\skt `[`Na [`Na } 
\dual{p}{\skti k\d s\d nya}{\skt [Nya `[Nya}{\skt `[`Nya [`Nya } 
\sing{c}{\skti k\d sma}{\skt [ma `[ma }
\sing{a}{\skti k\d smya}{\skt [m1ya `[m1ya }
\sing{c}{\skti k\d sya}{\skt [ya `[ya }
\sing{a}{\skti k\d sra}{\skt [r2a `[r2a }
\dual{a}{\skti k\d sla}{\skt [l `[l}{\skt `[l1a [l1a }
\sing{c}{\skti k\d sva}{\skt [va `[va }
\sing{p}{\skti ksa}{\skt k1sa} 
\sing{a}{\skti ks\d ta}{\skt k1s1f}
\sing{a}{\skti ks\d tra}{\skt k1s1f\ZH{-12}{r1}}
\sing{a}{\skti ks\d da}{\skt k1s1\ZM{cLe}.q}
\sing{p}{\skti kstra}{\skt k1s1:t4a} 
\sing{a}{\skti kspra}{\skt k1s1\ZM{cLe}.pra}
\dual{a}{\skti kspla}{\skt k1s1\ZM{cLe}.p\ZM{lbl0FI0PE}; k1s1\ZM{cLe}.pl}{\skt k1s1\ZM{cLe}.pl1a k1s1.p\ZM{qLepbL0bE}a }
\sing{p}{\skti ksra}{\skt k1s1\ZM{aLeDDr}:a} 
\sing{p}{\skti ksva}{\skt k1s1va}
\sing{a}{\skti khkha}{\skt K.Ka}
\sing{a}{\skti khta}{\skt K.ta}
\sing{a}{\skti khna}{\skt \ZM{0NKFRIDbnMbeRbE}*.a K.na }
\sing{a}{\skti khnya}{\skt \ZM{0NKFRIDbnMbeRbE}*.ay1a K.nya }
\sing{a}{\skti khma}{\skt K.ma}
\sing{c}{\skti khya}{\skt K.ya}
\sing{c}{\skti khra}{\skt K.r2a}
\sing{a}{\skti khla}{\skt K.l K.l1a }
\sing{a}{\skti khva}{\skt K.va}
\sing{a}{\skti kh\'sa}{\skt K.Za}
\sing{a}{\skti khsa}{\skt K.sa}
\sing{a}{\skti gga}{\skt gga}
\sing{p}{\skti ggha}{\skt gGa} 
\sing{a}{\skti gghya}{\skt gGya}
\sing{a}{\skti gja}{\skt g\ZS{-2}ia}
\sing{x}{\skti gj\~na}{\skt g.]a g\ZS{-2}`]a}
\sing{a}{\skti gjya}{\skt g\ZS{-2}iya}
\sing{a}{\skti gjha}{\skt gJa g`J }
\sing{a}{\skti g\d da}{\skt gq}
\sing{a}{\skti g\d dha}{\skt gQ}
\sing{a}{\skti g\d na}{\skt gNa g`Na }
\sing{p}{\skti gda}{\skt gd}
\sing{a}{\skti gddha}{\skt g;d\ZM{t0Dj0b}}
\sing{a}{\skti gddhva}{\skt g;d\ZM{t0Dhfv}}
\sing{a}{\skti gdya}{\skt gd\ZM{fByF0E};a gdy1a }
\sing{a}{\skti gdva}{\skt gd\ZM{oau}}
\sing{a}{\skti gdha}{\skt gDa}
\sing{a}{\skti gdhya}{\skt gDya}
\sing{a}{\skti gdhra}{\skt gDra}
\sing{a}{\skti gdhva}{\skt gDva}
\sing{m}{\skti gna}{\skt \ZM{0NgFRI0FnIFe}+;a gna } 
\sing{m}{\skti gnya}{\skt \ZM{0NgFRI0FnIFe}+;ay1a gnya }
\sing{a}{\skti gba}{\skt gba}
\sing{a}{\skti gbha}{\skt gBa}
\sing{m}{\skti gbhya}{\skt gBya}
\sing{p}{\skti gma}{\skt gma} 
\sing{a}{\skti gmya}{\skt gm1ya}
\sing{c}{\skti gya}{\skt gya}
\sing{c}{\skti gra}{\skt gr4a}
\sing{c}{\skti grya}{\skt gr4ya}
\sing{m}{\skti gla}{\skt gl gl1a } 
\sing{p}{\skti gva}{\skt gva} 
\sing{a}{\skti gsa}{\skt gsa}
\sing{a}{\skti g+ha}{\skt gh}
\sing{c}{\skti ghna}{\skt \ZM{BNHMDeDDnR0ARbA}*+ ;Gna }
\sing{c}{\skti ghnya}{\skt \ZM{BNHMDeDDnR0ARbA}*+y1a ;Gnya }
\sing{c}{\skti ghma}{\skt ;Gma}
\sing{c}{\skti ghya}{\skt ;Gya}
\sing{c}{\skti ghra}{\skt ;Gra}
\sing{a}{\skti ghrya}{\skt ;Grya}
\sing{a}{\skti ghla}{\skt ;Gl ;Gl1a }
\sing{p}{\skti ghva}{\skt ;Gva} 
\sing{c}{\skti \.nka}{\skt \ZM{0PqPOM0bvJbPJbEJdE}*:}
\sing{c}{\skti \.nkta}{\skt \ZM{0PqPOM0BoPhY0ktEceJbEJfE}*:}
\sing{c}{\skti \.nktya}{\skt *\ZM{pPq0OMpBo0hYpktkcefbEffE0hyLnA}+:a}
\sing{a}{\skti \.nktra}{\skt \ZM{0PqPOM0BoPhY0ktEceJbEJfE}*:\ZP{-10}{-12}{r2}}
\sing{a}{\skti \.nktrya}{\skt *\ZM{pPq0OMpBo0hYpktkcefbEffE0hyLnAftrfnE}+:a}
\sing{a}{\skti \.nktva}{\skt \ZM{DPqTOM0BoUhYPbE0ltHfVPhEMBi}*+}
\sing{a}{\skti \.nktha}{\skt *.\ZM{rPqbOMrbvhbwhdEBbTNdEh0I}\ZS{10}:a *.\ZM{rPqbOMrbvhbwhdEBbTNdEh0I}+;a }
\sing{c}{\skti \.nkya}{\skt *\ZM{pPq0OMpbvfdwfdEf0IBbYBbyNdE}+;a}
\sing{p}{\skti \.nkra}{\skt \ZM{0PqPOM0bvJbPJbEJdE}*:\ZP{-10}{-10}{r1}} 
\sing{p}{\skti \.nkva}{\skt \ZM{0PqPOM0bvJbPJbE0nvJpE}*:} 
\sing{c}{\skti \.nk\d sa}{\skt \ZM{0PqPOM0dxKdePnA}*: \ZM{0PqPOM0hXPBEPfE}*: }
\sing{a}{\skti \.nk\d s\d na}{\skt *\ZM{p0xdPqLOMbbNbBILBELdEd0a}* *\ZM{pbXbPqNOM0bN0BINDINbEN0E}*. *\ZM{phX0PqPOMbbOPDIPdE}*: *\ZM{pBx0PqPOMbbOPBEPdEdBa}*: }
\sing{a}{\skti \.nk\d s\d nva}{\skt *\ZM{p0xdPqLOMbbNbBILDIBnvLtAd0a}* *\ZM{pjXbPqNOM0bN0BINDIDlvNrA}*. *\ZM{phX0PqPOMbbOPBEFrvPxA}*: *\ZM{pBx0PqPOMbbOPBEErvPxAdBa}*: }
\sing{a}{\skti \.nk\d sma}{\skt *\ZM{jPqfbeFOMpbxbbmIbiPdE}*a *\ZM{hPqHOMrjXdbmKbePfE}*a }
\sing{a}{\skti \.nk\d sya}{\skt *\ZM{pPq0OMmdxbda0dY0dyLmA}+:a *\ZM{pPq0OMnhXB0YB0yNfE}+;a }
\sing{a}{\skti \.nk\d sra}{\skt \ZM{0PqPOM0dxKdePnA}*:\ZP{-4}{-14}{r1} \ZM{0PqPOM0hXPBEPfE}*:\ZP{-4}{-12}{r2} }
\sing{c}{\skti \.nk\d sva}{\skt \ZM{FPqVOM0bxLcvVfEVBE}*+. \ZM{HPqXOM0gXNbvXBEXdE}*+: }
\sing{c}{\skti \.nkha}{\skt \ZM{BPqROM0bKRBERfEFAI}*;}
\sing{a}{\skti \.nkhna}{\skt \ZM{BPqROM0bKRnAFAIDpnRvAMpe}*;}
\sing{c}{\skti \.nkhya}{\skt *\ZM{nPqBOMpbKjBIBbyNmA}+;a}
\sing{a}{\skti \.nkhra}{\skt \ZM{BPqROM0bKRBERfEFAI}*;\ZP{-4}{-12}{r2}}
\sing{c}{\skti \.nga}{\skt \ZM{0PqPOM0bgNaENdE}*:}
\sing{a}{\skti \.ngma}{\skt *\ZM{lPqpagdbmNbEjBIFOMIbe}+;a}
\sing{c}{\skti \.ngya}{\skt *\ZM{pPq0OMpbgbdYbdyJdE}+.a}
\sing{a}{\skti \.ngra}{\skt \ZM{0PqPOM0bgNaENdE}*:\ZP{-6}{-10}{r1}}
\sing{a}{\skti \.ngla}{\skt \ZM{FPqVOM00gFEILdlXDI}*+: *\ZM{lPqDOMp0gjBIddLLdE}+:a }
\sing{p}{\skti \.ngva}{\skt \ZM{DPqTOM00gFBITbETDILbV}*+} 
\sing{c}{\skti \.ngha}{\skt \ZM{0PqPOM0bHPBEPdE}*:}
\sing{c}{\skti \.nghya}{\skt *\ZM{pPq0OMpbH0DI0bI00yLhA}+:a}
\sing{c}{\skti \.nghra}{\skt \ZM{0PqPOM0bHPBEPdE}*:\ZP{-4}{-4}{r1}}
\sing{c}{\skti \.n\.na}{\skt \ZM{0PqPOM0bqPbM}*:}
\sing{p}{\skti \.nca}{\skt \ZM{BPqROM0fcRBERbE}*;} 
\sing{p}{\skti \.nja}{\skt \ZM{0PqPOMbhjPdEPBE}*:} 
\sing{p}{\skti \.n\d na}{\skt \ZM{0PqPOMBbNBBIPBEPbE}*: \ZM{DPqTOM0bOFBIRaERdE}*+ } 
\sing{p}{\skti \.n\d nva}{\skt \ZM{0PqPOMBbNBBIPDIFnvPtA}*: \ZM{BPqROMFAIRBERdE0bOFrkRxA}*; } 
\sing{p}{\skti \.nta}{\skt \ZM{0PqPOMBhtI0eNcENaE}*:} 
\sing{p}{\skti \.ndha}{\skt \ZM{DPqTOMD0DT0ETDI}*+} 
\sing{c}{\skti \.nna}{\skt \ZM{0PqPOM00nI0eNaE}*:}
\sing{p}{\skti \.npa}{\skt \ZM{0PqPOMDapNfENAI}*:} 
\sing{p}{\skti \.npra}{\skt \ZM{0PqPOMDapNfENAI}*:\ZP{-6}{-12}{@R}} 
\sing{p}{\skti \.nbha}{\skt \ZM{BPqROM0bBPaEPbE}*;} 
\sing{p}{\skti \.nbhya}{\skt *\ZM{pPq0OMpdB0dY0dyLdE}+:a} 
\sing{c}{\skti \.nma}{\skt \ZM{0PqPOMDbmQbiX0AXhA}*+;}
\sing{c}{\skti \.nya}{\skt zy3a}
\sing{a}{\skti \.nra}{\skt .z\ZH{-12}{r1}}
\sing{a}{\skti \.nrva}{\skt z\ZM{rfuhhEhdInhR}}
\sing{a}{\skti \.nrvya}{\skt \ZM{0PqPOMD0vHbrN0yZ0E}*+.a}
\sing{p}{\skti \.nla}{\skt \ZM{0PqPOM0dlL0I}*: \ZM{0PqPOM0dLPBEPdE}*: } 
\sing{p}{\skti \.nva}{\skt z\ZM{rfuhhEhdI}} 
\sing{p}{\skti \.n\'sa}{\skt \ZM{0PqPOM00ZPdEPDI}*:} 
\sing{a}{\skti \.n\d sa}{\skt \ZM{0PqPOMDaSNdENAI}*:}
\sing{p}{\skti \.nsa}{\skt \ZM{BPqROM0bsKbiRbERDI}*;} 
\sing{p}{\skti \.nstha}{\skt *\ZM{pPq0OMpbsebiBbTNjA}.\ZS{8}:a *\ZM{pPq0OMpbsebiBbTNjA}+;a } 
\sing{p}{\skti \.nspa}{\skt \ZM{FPqVOM0bsNbpXfEXBEFEIIbe}*+.} 
\sing{p}{\skti \.nsva}{\skt \ZM{DPqTOM0bsFBILbVTBETdE}*+} 
\sing{p}{\skti \.nha}{\skt \ZM{0PqPOMDbh}*:} 
\sing{p}{\skti \.nhya}{\skt \ZM{0PqPOMDbhLhyXnA}*+a} 
\sing{p}{\skti \.nhra}{\skt \ZM{0PqPOMFbhEnMCpM}*:} 
\sing{p}{\skti cka}{\skt ..ck} 
\sing{p}{\skti ckta}{\skt ..ck2 ..ck1ta } 
\sing{p}{\skti ckha}{\skt ..cKa} 
\sing{c}{\skti cca}{\skt c1a ..cca }
\sing{a}{\skti ccya}{\skt c1ya ..ccya }
\sing{c}{\skti ccha}{\skt ..cC}
\sing{m}{\skti cchya}{\skt ..cC1 ..cC.y1a } 
\sing{c}{\skti cchra}{\skt ..cC\ZH{-12}{r1}}
\sing{p}{\skti cchla}{\skt ..c\ZM{0PC0dlLAI}*: ..c\ZM{0PC0dLPdEPbIP0I}*: } 
\sing{p}{\skti cchva}{\skt ..cC\ZM{rguheEhhE}} 
\sing{c}{\skti c\~na}{\skt \ZM{0JcBBzRdA}*.a ..c.Va }
\sing{p}{\skti cta}{\skt ..cta} 
\sing{p}{\skti ctrya}{\skt ..c;t4ya} 
\sing{a}{\skti cna}{\skt \ZM{0JcDDnMDeRDE}*.a ..cna }
\sing{p}{\skti cpa}{\skt ..cpa} 
\sing{p}{\skti cpra}{\skt ..cpra} 
\sing{p}{\skti cpha}{\skt ..cP} 
\sing{c}{\skti cma}{\skt ..cma}
\sing{c}{\skti cya}{\skt ..cya}
\sing{a}{\skti cra}{\skt ..cr4a}
\sing{p}{\skti cla}{\skt ..cl ..cl1a } 
\sing{p}{\skti cva}{\skt ..cva} 
\sing{p}{\skti cvya}{\skt ..cv.ya} 
\sing{a}{\skti c\d sa}{\skt ..cSa}
\sing{p}{\skti csa}{\skt ..csa} 
\sing{p}{\skti csva}{\skt ..cs1va} 
\sing{a}{\skti chna}{\skt \ZM{0PC00nLbELAIG0e}*:}
\sing{a}{\skti chma}{\skt \ZM{0PCDbmQbiXbEJ0I}*+a C.m2a }
\sing{c}{\skti chya}{\skt C1 C.y1a }
\sing{c}{\skti chra}{\skt C\ZH{-12}{r1}}
\sing{a}{\skti chrya}{\skt C1\ZH{-24}{r1} C\ZH{-14}{r1}.y1a }
\sing{a}{\skti chla}{\skt \ZM{0PC0dlLAI}*: \ZM{0PC0dLPdEPbIP0I}*: }
\sing{a}{\skti chva}{\skt C\ZM{rguheEhhE}}
\sing{p}{\skti jka}{\skt .j1k} 
\sing{c}{\skti jja}{\skt \ZM{0Jj0djRdA}*.a j2a }
\sing{a}{\skti jj\~na}{\skt j\ZM{cNe}.]a j\ZS{-2}`]a }
\sing{a}{\skti jjya}{\skt \ZM{0Jj0djRdA}*.ay1a j2ya }
\sing{p}{\skti jjva}{\skt j2va} 
\sing{c}{\skti jjha}{\skt jJa j1`J }
\sing{a}{\skti jjhra}{\skt jJr1a j1`J\ZH{-8}{r} }
\sing{c}{\skti j\~na}{\skt :]a `]a }
\sing{c}{\skti j\~nya}{\skt :]ya `]ya }
\sing{a}{\skti j\~nra}{\skt :]r2a `]r2a }
\sing{a}{\skti j\d ta}{\skt .j1f}
\sing{a}{\skti j\d da}{\skt .jq}
\sing{p}{\skti jda}{\skt .j1d} 
\sing{a}{\skti jna}{\skt \ZM{0JjDDnMDeRDE}*.a .j1na }
\sing{a}{\skti jpa}{\skt .jpa} 
\sing{p}{\skti jba}{\skt .j1ba} 
\sing{p}{\skti jbhya}{\skt .j1Bya} 
\sing{p}{\skti jbhra}{\skt .j1Bra} 
\sing{c}{\skti jma}{\skt .j1ma}
\sing{c}{\skti jya}{\skt .j1ya}
\sing{c}{\skti jra}{\skt .jr1a}
\sing{a}{\skti jla}{\skt .j1l .j1l1a }
\sing{c}{\skti jva}{\skt .j1va}
\sing{a}{\skti jhjha}{\skt JJa \ZM{aXiFPE0LmRBYRXe}\ZS{22}`J }
\sing{a}{\skti jhna}{\skt \ZM{0PJBbnKbiRbE}*.a B\ZM{jFnHBYhLoaFe}:a }
\sing{a}{\skti jhma}{\skt Jam2a \ZM{aXiFPE0LmRBYRXe}\ZS{22}ma }
\sing{a}{\skti jhya}{\skt Jay1a `Jy1a }
\sing{a}{\skti jhra}{\skt Jr1a `J\ZH{-8}{@R} }
\sing{a}{\skti jhla}{\skt Jl .\ZM{cXiDRIbNmXDYF0lHNoRPERJE}\ZS{12}+; \ZM{aXiFRI0NmZDYD0LJNoT0E}\ZS{14};a. Jl1a }
\sing{a}{\skti jhva}{\skt Jva \ZM{JBuTBE}`J }
\sing{p}{\skti \~nka}{\skt Vk} 
\sing{p}{\skti \~nkva}{\skt V\ZM{0NkLNPLPE00kLhA}*: Vk1va } 
\sing{p}{\skti \~nkta}{\skt Vk2 Vk1ta } 
\sing{p}{\skti \~nkha}{\skt VKa} 
\sing{p}{\skti \~ngra}{\skt Vgr4a} 
\sing{c}{\skti \~nca}{\skt \ZM{BNz0dcRfA}*.a Vca }
\sing{a}{\skti \~nccha}{\skt \ZM{BOz0bc}*.C VcC }
\sing{c}{\skti \~ncma}{\skt \ZM{BOz0bc}*.am2a Vcma }
\sing{c}{\skti \~ncya}{\skt \ZM{BNz0dcRfA}*.ay1a Vcya }
\sing{a}{\skti \~ncva}{\skt *\ZM{pOzcOi0JupccLDE}+:a Vcva }
\sing{c}{\skti \~ncha}{\skt VC}
\sing{a}{\skti \~nchya}{\skt VC1 VC.y1a }
\sing{a}{\skti \~nchra}{\skt VC\ZH{-12}{r1}}
\sing{c}{\skti \~nja}{\skt \ZM{BNz0djR0ARdA}*+ V\ZS{-6}ia }
\sing{p}{\skti \~nj\~na}{\skt V]a V\ZS{-2}`]a } 
\sing{a}{\skti \~njma}{\skt \ZM{BNz0djR0ARdA}*+m2a V\ZS{-6}ima }
\sing{c}{\skti \~njya}{\skt \ZM{BNz0djR0ARdA}*+y1a V\ZS{-6}iya }
\sing{p}{\skti \~njva}{\skt \ZM{0cj0OzMEiNJuZBEMOaLOi}*+.a V\ZS{-6}iva } 
\sing{a}{\skti \~njha}{\skt VJa V`J }
\sing{p}{\skti \~n\~na}{\skt \ZM{0Oz0BzPBE}*a VVa } 
\sing{p}{\skti \~n\~nya}{\skt \ZM{0Oz0BzPBE}*ay1a VVya } 
\sing{p}{\skti \~n\d tha}{\skt VF} 
\sing{p}{\skti \~n\d na}{\skt VNa V`Na } 
\sing{p}{\skti \~nda}{\skt Vd} 
\sing{p}{\skti \~ndva}{\skt Vd\ZM{oau}} 
\sing{p}{\skti \~nna}{\skt \ZM{0OzBFnKFe}*a Vna } 
\sing{p}{\skti \~npa}{\skt Vpa} 
\sing{p}{\skti \~nbha}{\skt VBa} 
\sing{p}{\skti \~nbhya}{\skt VBya} 
\sing{p}{\skti \~nma}{\skt Vma} 
\sing{p}{\skti \~nya}{\skt Vya} 
\sing{a}{\skti \~nra}{\skt Vr4a}
\sing{a}{\skti \~nla}{\skt Vl Vl1a }
\sing{p}{\skti \~nva}{\skt Vva} 
\sing{p}{\skti \~n\'sa}{\skt VZa} 
\sing{p}{\skti \~nsa}{\skt Vsa} 
\sing{p}{\skti \~nsna}{\skt V=+:\ZM{rMolHneHegMi}a Vs1na } 
\sing{p}{\skti \d tka}{\skt \ZM{BPf00vJ0PJ0EJbE}*:} 
\sing{a}{\skti \d tkha}{\skt .\ZM{BPf00KRDERdEFBI}*:}
\sing{p}{\skti \d tca}{\skt \ZM{BPf0fcRFER0E}*:} 
\sing{p}{\skti \d tcha}{\skt .\ZM{0Pf00C}*.} 
\sing{c}{\skti \d t\d ta}{\skt \ZM{0Pf00f}*}
\sing{p}{\skti \d t\d tya}{\skt \ZM{0Pf00f}*.y1a} 
\sing{p}{\skti \d t\d tha}{\skt \ZM{0Pf00F}*} 
\sing{a}{\skti \d t\d thya}{\skt \ZM{0Pf00F}*.y1a}
\sing{a}{\skti \d t\d dha}{\skt \ZM{0PfB0Q}*}
\sing{a}{\skti \d t\d na}{\skt \ZM{0PfC0NCCIP0EPDE}* .\ZM{BPf00OFBIRbERDE}*. }
\sing{p}{\skti \d tta}{\skt \ZM{0PfBftIBeNbENAE}*} 
\sing{p}{\skti \d ttra}{\skt \ZM{0PfLdEL0ELhrB0w}*} 
\sing{a}{\skti \d ttsa}{\skt \ZM{0ftG0sHPfXbEXFIQ0i}*+}
\sing{a}{\skti \d ttha}{\skt \ZM{0PfLdTXjA}+:\ZS{8}:a \ZM{0PfLdTXjA}*+a }
\sing{p}{\skti \d tda}{\skt \ZM{0PfB0d}*} 
\sing{a}{\skti \d tna}{\skt \ZM{0Pf0BnIBeN0ENCI}*}
\sing{p}{\skti \d tpa}{\skt \ZM{0PfBBpLbELBI}*} 
\sing{a}{\skti \d tpha}{\skt \ZM{0PfBBpLbELBIL0P}*:}
\sing{a}{\skti \d tba}{\skt \ZM{0PfCbuNdENAEBbb}*}
\sing{a}{\skti \d tma}{\skt \ZM{0PfB0mQ0eV0E}*;a fm2a }
\sing{c}{\skti \d tya}{\skt fy1a}
\sing{a}{\skti \d tra}{\skt f\ZH{-12}{r1}}
\sing{p}{\skti \d trva}{\skt .f\ZM{pfuffEnhR}} 
\sing{p}{\skti \d tla}{\skt \ZM{0Pf0blLBI}* \ZM{0Pf0bLPdEPDE}* } 
\sing{p}{\skti \d tva}{\skt f\ZM{pfuffE}} 
\sing{p}{\skti \d t\'sa}{\skt \ZM{0Pf0BZPbEPFI}*} 
\sing{p}{\skti \d t\'sva}{\skt \ZM{0BZFPfLbvVbEVDE}*;} 
\sing{p}{\skti \d t\'svya}{\skt *\ZM{pBZd0VF0YF0ymPfRbE}*.a} 
\sing{a}{\skti \d t\d sa}{\skt \ZM{0PfB0SLbELBI}*}
\sing{p}{\skti \d tsa}{\skt .\ZM{DPf00sK0iRbERCI}*:} 
\sing{p}{\skti \d tsta}{\skt \ZM{00sNftVbEVDEFPfI0eFFE}*;} 
\sing{a}{\skti \d tsla}{\skt .\ZM{FPf00sFFEL0lXFIVLa}*+: .*\ZM{jPfp0sjFEd0LL0E}+:a }
\sing{p}{\skti \d tsva}{\skt .\ZM{FPf00sN0VV0EFFEVFII0e}*+} 
\sing{a}{\skti \d th\d tha}{\skt \ZM{0PF00F}*}
\sing{a}{\skti \d th\d na}{\skt \ZM{0PFC0NCCIP0EPDE}* .\ZM{BPF00OFBIRbERDE}*. }
\sing{a}{\skti \d ththa}{\skt \ZM{0PFLbTXjA}+:\ZS{8}:a \ZM{0PFLbTXjA}*+a }
\sing{a}{\skti \d ththya}{\skt \ZM{0PFLbTXjA}+:\ZS{8}:ay1a \ZM{0PFLbTXjA}*+ay1a }
\sing{a}{\skti \d thna}{\skt \ZM{0PF0BnIBeN0ENAE}*}
\sing{a}{\skti \d thma}{\skt \ZM{0PFB0mQ0eV0E}*;a F:m2a }
\sing{c}{\skti \d thya}{\skt F:y3a Fy1a }
\sing{c}{\skti \d thra}{\skt F\ZH{-10}{r1}}
\sing{a}{\skti \d thla}{\skt \ZM{0PF0blLBI}* \ZM{0PF0bLPbEPDE}* }
\sing{a}{\skti \d thva}{\skt F\ZM{pfufgEfhE}}
\sing{p}{\skti \d thsa}{\skt \ZM{DPF00sK0iRAERbE}*:} 
\sing{c}{\skti \d dga}{\skt .\ZM{0Pq0bgNaENdE}*}
\sing{c}{\skti \d dgya}{\skt .*\ZM{pPqpbgbdYbdyJjA}+.a}
\sing{c}{\skti \d dgha}{\skt \ZM{0Pq0bHPBEPdE}*}
\sing{c}{\skti \d dghra}{\skt \ZM{0Pq0bHPBEPdE}*\ZV{-4}{r1}}
\sing{a}{\skti \d dja}{\skt .\ZM{0PqbhjPdEPBE}*}
\sing{a}{\skti \d djha}{\skt \ZM{DPq00BPbEPdEO0eUjY}*; \ZM{BPq0bJRBERfE}*. }
\sing{a}{\skti \d d\d ta}{\skt \ZM{0Pq0bf}*}
\sing{p}{\skti \d d\d da}{\skt \ZM{0Pq0bq}*} 
\sing{p}{\skti \d d\d dya}{\skt \ZM{0Pq0bq}*.y1a} 
\sing{p}{\skti \d d\d dva}{\skt \ZM{0Pq0bqDrVLtE}*} 
\sing{p}{\skti \d d\d dha}{\skt \ZM{0PqBbQ}*} 
\sing{a}{\skti \d d\d dhva}{\skt \ZM{0PqBbQDrVLsE}*}
\sing{a}{\skti \d d\d na}{\skt \ZM{0PqAbNADIPBEPdE}* .\ZM{DPq0bOFBIRBERdE}*. }
\sing{a}{\skti \d dna}{\skt \ZM{0Pq00nI0eNbENaE}*}
\sing{a}{\skti \d dba}{\skt q\ZM{nfudhEddInfb}}
\sing{a}{\skti \d dbha}{\skt \ZM{BPq0bBRbERBEMbe}*.}
\sing{p}{\skti \d dbhya}{\skt *\ZM{pPqpdB0dY0dyLjA}+:a} 
\sing{c}{\skti \d dma}{\skt \ZM{0PqDbmObiVbE}*;a q:m2a }
\sing{c}{\skti \d dya}{\skt q:y3a qy1a }
\sing{a}{\skti \d dra}{\skt .q\ZH{-8}{r1}}
\sing{a}{\skti \d dla}{\skt \ZM{0Pq0dlL0I}* \ZM{0Pq0dLPBEPdE}* }
\sing{p}{\skti \d dva}{\skt q\ZM{nfudhEddI}} 
\sing{p}{\skti \d dvya}{\skt q\ZM{nfudhEddI}:y3a q\ZM{nfudhEddI}y1a } 
\sing{a}{\skti \d dh\d dha}{\skt \ZM{0PQ0bQ}*}
\sing{a}{\skti \d dh\d dhya}{\skt \ZM{0PQ0bQ}*y1a}
\sing{a}{\skti \d dh\d na}{\skt \ZM{0PQ0bN0FINBENbE}+; .\ZM{DPQ0bOFBIRBERdE}*. }
\sing{a}{\skti \d dhna}{\skt \ZM{0PQ00nNbEI0eNBE}+;}
\sing{a}{\skti \d dhma}{\skt \ZM{0PQB0mO0eT0E}*:a Q.m2a }
\sing{c}{\skti \d dhya}{\skt Q.y3a Qy1a }
\sing{c}{\skti \d dhra}{\skt Q\ZH{-10}{r1}}
\sing{a}{\skti \d dhrya}{\skt Q.y3a\ZH{-20}{r1} Qy1\ZH{-24}{r1}a }
\sing{a}{\skti \d dhla}{\skt \ZM{0PQ0dlLAI}* \ZM{BPQ0dLPBEPdE}* }
\sing{p}{\skti \d dhva}{\skt Q\ZM{ffEpeu}} 
\sing{p}{\skti \d nka}{\skt :Nk .`Nk } 
\sing{p}{\skti \d nca}{\skt :N.ca .`N:ca } 
\sing{p}{\skti \d njya}{\skt :Niya .`Nj1ya } 
\sing{c}{\skti \d n\d ta}{\skt :Nf .`Nf }
\sing{a}{\skti \d n\d tya}{\skt :Nfy1a .`Nfy1a }
\sing{c}{\skti \d n\d tha}{\skt :NF .`NF }
\dual{a}{\skti \d n\d thya}{\skt :NF:y3a .`NF:y3a}{\skt .`NFy1a :NFy1a }
\sing{c}{\skti \d n\d da}{\skt :Nq .`Nq }
\dual{c}{\skti \d n\d dya}{\skt :Nq:y3a .`Nq:y3a}{\skt .`Nqy1a :Nqy1a }
\sing{c}{\skti \d n\d dra}{\skt :Nq\ZH{-8}{r1} .`Nq\ZH{-8}{r1} }
\dual{c}{\skti \d n\d drya}{\skt :Nq\ZH{-8}{r1}y1a .`Nq\ZH{-8}{r1}y1a}{\skt .`Nq\ZH{-8}{r1}y1a :Nq\ZH{-8}{r1}y1a }
\sing{p}{\skti \d n\d dva}{\skt :Nq\ZM{nfudhEddI} .`Nq\ZM{nfudhEddI} } 
\sing{c}{\skti \d n\d dha}{\skt :NQ .`NQ }
\sing{c}{\skti \d n\d na}{\skt :NNa .`N`Na }
\sing{p}{\skti \d n\d nya}{\skt :NNya .`N`Nya } 
\sing{p}{\skti \d nta}{\skt :Nta .`Nta } 
\dual{a}{\skti \d ntha}{\skt :NTa .`NTa}{\skt .`N`Ta :N`Ta }
\dual{a}{\skti \d nthya}{\skt :NTya .`NTya}{\skt .`N`Tya :N`Tya }
\sing{p}{\skti \d nda}{\skt :Nd .`Nd } 
\sing{p}{\skti \d nna}{\skt :\ZM{DBnMBeRdI}Na :Nna .`Nna } 
\sing{p}{\skti \d nbha}{\skt :NBa .`NBa } 
\sing{c}{\skti \d nma}{\skt :Nma .`Nma }
\sing{c}{\skti \d nya}{\skt :Nya .`Nya }
\sing{p}{\skti \d nra}{\skt :N.= :N@Ra .`Nr2a } 
\dual{a}{\skti \d nla}{\skt :Nl .`Nl}{\skt .`Nl1a :Nl1a }
\sing{c}{\skti \d nva}{\skt :Nva .`Nva }
\sing{p}{\skti \d nvya}{\skt :Nv.ya .`Nv.ya } 
\sing{a}{\skti \d nsa}{\skt :Nsa .`Nsa }
\sing{a}{\skti \d nsma}{\skt :Nsma .`Nsma }
\sing{a}{\skti \d nha}{\skt :Nh .`Nh }
\sing{a}{\skti \d nhma}{\skt :Nh2 .`Nh2 }
\sing{a}{\skti \d nhya}{\skt :Nh\ZM{hByDBE}:a .`Nh\ZM{hByDBE}:a }
\sing{a}{\skti \d nhva}{\skt :Nh3\ZM{mAk} .`Nh3\ZM{mAk} }
\sing{c}{\skti tka}{\skt tk}
\sing{a}{\skti tkma}{\skt tk4 tk1ma }
\sing{a}{\skti tkya}{\skt tky2+.a tk1ya }
\sing{p}{\skti tkra}{\skt tk\ZM{l0R}} 
\dual{a}{\skti tkla}{\skt t\ZM{0NkLNPLPELFI00l}*: t\ZM{0NkLNPL0ALbEd0L}*:}{\skt tk1l1a tk1l }
\sing{a}{\skti tkva}{\skt t\ZM{0NkLNPLPE00kLhA}*: tk1va }
\sing{p}{\skti tk\d sa}{\skt t[a t`[a } 
\sing{a}{\skti tksa}{\skt tk1sa}
\sing{p}{\skti tkha}{\skt tKa} 
\sing{a}{\skti tkhna}{\skt t\ZM{0NKFRIDbnMbeRbE}*.a tK.na }
\sing{a}{\skti tkhra}{\skt tK.r2a}
\sing{a}{\skti tga}{\skt tga}
\sing{a}{\skti tgha}{\skt tGa}
\sing{a}{\skti t\.na}{\skt tz}
\sing{a}{\skti tca}{\skt t:ca}
\sing{a}{\skti tcha}{\skt tC}
\sing{a}{\skti tja}{\skt tja}
\sing{a}{\skti tjha}{\skt tJa t`J }
\sing{a}{\skti t\~na}{\skt tVa}
\sing{a}{\skti t\d ta}{\skt tf}
\sing{a}{\skti t\d tha}{\skt tF}
\sing{a}{\skti t\d da}{\skt tq}
\sing{a}{\skti t\d dha}{\skt tQ}
\sing{a}{\skti t\d na}{\skt tNa t`Na }
\sing{c}{\skti tta}{\skt t1a tta }
\sing{p}{\skti ttka}{\skt t1k ttk } 
\dual{a}{\skti ttk\d sa}{\skt t1[a tt[a}{\skt tt`[a t1`[a }
\sing{a}{\skti ttna}{\skt tt2a t1na ttna }
\sing{c}{\skti ttya}{\skt t1ya ttya }
\sing{c}{\skti ttra}{\skt \ZM{0DtHLaaAb}+;t4a}
\sing{a}{\skti ttrya}{\skt \ZM{0DtHLaaAb}+;t4ya}
\sing{c}{\skti ttva}{\skt t1va ttva }
\sing{c}{\skti ttha}{\skt tTa t`Ta }
\sing{a}{\skti tthya}{\skt tTya t`Tya }
\sing{a}{\skti tda}{\skt td}
\sing{a}{\skti tdha}{\skt tDa}
\sing{c}{\skti tna}{\skt t2a tna }
\sing{c}{\skti tnya}{\skt t2ya tnya }
\sing{p}{\skti tnva}{\skt t2\ZM{bLu}+.a tnva } 
\sing{c}{\skti tpa}{\skt tpa}
\sing{a}{\skti tppha}{\skt tpP}
\sing{c}{\skti tpra}{\skt tpra}
\sing{a}{\skti tpla}{\skt tp\ZM{lbl0FI0PE}; tpl tpl1a :tp\ZM{pbL0bE}a }
\sing{p}{\skti tpha}{\skt tP} 
\sing{a}{\skti tphra}{\skt tP\ZH{-10}{r}}
\sing{a}{\skti tba}{\skt tba}
\sing{a}{\skti tbha}{\skt tBa}
\sing{c}{\skti tma}{\skt tma}
\sing{c}{\skti tmya}{\skt tm1ya}
\sing{c}{\skti tya}{\skt tya}
\sing{c}{\skti tra}{\skt t3a}
\sing{c}{\skti trya}{\skt t3ya}
\sing{a}{\skti trva}{\skt t3va}
\sing{a}{\skti tla}{\skt tl tl1a }
\sing{c}{\skti tva}{\skt tva}
\sing{p}{\skti tvya}{\skt tv.ya} 
\sing{a}{\skti t\'sa}{\skt tZa}
\sing{p}{\skti t\d sa}{\skt tSa} 
\sing{p}{\skti t\d s\d tha}{\skt tS2 tSF } 
\sing{c}{\skti tsa}{\skt tsa}
\sing{a}{\skti tska}{\skt ts1k}
\sing{p}{\skti tsta}{\skt ts1ta} 
\sing{p}{\skti tstha}{\skt ts1Ta ts1`Ta } 
\sing{c}{\skti tsna}{\skt t=+:\ZM{rMolHneHegMi}a ts1na }
\sing{c}{\skti tsnya}{\skt t=+:\ZM{rMolHneHegMi}ya ts1nya }
\sing{p}{\skti tsma}{\skt tsma} 
\sing{a}{\skti tsmya}{\skt tsm1ya}
\sing{m}{\skti tsya}{\skt ts1ya} 
\sing{a}{\skti tsra}{\skt ts1\ZM{aLeDDr}:a}
\sing{p}{\skti tsva}{\skt ts1va} 
\sing{a}{\skti t+ha}{\skt th}
\sing{a}{\skti ththa}{\skt TTa `T`Ta }
\sing{a}{\skti thna}{\skt T\ZM{pBneBe0BE}a `T\ZM{pBneBe0BE}a `Tna Tna }
\sing{a}{\skti thma}{\skt Tm1a `Tm1a }
\sing{c}{\skti thya}{\skt Tya `Tya }
\sing{a}{\skti thra}{\skt Tra `Tra }
\dual{a}{\skti thla}{\skt Tl `Tl}{\skt `Tl1a Tl1a }
\sing{p}{\skti thva}{\skt Tva `Tva } 
\sing{c}{\skti dga}{\skt .d2\ZM{rbgddE}}
\sing{a}{\skti dgya}{\skt d2\ZM{rbgdByHBE}+a .d2\ZM{rbgddE}y1a }
\sing{c}{\skti dgra}{\skt .d2\ZM{rbgddE}\ZP{-4}{-6}{r1}}
\sing{c}{\skti dgha}{\skt .d2\ZM{t0HdbE}}
\sing{c}{\skti dghra}{\skt .d2\ZM{t0HdbE}\ZP{-4}{-2}{r1}}
\sing{a}{\skti djha}{\skt .d2\ZM{vaJddEdfE} :d2\ZM{v0Bg0iBjYddE}: }
\sing{p}{\skti d\d da}{\skt d2\ZM{pbq}} 
\sing{p}{\skti d\d d\d da}{\skt d2\ZM{pbqptq}} 
\sing{a}{\skti d\d dha}{\skt d2\ZM{ndQ}}
\sing{c}{\skti dda}{\skt d1}
\sing{a}{\skti ddba}{\skt d1\ZM{oekoeb}}
\sing{a}{\skti ddbra}{\skt d1\ZM{oekoeb}\ZP{-8}{-10}{r1}}
\sing{c}{\skti ddya}{\skt d1\ZM{dbyHbE}+a d1y1a }
\sing{p}{\skti ddra}{\skt d1\ZH{-8}{r1}} 
\sing{a}{\skti ddva}{\skt d1\ZM{oek}}
\sing{p}{\skti ddvya}{\skt d1\ZM{oekdbyHbE}+a d1\ZM{oek}y1a } 
\sing{a}{\skti ddvra}{\skt d1\ZM{oek}\ZP{-8}{-10}{r1}}
\sing{c}{\skti ddha}{\skt .;d\ZM{t0Dj0b}}
\sing{a}{\skti ddhna}{\skt .;d2\ZM{tBDrhnihedfE}}
\sing{a}{\skti ddhnya}{\skt .;d2\ZM{tBDrhnihedfE}y1a}
\sing{a}{\skti ddhma}{\skt .;d2\ZM{tBDjhmCheHnAdbE}+a .;d\ZM{t0Dj0b}m2a }
\sing{c}{\skti ddhya}{\skt .;d\ZM{t0DfByF0E};a .;d\ZM{t0Dj0b}y1a }
\sing{p}{\skti ddhra}{\skt .;d\ZM{t0Dj0b}\ZP{-10}{-6}{r1}} 
\sing{a}{\skti ddhrya}{\skt .;d\ZM{t0DfByF0EfjR};a .;d\ZM{t0Dj0b}\ZP{-10}{-6}{r1}y1a }
\sing{a}{\skti ddhva}{\skt .;d\ZM{t0Dhfv}}
\sing{c}{\skti dna}{\skt .d2\ZM{r0ni0ed0E}}
\sing{c}{\skti dba}{\skt d\ZM{oaupabj0b}}
\sing{p}{\skti dbra}{\skt d\ZM{oaupabj0b}\ZP{-8}{-6}{r1}} 
\sing{c}{\skti dbha}{\skt .;d2\ZM{x0Bi0ed0E}}
\sing{c}{\skti dbhya}{\skt .;d\ZM{x0Bi0efByF0E};a .;d2\ZM{x0Bi0ed0E}y1a }
\sing{a}{\skti dbhra}{\skt .;d2\ZM{x0Bi0ed0E}\ZP{-4}{-6}{r1}}
\sing{c}{\skti dma}{\skt d2\ZM{j0mC0eH0E}+a dm2a }
\sing{a}{\skti dmya}{\skt d2\ZM{j0mC0eH0E}+ay1a dm2ay1a }
\sing{c}{\skti dya}{\skt d\ZM{fByF0E};a dy1a }
\sing{c}{\skti dra}{\skt d\ZP{-8}{-4}{@R}}
\sing{c}{\skti drya}{\skt d\ZM{fByF0Ehdr};a d\ZP{-8}{-4}{@R}y1a }
\sing{p}{\skti drva}{\skt .d\ZM{jdRnbu}} 
\sing{a}{\skti dla}{\skt d2\ZM{pdl} .d2\ZM{tdLdfE} }
\sing{c}{\skti dva}{\skt d\ZM{oau}}
\sing{c}{\skti dvya}{\skt d\ZM{oaufByF0E};a d\ZM{oau}y1a }
\sing{a}{\skti dvra}{\skt d\ZM{oau}\ZP{-8}{-6}{r1}}
\sing{a}{\skti dvrya}{\skt d\ZM{oaufByF0EinrhlIhnI};a d\ZM{oau}\ZP{-8}{-6}{r1}y1a }
\sing{a}{\skti dhda}{\skt ;Dd} 
\sing{c}{\skti dhna}{\skt \ZM{0XiBNHMXeDDnRDENXiKDi}\ZS{14}:a ;Dna }
\sing{c}{\skti dhnya}{\skt \ZM{0XiBNHMXeDDnRDENXiKDi}\ZS{14}:ay1a ;Dnya }
\sing{a}{\skti dhnva}{\skt .\ZM{aXeDPGFGnPGe}\ZS{18}va ;Dnva }
\sing{c}{\skti dhma}{\skt ;Dm1\ZM{cLe}.a}
\sing{c}{\skti dhya}{\skt ;Dya}
\sing{c}{\skti dhra}{\skt ;Dra}
\sing{c}{\skti dhrya}{\skt ;Drya}
\sing{a}{\skti dhla}{\skt ;Dl ;Dl1a }
\sing{c}{\skti dhva}{\skt ;Dva}
\sing{a}{\skti dhvya}{\skt ;Dv.ya}
\sing{a}{\skti dhvra}{\skt ;Dv.ra}
\sing{p}{\skti nka}{\skt nk} 
\sing{p}{\skti nkta}{\skt nk2 nk1ta } 
\sing{a}{\skti nk\d sa}{\skt n[a n`[a }
\sing{p}{\skti nksa}{\skt nk1sa} 
\sing{p}{\skti nkva}{\skt n\ZM{0NkLNPLPE00kLhA}*: nk1va } 
\sing{a}{\skti nga}{\skt nga}
\sing{a}{\skti ngla}{\skt ngl ngl1a }
\sing{a}{\skti nghya}{\skt nGya}
\sing{p}{\skti n\.na}{\skt nz} 
\sing{a}{\skti nca}{\skt \ZM{00cBRnMRe}*.a n.ca }
\sing{a}{\skti nja}{\skt \ZM{00jDRnKRi}*.a n\ZS{-6}ia }
\sing{a}{\skti njya}{\skt \ZM{00jDRnKRi}*.ay1a n\ZS{-6}iya }
\sing{a}{\skti njva}{\skt \ZM{0aj0QnKQiMGiNLu}*+.a n\ZS{-6}iva }
\sing{p}{\skti njha}{\skt nJa n`J } 
\sing{a}{\skti n\d ta}{\skt nf}
\sing{a}{\skti n\d tra}{\skt nf\ZH{-12}{r1}}
\sing{a}{\skti n\d da}{\skt nq}
\sing{p}{\skti n\d nva}{\skt nNva n`Nva } 
\sing{c}{\skti nta}{\skt nta}
\sing{a}{\skti ntta}{\skt \ZM{0JnLJe}+:t1a ntta }
\sing{a}{\skti nttha}{\skt ntTa nt`Ta }
\sing{a}{\skti ntma}{\skt ntma}
\sing{c}{\skti ntya}{\skt ntya}
\sing{c}{\skti ntra}{\skt n:t4a}
\sing{m}{\skti ntrya}{\skt n:t4ya} 
\sing{p}{\skti ntva}{\skt ntva} 
\sing{a}{\skti ntvya}{\skt ntv.ya}
\sing{p}{\skti ntsa}{\skt ntsa} 
\sing{a}{\skti ntsya}{\skt nts1ya}
\sing{a}{\skti ntsva}{\skt nts1va}
\sing{p}{\skti ntha}{\skt nTa n`Ta } 
\sing{a}{\skti nthya}{\skt nTya n`Tya }
\sing{a}{\skti nthva}{\skt nTva n`Tva }
\sing{c}{\skti nda}{\skt nd}
\sing{a}{\skti nddra}{\skt nd1\ZH{-8}{r1}}
\sing{a}{\skti nddha}{\skt +;\ZM{nNnfNibdDNdE}d2}
\sing{a}{\skti nddhya}{\skt +;\ZM{nPnePibaDNaIN0yZ0E}d2+a +;\ZM{nNnfNibdDNdE}d2y1a }
\sing{a}{\skti ndma}{\skt nd2\ZM{j0mC0eH0E}+a ndm2a }
\sing{a}{\skti ndya}{\skt nd\ZM{fByF0E};a ndy1a }
\sing{c}{\skti ndra}{\skt nd\ZP{-8}{-4}{@R}}
\sing{p}{\skti ndva}{\skt nd\ZM{oau}} 
\sing{c}{\skti ndha}{\skt nDa}
\sing{a}{\skti ndhma}{\skt nDm1\ZM{cLe}.a}
\sing{a}{\skti ndhya}{\skt nDya}
\sing{c}{\skti ndhra}{\skt nDra}
\sing{a}{\skti ndhrya}{\skt nDrya}
\sing{p}{\skti ndhva}{\skt nDva} 
\sing{c}{\skti nna}{\skt n1a \ZM{0Rn0HnIReIHe}+;a }
\sing{a}{\skti nnpa}{\skt n1pa \ZM{0Rn0HnIReIHe}+;pa }
\sing{a}{\skti nnya}{\skt n1ya \ZM{0Rn0HnIReIHe}+;ya }
\sing{c}{\skti npa}{\skt npa}
\sing{c}{\skti npra}{\skt npra}
\sing{a}{\skti npha}{\skt nP}
\sing{a}{\skti nphra}{\skt nP\ZH{-10}{r}}
\sing{p}{\skti nba}{\skt nba} 
\sing{a}{\skti nbra}{\skt nb.ra}
\sing{p}{\skti nbha}{\skt nBa} 
\sing{p}{\skti nbhya}{\skt nBya} 
\sing{a}{\skti nbhva}{\skt nBva}
\sing{c}{\skti nma}{\skt nm1\ZM{cLe}.a}
\sing{a}{\skti nmya}{\skt nm1ya}
\sing{a}{\skti nmra}{\skt nm1\ZM{cLe}.r4a}
\sing{c}{\skti nya}{\skt nya}
\sing{a}{\skti nyva}{\skt nyva}
\sing{c}{\skti nra}{\skt nr4a}
\sing{a}{\skti nrya}{\skt nr4ya}
\sing{p}{\skti nla}{\skt nl nl1a } 
\sing{p}{\skti nva}{\skt nva} 
\sing{p}{\skti nvya}{\skt nv.ya} 
\sing{p}{\skti nvra}{\skt nv.ra} 
\sing{p}{\skti n\'sa}{\skt nZa} 
\sing{a}{\skti n\d sa}{\skt nSa}
\sing{p}{\skti n\d s\d tha}{\skt nS2 nSF } 
\sing{c}{\skti nsa}{\skt nsa}
\sing{a}{\skti ns\d ta}{\skt ns1f}
\sing{a}{\skti ns\d tra}{\skt ns1f\ZH{-12}{r1}}
\sing{p}{\skti nsya}{\skt ns1ya} 
\sing{a}{\skti nha}{\skt nh}
\sing{a}{\skti nhya}{\skt nh\ZM{hByDBE}:a}
\sing{a}{\skti nhra}{\skt nh\ZM{ojr}}
\sing{a}{\skti pka}{\skt :pk}
\sing{a}{\skti pkha}{\skt :pKa}
\sing{p}{\skti pca}{\skt :p.ca} 
\sing{a}{\skti pcha}{\skt :pC}
\sing{a}{\skti p\d ta}{\skt :pf}
\sing{a}{\skti p\d tra}{\skt :pf\ZH{-12}{r1}}
\sing{p}{\skti p\d tha}{\skt :pF} 
\sing{a}{\skti p\d nva}{\skt :pNva :p`Nva }
\sing{c}{\skti pta}{\skt p1a :pta }
\sing{c}{\skti ptya}{\skt p1ya :ptya }
\sing{p}{\skti ptra}{\skt :p;t4a} 
\sing{a}{\skti ptrya}{\skt :p;t4ya}
\sing{a}{\skti ptva}{\skt p1va :ptva }
\sing{p}{\skti ptha}{\skt :pTa :p`Ta } 
\sing{c}{\skti pna}{\skt :p\ZM{lBn0BE}a :pna }
\sing{c}{\skti ppa}{\skt :ppa}
\sing{p}{\skti ppra}{\skt :ppra} 
\sing{a}{\skti ppha}{\skt :pP}
\sing{a}{\skti pba}{\skt :pba}
\sing{c}{\skti pma}{\skt :pma}
\sing{c}{\skti pya}{\skt :pya}
\sing{c}{\skti pra}{\skt :pra}
\sing{a}{\skti prya}{\skt :prya}
\sing{c}{\skti pla}{\skt :p\ZM{lbl0FI0PE}; :pl :pl1a ::p\ZM{pbL0bE}a }
\sing{a}{\skti plya}{\skt :p\ZM{lbl0FI0PE};y1a ::p\ZM{pbL0bE}ay1a :pl1ya }
\sing{a}{\skti plva}{\skt \ZM{0bLPbuZdE}+;pa :pl1va }
\sing{c}{\skti pva}{\skt :pva}
\sing{a}{\skti pvya}{\skt :pv.ya}
\sing{p}{\skti p\'sa}{\skt :p.Za} 
\sing{p}{\skti p\'sya}{\skt :p.Zya} 
\sing{a}{\skti p\d sa}{\skt :pSa}
\sing{c}{\skti psa}{\skt :psa}
\sing{a}{\skti pstha}{\skt :ps1Ta :ps1`Ta }
\sing{a}{\skti psna}{\skt :p=+:\ZM{rMolHneHegMi}a :ps1na }
\sing{a}{\skti psma}{\skt :psma}
\sing{p}{\skti psya}{\skt :ps1ya} 
\sing{c}{\skti psva}{\skt :ps1va}
\sing{a}{\skti phja}{\skt :P1ja}
\sing{a}{\skti ph\d ta}{\skt :P1f}
\sing{a}{\skti phta}{\skt :P1ta}
\sing{a}{\skti phna}{\skt :P\ZM{vBnjBE} :P1na }
\sing{a}{\skti phpa}{\skt :P1pa}
\sing{a}{\skti phpha}{\skt :P1P}
\sing{a}{\skti phma}{\skt :P1ma}
\sing{a}{\skti phya}{\skt :Py2+.a :P1ya }
\sing{a}{\skti phra}{\skt :P\ZH{-10}{r}}
\sing{a}{\skti phla}{\skt :P1l :P1l1a }
\sing{a}{\skti phva}{\skt :P1va}
\sing{a}{\skti ph\'sa}{\skt :P1Za}
\sing{a}{\skti bka}{\skt b.k}
\sing{a}{\skti bga}{\skt b.ga}
\sing{c}{\skti bgha}{\skt b.Ga}
\sing{c}{\skti bja}{\skt b.ia}
\sing{a}{\skti bjya}{\skt b.iya}
\sing{a}{\skti bjha}{\skt b.Ja b.`J }
\sing{a}{\skti b\d ta}{\skt b.f}
\sing{a}{\skti b\d da}{\skt b.q}
\sing{a}{\skti b\d dha}{\skt b.Q}
\sing{a}{\skti bta}{\skt b.ta}
\sing{c}{\skti bda}{\skt b.d}
\sing{a}{\skti bdya}{\skt b.d\ZM{fByF0E};a b.dy1a }
\sing{c}{\skti bdha}{\skt b.Da}
\sing{a}{\skti bdhya}{\skt b.Dya}
\sing{a}{\skti bdhra}{\skt b.Dra}
\sing{a}{\skti bdhva}{\skt b.Dva}
\sing{c}{\skti bna}{\skt \ZM{0Ok0Ob0FnIFe}+;a b.na }
\sing{c}{\skti bba}{\skt \ZM{0Ok0Ob0Bk0BbNdA}+;a b.ba }
\sing{c}{\skti bbha}{\skt b.Ba}
\sing{c}{\skti bbhya}{\skt b.Bya}
\sing{a}{\skti bbhra}{\skt b.Bra}
\sing{a}{\skti bma}{\skt b.ma}
\sing{c}{\skti bya}{\skt b.ya}
\sing{c}{\skti bra}{\skt b.ra}
\sing{p}{\skti bla}{\skt b.l b.l1a } 
\sing{a}{\skti blya}{\skt b.l1ya}
\sing{c}{\skti bva}{\skt \ZM{0Ok0Ob0BkNdA}+;a b.va }
\sing{a}{\skti b\'sa}{\skt b.Za}
\sing{a}{\skti bsa}{\skt b.sa}
\sing{a}{\skti bh\d na}{\skt BNa B`Na }
\sing{a}{\skti bhda}{\skt Bd}
\sing{c}{\skti bhna}{\skt B\ZM{jFncLe}.a Bna }
\sing{a}{\skti bhnva}{\skt B\ZM{jGnbGi0Lu}+.a Bnva }
\sing{a}{\skti bhba}{\skt Bba}
\sing{a}{\skti bhma}{\skt Bm1\ZM{cLe}.a}
\sing{c}{\skti bhya}{\skt Bya}
\sing{c}{\skti bhra}{\skt Bra}
\sing{a}{\skti bhtya}{\skt Btya}
\sing{a}{\skti bhla}{\skt Bl Bl1a }
\sing{c}{\skti bhva}{\skt Bva}
\sing{p}{\skti m\d na}{\skt m1\ZM{cLe}.Na m1\ZM{cLe}.`Na } 
\sing{a}{\skti mta}{\skt m1\ZM{cLe}.ta}
\sing{a}{\skti mda}{\skt m1\ZM{cLe}.d}
\sing{p}{\skti mdha}{\skt m1\ZM{cLe}.Da} 
\sing{p}{\skti mdhva}{\skt m1\ZM{cLe}.Dva} 
\sing{c}{\skti mna}{\skt m1\ZM{hFnaLe}:a m1\ZM{cLe}.na }
\sing{p}{\skti mnya}{\skt m1\ZM{hFnaLe}:ay1a m1\ZM{cLe}.nya } 
\sing{c}{\skti mpa}{\skt m1\ZM{cLe}.pa}
\sing{a}{\skti mpya}{\skt m1\ZM{cLe}.pya}
\sing{c}{\skti mpra}{\skt m1\ZM{cLe}.pra}
\dual{a}{\skti mpla}{\skt m1\ZM{cLe}.p\ZM{lbl0FI0PE}; m1\ZM{cLe}.pl}{\skt m1\ZM{cLe}.pl1a :m1.p\ZM{qLepbL0bE}a }
\sing{a}{\skti mpsa}{\skt m1\ZM{cLe}.psa}
\sing{a}{\skti mpsya}{\skt m1\ZM{cLe}.ps1ya}
\sing{a}{\skti mpha}{\skt m1\ZM{cLe}.P}
\sing{a}{\skti mphya}{\skt m1\ZM{cLe}.Py2+.a m1\ZM{cLe}.P1ya }
\sing{c}{\skti mba}{\skt m1ba}
\sing{a}{\skti mbpa}{\skt m1b.pa}
\sing{m}{\skti mbya}{\skt m1b.ya}
\sing{a}{\skti mbla}{\skt m1b.l m1b.l1a }
\sing{p}{\skti mbva}{\skt m1\ZM{0Ok0Ob0BkNdA}+;a m1b.va } 
\sing{c}{\skti mbha}{\skt m1Ba}
\sing{a}{\skti mbhma}{\skt m1Bm1\ZM{cLe}.a}
\sing{p}{\skti mbhya}{\skt m1Bya} 
\sing{a}{\skti mbhra}{\skt m1Bra}
\sing{a}{\skti mbhva}{\skt m1Bva}
\sing{c}{\skti mma}{\skt mma}
\sing{a}{\skti mmya}{\skt mm1ya}
\sing{a}{\skti mmra}{\skt mm@Ra}
\sing{c}{\skti mya}{\skt m1ya}
\sing{c}{\skti mra}{\skt m@Ra}
\sing{c}{\skti mla}{\skt m1\ZM{aLeDPEDFIhBl}+ m1l m1l1a m1\ZM{aLeDdElbL}:a }
\sing{c}{\skti mva}{\skt m1va}
\sing{p}{\skti mvya}{\skt m1v.ya} 
\sing{a}{\skti mvra}{\skt m1v.ra}
\sing{a}{\skti mvla}{\skt m1v.l m1v.l1a }
\sing{a}{\skti m\'sa}{\skt m1\ZM{cLe}.Za}
\sing{p}{\skti msa}{\skt m1\ZM{cLe}.sa} 
\sing{a}{\skti mha}{\skt m1\ZM{cLe}.h}
\sing{a}{\skti yna}{\skt y\ZM{nBneBe0BE}a yna }
\sing{p}{\skti ypa}{\skt ypa} 
\sing{a}{\skti yma}{\skt yma}
\sing{c}{\skti yya}{\skt yya}
\sing{a}{\skti yra}{\skt yra}
\sing{a}{\skti yla}{\skt yl yl1a }
\sing{c}{\skti yva}{\skt yva}
%%%
\sing{a}{\skti rka}{\skt k\ZH{-12}{R}}
\sing{a}{\skti rkka}{\skt \ZM{0NkLNPLPE00kL0PLhA}*:\ZH{-8}{R} k1k\ZH{-12}{R} }
\sing{a}{\skti rk\d sa}{\skt [Ra `[Ra }
\sing{a}{\skti rk\d sma}{\skt [mRa `[mRa }
\sing{a}{\skti rk\d sya}{\skt [yRa `[yRa }
\sing{a}{\skti rk\d sva}{\skt [vRa `[vRa }
\sing{a}{\skti rksa}{\skt k1sRa} 
\sing{a}{\skti rkha}{\skt KRa}
\sing{a}{\skti rkhva}{\skt K.vRa}
\sing{a}{\skti rga}{\skt gRa}
\sing{a}{\skti rgga}{\skt ggRa}
\sing{a}{\skti rggha}{\skt gGRa} 
\sing{a}{\skti rgya}{\skt gyRa}
\sing{a}{\skti rgra}{\skt gr4Ra}
\sing{a}{\skti rgha}{\skt ;GRa}
\sing{a}{\skti rghya}{\skt ;GyRa}
\sing{a}{\skti r\.na}{\skt .z\ZH{-10}{R}}
\sing{a}{\skti r\.nk\d sma}{\skt *\ZM{jPqfbeFOMpbxbbmIbiPdE}*a\ZH{-6}{R} *\ZM{hPqHOMrjXdbmKbePfE}*a\ZH{-6}{R} }
\sing{a}{\skti r\.nk\d sva}{\skt \ZM{FPqVOM0bxLcvVfEVBE}*+.\ZH{-8}{R} \ZM{HPqXOM0gXNbvXBEXdE}*+:\ZH{-8}{R} }
\sing{a}{\skti r\.nga}{\skt \ZM{0PqPOM0bgNaENdE}*:\ZH{-8}{R}}
\sing{a}{\skti rca}{\skt ..cRa} 
\sing{a}{\skti rcca}{\skt c1Ra ..ccRa }
\sing{a}{\skti rccha}{\skt ..cC\ZH{-6}{R}}
\sing{a}{\skti rcpa}{\skt ..cpRa} 
\sing{a}{\skti rcya}{\skt ..cyRa}
\sing{a}{\skti rcha}{\skt C\ZH{-6}{R}}
\sing{a}{\skti rja}{\skt .jRa} 
\sing{a}{\skti rjja}{\skt \ZM{0Jj0djRdA}*.a\ZH{-6}{R} j2Ra }
\sing{a}{\skti rjjha}{\skt jJRa j1`J\ZH{-8}{R} }
\sing{a}{\skti rj\~na}{\skt :]Ra `]Ra }
\sing{a}{\skti rjpa}{\skt .jpRa} 
\sing{a}{\skti rjya}{\skt .j1yRa}
\sing{a}{\skti rjha}{\skt JRa `J\ZH{-8}{R} }
\sing{a}{\skti r\~na}{\skt VRa} 
\sing{a}{\skti r\d ta}{\skt f\ZH{-8}{R}} 
\sing{a}{\skti r\d tta}{\skt \ZM{0PfBftIBeNbENAE}*\ZH{-6}{R}} 
\sing{a}{\skti r\d tya}{\skt fy1Ra}
\sing{a}{\skti r\d tha}{\skt F\ZH{-8}{R}}
\sing{a}{\skti r\d th\d tha}{\skt \ZM{0PF00F}*\ZH{-6}{R}}
\sing{a}{\skti r\d da}{\skt .q\ZH{-6}{R}}
\sing{a}{\skti r\d d\d da}{\skt \ZM{0Pq0bq}*\ZH{-4}{R}} 
\sing{a}{\skti r\d dha}{\skt Q\ZH{-6}{R}}
\sing{a}{\skti r\d dh\d dha}{\skt \ZM{0PQ0bQ}*\ZH{-6}{R}}
\sing{a}{\skti r\d dhya}{\skt Q.y3a\ZH{-6}{R} Qy1Ra }
\sing{a}{\skti r\d na}{\skt :NRa .`NRa } 
\sing{a}{\skti r\d n\d na}{\skt :NNRa .`N`NRa }
\sing{a}{\skti r\d nya}{\skt :NyRa .`NyRa }
\sing{a}{\skti rta}{\skt tRa}
\sing{a}{\skti rttya}{\skt t1yRa ttyRa }
\sing{a}{\skti rttra}{\skt \ZM{0DtHLaaAb}+;t4Ra}
\sing{a}{\skti rtma}{\skt tmRa}
\sing{a}{\skti rtya}{\skt tyRa}
\sing{a}{\skti rtra}{\skt t3Ra}
\sing{a}{\skti rtrya}{\skt t3yRa}
\sing{a}{\skti rtva}{\skt tvRa}
\sing{a}{\skti rtsa}{\skt tsRa}
\sing{a}{\skti rtsna}{\skt t=+:\ZM{rMolHneHegMi}Ra ts1nRa }
\sing{a}{\skti rtsnya}{\skt t=+:\ZM{rMolHneHegMi}yRa ts1nyRa }
\sing{a}{\skti rtsya}{\skt ts1yRa}
\sing{a}{\skti rtha}{\skt TRa  `TRa}
\sing{a}{\skti rthya}{\skt TyRa `TyRa }
\sing{a}{\skti rda}{\skt d\ZH{-6}{R}}
\sing{a}{\skti rdda}{\skt d1\ZH{-6}{R}}
\sing{a}{\skti rddya}{\skt d1\ZM{dbyHbE}+a\ZH{-6}{R} d1y1Ra }
\sing{a}{\skti rddha}{\skt .;d\ZM{t0Dj0b}\ZH{-6}{R}}
\sing{a}{\skti rddhya}{\skt .;d\ZM{t0DfByF0E};a\ZH{-6}{R}}
\sing{a}{\skti rddhra}{\skt .;d\ZM{t0Dj0b}\ZP{-10}{-6}{r1}\ZH{-6}{R}} 
\sing{a}{\skti rddhrya}{\skt .;d\ZM{t0DfByF0EfjR};a\ZH{-6}{R} .;d\ZM{t0Dj0b}\ZP{-10}{-6}{r1}y1Ra }
\sing{a}{\skti rdra}{\skt d\ZP{-8}{-4}{@R}\ZH{-6}{R}}
\sing{a}{\skti rdha}{\skt ;DRa} 
\sing{a}{\skti rdhda}{\skt ;Dd\ZH{-6}{R}} 
\sing{a}{\skti rdhnya}{\skt \ZM{0XiBNHMXeDDnRDENXiKDi}\ZS{14}:ay1Ra ;DnyRa }
\sing{a}{\skti rdhma}{\skt ;Dm1\ZM{cLe}.Ra}
\sing{a}{\skti rdhya}{\skt ;DyRa}
\sing{a}{\skti rdhra}{\skt ;DrRa}
\sing{a}{\skti rdhrya}{\skt ;DryRa}
\sing{a}{\skti rdhva}{\skt ;DvRa}
\sing{a}{\skti rna}{\skt nRa} 
\sing{a}{\skti rnna}{\skt n1Ra \ZM{0Rn0HnIReIHe}+;Ra }
\sing{a}{\skti rpa}{\skt :pRa}
\sing{a}{\skti rpta}{\skt p1Ra :ptRa }
\sing{a}{\skti rppha}{\skt :pP\ZH{-10}{R}}
\sing{a}{\skti rpba}{\skt :pbRa}
\sing{a}{\skti rpya}{\skt :pyRa}
\sing{a}{\skti rpha}{\skt :P\ZH{-10}{R}}
\sing{a}{\skti rphya}{\skt :Py2+.a\ZH{-6}{R} :P1yRa }
\sing{a}{\skti rba}{\skt bRa}
\sing{a}{\skti rbba}{\skt \ZM{0Ok0Ob0Bk0BbNdA}+;a\ZH{-6}{R} b.bRa }
\sing{a}{\skti rbbha}{\skt b.BRa}
\sing{a}{\skti rbha}{\skt BRa}
\sing{a}{\skti rbhba}{\skt BbRa}
\sing{a}{\skti rma}{\skt mRa}
\sing{a}{\skti rmma}{\skt mmRa}
\sing{a}{\skti rmya}{\skt m1yRa}
\sing{a}{\skti rya}{\skt yRa}
\sing{a}{\skti ryya}{\skt yyRa}
\sing{a}{\skti rra}{\skt .=\ZH{-6}{R}}
\sing{a}{\skti rla}{\skt l\ZH{-8}{R}}
\sing{a}{\skti rlla}{\skt l2\ZH{-4}{R} l1l\ZH{-8}{R} l1l1Ra \ZM{0CL0MLPBE}++a\ZH{-6}{R} }
\sing{a}{\skti rva}{\skt vRa}
\sing{a}{\skti rvya}{\skt v.yRa}
\sing{a}{\skti rvva}{\skt \ZM{0Ok0BkNdA}+;a\ZH{-6}{R} v.vRa }
\sing{a}{\skti rvha}{\skt v.h\ZH{-6}{R}}
\sing{a}{\skti r\'sa}{\skt ZRa} 
\sing{a}{\skti r\'sya}{\skt ZyRa}
\sing{a}{\skti r\'sva}{\skt (\ZM{dGu};Ra )\ZM{dGu};Ra ZvRa }
\sing{a}{\skti r\'s\'sa}{\skt ZZRa}
\sing{a}{\skti r\d sa}{\skt :SRa} 
\sing{a}{\skti r\d s\d ta}{\skt :S1\ZH{-6}{R} :Sf\ZH{-8}{R} }
\sing{a}{\skti r\d s\d tya}{\skt :S1y1Ra :Sfy1Ra }
\sing{a}{\skti r\d s\d tra}{\skt :S1\ZH{-10}{r1}\ZH{-6}{R} :Sf\ZH{-12}{r1}\ZH{-8}{R} }
\sing{a}{\skti r\d s\d na}{\skt :SNRa :S`NRa }
\sing{a}{\skti r\d sma}{\skt :SmRa}
\sing{a}{\skti r\d sya}{\skt :SyRa}
\sing{a}{\skti r\d s\d sa}{\skt :SSRa}
\sing{a}{\skti rsa}{\skt .sRa}
\sing{a}{\skti rsma}{\skt .smRa}
\sing{a}{\skti rssa}{\skt .ssRa}
\sing{a}{\skti rha}{\skt h\ZH{-6}{R}}
\sing{a}{\skti rhma}{\skt h2\ZH{-6}{R}}
%%%
%\sing{a}{\skti rra}{\skt rra}
\sing{c}{\skti lka}{\skt l1k}
\sing{a}{\skti lkya}{\skt l1ky2+.a l1k1ya }
\sing{a}{\skti lkha}{\skt l1Ka}
\sing{p}{\skti lga}{\skt l1ga} 
\sing{a}{\skti lgya}{\skt l1gya}
\sing{p}{\skti l\.na}{\skt l1z} 
\sing{p}{\skti l\.nya}{\skt l1zy3a} 
\sing{a}{\skti lja}{\skt l1ja}
\sing{a}{\skti l\d ta}{\skt l1f}
\sing{a}{\skti l\d tra}{\skt l1f\ZH{-12}{r1}}
\sing{a}{\skti l\d tha}{\skt l1F}
\sing{a}{\skti l\d da}{\skt l1q}
\sing{a}{\skti l\d dra}{\skt l1q\ZH{-8}{r1}}
\sing{a}{\skti l\d dha}{\skt l1Q}
\sing{p}{\skti lta}{\skt l1ta} 
\sing{a}{\skti ltha}{\skt l1Ta l1`Ta }
\sing{a}{\skti lda}{\skt l1d}
\sing{p}{\skti ldha}{\skt l1Da} 
\sing{a}{\skti lna}{\skt l1na}
\sing{c}{\skti lpa}{\skt l1pa}
\sing{a}{\skti lpta}{\skt l1p1a l1pta }
\sing{a}{\skti lptya}{\skt l1p1ya l1ptya }
\sing{a}{\skti lptva}{\skt l1p1va l1ptva }
\sing{a}{\skti lptha}{\skt l1pTa l1p`Ta }
\sing{a}{\skti lpya}{\skt l1pya}
\sing{a}{\skti lpsa}{\skt l1psa}
\sing{a}{\skti lpsma}{\skt l1psma}
\sing{a}{\skti lpsya}{\skt l1ps1ya}
\sing{a}{\skti lpsva}{\skt l1ps1va}
\sing{a}{\skti lpha}{\skt l1P}
\sing{p}{\skti lba}{\skt l1ba} 
\sing{a}{\skti lbha}{\skt l1Ba}
\sing{p}{\skti lbhya}{\skt l1Bya} 
\sing{c}{\skti lma}{\skt l1ma}
\sing{c}{\skti lya}{\skt l1ya}
\sing{a}{\skti lra}{\skt l\ZH{-6}{r1} l1r1a }
\sing{c}{\skti lla}{\skt l2 l1l l1l1a \ZM{0CL0MLPBE}++a }
\sing{a}{\skti llya}{\skt l2:y1a \ZM{0CL0MLPBE}++ay1a l1l1ya }
\sing{c}{\skti lva}{\skt l1va}
\sing{a}{\skti lv\d da}{\skt l1v.q}
\sing{a}{\skti lvdhva}{\skt l1v.Dva}
\sing{a}{\skti l\'sa}{\skt l1Za}
\sing{a}{\skti l\d sa}{\skt l1Sa}
\sing{a}{\skti lsa}{\skt l1sa}
\sing{c}{\skti lha}{\skt l1h}
\sing{a}{\skti lhya}{\skt l1h\ZM{hByDBE}:a}
\sing{a}{\skti \ZZ dya}{\skt L1ya L2.ya }
\sing{a}{\skti \ZZ dha}{\skt L1h L2h }
\sing{p}{\skti vja}{\skt via} 
\sing{a}{\skti vjha}{\skt v.Ja v.`J }
\sing{a}{\skti v\d dha}{\skt v.Q}
\sing{a}{\skti vda}{\skt v.d}
\sing{a}{\skti vdya}{\skt v.d\ZM{fByF0E};a v.dy1a }
\sing{a}{\skti vdha}{\skt v.Da}
\sing{a}{\skti vdhma}{\skt v.Dm1\ZM{cLe}.a}
\sing{a}{\skti vdhya}{\skt v.Dya}
\sing{a}{\skti vdhrya}{\skt v.Drya}
\sing{a}{\skti vdhva}{\skt v.Dva}
\sing{c}{\skti vna}{\skt \ZM{0Ok0FnIFeN0A}+;a v.na }
\sing{a}{\skti vbha}{\skt v.Ba}
\sing{a}{\skti vbhya}{\skt v.Bya}
\sing{a}{\skti vma}{\skt v.ma}
\sing{c}{\skti vya}{\skt v.ya}
\sing{c}{\skti vra}{\skt v.ra}
\sing{a}{\skti vrla}{\skt v.rl v.rl1a }
\sing{p}{\skti vla}{\skt v.l v.l1a } 
\sing{c}{\skti vva}{\skt \ZM{0Ok0BkNdA}+;a v.va }
\sing{a}{\skti vha}{\skt v.h}
\sing{p}{\skti \'ska}{\skt Zk} 
\sing{c}{\skti \'sca}{\skt (\ZM{rac0FI}a )\ZM{rac0FI}a Z.ca }
\sing{p}{\skti \'scpha}{\skt (\ZM{rac0FI}P )\ZM{rac0FI}P Z.cP } 
\sing{c}{\skti \'scya}{\skt (\ZM{rac0FI}ya )\ZM{rac0FI}ya Z.cya }
\sing{a}{\skti \'scra}{\skt (\ZM{rac0FI}r1a )\ZM{rac0FI}r1a Z.c@Ra }
\sing{p}{\skti \'scha}{\skt ZC} 
\sing{a}{\skti \'schya}{\skt ZC1 ZC.y1a }
\sing{p}{\skti \'sja}{\skt Zja} 
\sing{p}{\skti \'sjha}{\skt ZJa Z`J } 
\sing{a}{\skti \'s\d ta}{\skt Zf}
\sing{c}{\skti \'sna}{\skt (\ZM{pFngFi}a )\ZM{pFngFi}a Zna }
\sing{a}{\skti \'sta}{\skt Zta}
\sing{a}{\skti \'spa}{\skt Zpa}
\sing{p}{\skti \'sma}{\skt Zma} 
\sing{c}{\skti \'sya}{\skt Zya}
\sing{c}{\skti \'sra}{\skt (ra )ra }
\sing{c}{\skti \'srya}{\skt (rya )rya }
\dual{c}{\skti \'sla}{\skt (\ZM{lBl0FI0PE}; )\ZM{lBl0FI0PE}; )\ZM{pBL00E}a (\ZM{pBL00E}a}{\skt Zl1a Zl }
\sing{c}{\skti \'sva}{\skt (\ZM{dGu};a )\ZM{dGu};a Zva }
\sing{c}{\skti \'svya}{\skt (\ZM{dGu};ya )\ZM{dGu};ya Zv.ya }
\sing{c}{\skti \'s\'sa}{\skt ZZa}
\sing{p}{\skti \d ska}{\skt :Sk} 
\sing{a}{\skti \d skya}{\skt :Sky2+.a :Sk1ya }
\sing{p}{\skti \d skra}{\skt :Sk\ZM{l0R}} 
\sing{a}{\skti \d skva}{\skt :S\ZM{0NkLNPLPE00kLhA}*: :Sk1va }
\sing{a}{\skti \d skha}{\skt :SKa}
\sing{p}{\skti \d sjha}{\skt :SJa :S`J } 
\sing{c}{\skti \d s\d ta}{\skt :S1 :Sf }
\sing{a}{\skti \d s\d tnya}{\skt :S1\ZM{rfnifeddEdfE}y1a :S\ZM{0Pf0BnIBeN0ENCI}*y1a }
\sing{c}{\skti \d s\d tya}{\skt :S1y1a :Sfy1a }
\sing{c}{\skti \d s\d tra}{\skt :S1\ZH{-10}{r1} :Sf\ZH{-12}{r1} }
\sing{c}{\skti \d s\d trya}{\skt :S1\ZH{-10}{r1}y1a :Sf\ZH{-12}{r1}y1a }
\sing{p}{\skti \d s\d tla}{\skt :S1\ZM{rjlffIfdI} :S\ZM{0Pf0blLBI}* :S\ZM{0Pf0bLPdEPDE}* :S1\ZM{tjLdlEddE} } 
\sing{c}{\skti \d s\d tva}{\skt :S1\ZM{pfuffE} :Sf\ZM{pfuffE} }
\sing{c}{\skti \d s\d tha}{\skt :S2 :SF }
\dual{p}{\skti \d s\d thya}{\skt :S2.y3a :SF:y3a}{\skt :SFy1a :S2y1a } 
\sing{a}{\skti \d s\d thra}{\skt :S2\ZH{-10}{r1} :SF\ZH{-10}{r1} }
\dual{a}{\skti \d s\d thrya}{\skt :S2\ZH{-10}{r1}.y3a :SF\ZH{-10}{r1}:y3a}{\skt :SF\ZH{-10}{r1}y1a :S2\ZH{-10}{r1}y1a }
\sing{a}{\skti \d s\d thva}{\skt :S2\ZM{pfuffE} :SF\ZM{pfufgEfhE} }
\sing{c}{\skti \d s\d na}{\skt :SNa :S`Na }
\sing{c}{\skti \d s\d nya}{\skt :SNya :S`Nya }
\sing{a}{\skti \d s\d nva}{\skt :SNva :S`Nva }
\sing{a}{\skti \d sta}{\skt :Sta}
\sing{a}{\skti \d sna}{\skt :S\ZM{lBn0dI}a :Sna }
\sing{c}{\skti \d spa}{\skt :Spa}
\sing{p}{\skti \d spya}{\skt :Spya} 
\sing{c}{\skti \d spra}{\skt :Spra}
\sing{p}{\skti \d spha}{\skt :SP} 
\sing{c}{\skti \d sma}{\skt :Sma}
\sing{a}{\skti \d smya}{\skt :Sm1ya}
\sing{c}{\skti \d sya}{\skt :Sya}
\sing{a}{\skti \d syya}{\skt :Syya}
\sing{a}{\skti \d sra}{\skt :Sra}
\sing{p}{\skti \d sla}{\skt :Sl :Sl1a } 
\sing{c}{\skti \d sva}{\skt :Sva}
\sing{a}{\skti \d s\d sa}{\skt :SSa}
\sing{c}{\skti ska}{\skt .s1k}
\sing{a}{\skti skya}{\skt .s1ky2+.a .s1k1ya }
\sing{a}{\skti skra}{\skt .s1k\ZM{l0R}}
\sing{a}{\skti sk\d sa}{\skt .s1[a .s1`[a }
\sing{c}{\skti skha}{\skt .s1Ka}
\sing{a}{\skti sga}{\skt .s1ga}
\sing{a}{\skti sgha}{\skt .s1\ZM{cLe}.Ga}
\sing{p}{\skti s\.na}{\skt .s1z} 
\sing{a}{\skti sca}{\skt .s1.ca}
\sing{a}{\skti scha}{\skt .s1\ZM{cLe}.C}
\sing{p}{\skti sja}{\skt .s1ja} 
\sing{p}{\skti sjha}{\skt .s1\ZM{cLe}.Ja .s1\ZM{cLe}.`J } 
\sing{a}{\skti s\~na}{\skt .s1Va}
\sing{a}{\skti s\d ta}{\skt .s1f}
\sing{a}{\skti s\d tra}{\skt .s1f\ZH{-12}{r1}}
\sing{a}{\skti s\d tra}{\skt .s1f\ZH{-12}{r1}}
\sing{a}{\skti s\d da}{\skt .s1\ZM{cLe}.q}
\sing{a}{\skti s\d dha}{\skt .s1Q}
\sing{a}{\skti s\d na}{\skt .s1\ZM{cLe}.Na .s1\ZM{cLe}.`Na }
\sing{c}{\skti sta}{\skt .s1ta}
\sing{a}{\skti stta}{\skt .s\ZS{-6}t1a .s1tta }
\sing{a}{\skti sttya}{\skt .s\ZS{-6}t1ya .s1ttya }
\sing{c}{\skti stya}{\skt .s1tya}
\sing{c}{\skti stra}{\skt .s1:t4a}
\sing{a}{\skti strya}{\skt .s1:t4ya}
\sing{c}{\skti stva}{\skt .s1tva}
\sing{p}{\skti stvya}{\skt .s1tv.ya} 
\sing{c}{\skti stha}{\skt .s1Ta .s1`Ta }
\dual{m}{\skti sthna}{\skt .s1T\ZM{pBneBe0BE}a .s1Tna}{\skt .s1`Tna .s1`T\ZM{pBneBe0BE}a }
\sing{a}{\skti sthya}{\skt .s1Tya .s1`Tya }
\sing{a}{\skti sda}{\skt .s1\ZM{cLe}.d}
\sing{a}{\skti sdha}{\skt .s1\ZM{cLe}.Da}
\sing{p}{\skti sdhva}{\skt .s1\ZM{cLe}.Dva} 
\sing{c}{\skti sna}{\skt .=+:\ZM{rMolHneHegMi}a .s1na }
\sing{c}{\skti snya}{\skt .=+:\ZM{rMolHneHegMi}ya .s1nya }
\sing{a}{\skti snva}{\skt .=\ZM{fMo0HnHMu}*:a .s1nva }
\sing{c}{\skti spa}{\skt .s1\ZM{cLe}.pa}
\sing{a}{\skti spma}{\skt .s1\ZM{cLe}.pma}
\sing{a}{\skti spya}{\skt .s1\ZM{cLe}.pya}
\sing{p}{\skti spra}{\skt .s1\ZM{cLe}.pra} 
\sing{c}{\skti spha}{\skt .s1\ZM{cLe}.P}
\sing{a}{\skti sphya}{\skt .s1\ZM{cLe}.Py2+.a .s1\ZM{cLe}.P1ya }
\sing{p}{\skti sba}{\skt .s1ba} 
\sing{a}{\skti sbha}{\skt .s1\ZM{cLe}.Ba}
\sing{c}{\skti sma}{\skt .sma}
\sing{c}{\skti smya}{\skt .sm1ya}
\sing{a}{\skti smra}{\skt .sm@Ra}
\sing{c}{\skti sya}{\skt .s1ya}
\sing{a}{\skti syya}{\skt .s1yya}
\sing{c}{\skti sra}{\skt .s1\ZM{aLeDDr}:a}
\sing{a}{\skti srya}{\skt .s1\ZM{aLeDDr}:ya}
\sing{p}{\skti srva}{\skt .s1\ZM{aLeDDr}:va} 
\sing{a}{\skti sla}{\skt .s1l .s1l1a }
\sing{c}{\skti sva}{\skt .s1va}
\sing{a}{\skti svya}{\skt .s1v.ya}
\sing{a}{\skti svra}{\skt .s1v.ra}
\sing{a}{\skti svva}{\skt .s1\ZM{0Ok0BkNdA}+;a .s1v.va }
\sing{a}{\skti s\'sa}{\skt .s1\ZM{cLe}.Za}
\sing{a}{\skti s\d sa}{\skt .s1\ZM{cLe}.Sa}
\sing{c}{\skti ssa}{\skt .ssa}
\sing{a}{\skti ssma}{\skt .ssma}
\sing{p}{\skti ssva}{\skt .ss1va} 
\sing{p}{\skti sha}{\skt .s1\ZM{cLe}.h} 
\sing{c}{\skti h\d na}{\skt h3\ZM{m0NmDIfDI} h4\ZM{rcOlDIfDI0dE} }
\sing{c}{\skti hna}{\skt h3\ZM{nCneCe}}
\sing{a}{\skti hnya}{\skt h3\ZM{nCneCe}y1a}
\sing{p}{\skti hnva}{\skt h4\ZM{qBngBillk0lE}} 
\sing{a}{\skti hba}{\skt h3\ZM{mAkmAb}}
\sing{c}{\skti hma}{\skt h2}
\sing{p}{\skti hmya}{\skt h2y1a} 
\sing{c}{\skti hya}{\skt h\ZM{hByDBE}:a}
\sing{c}{\skti hra}{\skt :h\ZM{ojr}}
\sing{a}{\skti hrya}{\skt :h\ZM{hByDBEojr}:a}
\sing{c}{\skti hla}{\skt h4\ZM{p0L}}
\sing{c}{\skti hva}{\skt h3\ZM{mAk}}
\sing{a}{\skti hvya}{\skt h3\ZM{mAk}y1a}
\sing{a}{\skti hvra}{\skt h3\ZM{mAk}\ZV{-6}{r1}}

\end{multicols}

\end{document}

